### 2017-02-15 paper.tex
first commit

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}
\documentclass[journal]{IEEEtran}

\usepackage{techrep}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{subfigure}

% \setlength{\columnsep}{10mm}
% \setlength{\textwidth}{180mm}
% \setlength{\textheight}{250mm}
% \addtolength{\oddsidemargin}{-9mm}
% \addtolength{\topmargin}{-25mm}

\graphicspath{{figures/}}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
% Axel Sommerfeldt. This package may be useful when used in conjunction with
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.

% title
% \title{Bare Demo of IEEEtran.cls\\ for IEEE Journals}

%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

% auther
% \author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
%         John~Doe,~\IEEEmembership{Fellow,~OSA,}
%         and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
% \thanks{M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
% \thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

% note the % following the last \IEEEmembership and also \thanks -
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
%
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
% \maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
% \begin{abstract}
% The abstract goes here.
% \end{abstract}

% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
% IEEE, IEEEtran, journal, \LaTeX, paper, template.
% \end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

% Introduction
% First paragraph of paper need be big Alhabet
% \section{Introduction}
% \IEEEPARstart{T}{his}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{vCPE System Overview}
Our object is to demonstrate that our vCPE system can help the telco to reduce the Capex and Opex when deploying, maintaining and updating CPE service. This section describes our vCPE system architecture and how we achieve our goal. In the subsection \ref{ssec:service_design}, we will introduce the overview architecture of our virtual CPE Service. Then in subsection \ref{ssec:vcpe_deploy}, we will explain that through the advantages of service architecture, our vCPE system can deploy our service to the customer easily. In the subsection \ref{ssec:vcpe_archi}, we will give details of the whole vCPE system.

\subsection{vCPE Service Design Overview} \label{ssec:service_design}
\begin{figure}[!t]
  \centering
  \includegraphics[width=3in]{./figures/service_design_overview}
  \caption{vCPE Service Design Architecture}
  \label{fig:service_overview}
\end{figure}
With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig. \ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures. The former is mainly responsible for dealing with stateful processing, and the latter is used for stateless processing component.

\subsubsection{Stateful Processing Componemt}
This component have to perform more complex algorithm, keep the state associated with the VNF and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component, since software is good at these tasks. It's worth noting that we use southbound APIs of SDN controller to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.

\subsubsection{Stateless Processing Componemt}
Stateless processing component, are implemented by SDN datapath resources, which is optimized for data plane traffic processing. Since SDN datapath have decoupled the control plane and data plane, so it can accept the control message from the stateful processing component.

\subsection{Service Deployment Model} \label{ssec:vcpe_deploy}

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/deployment}
\caption{Service Deployment Model}
\label{fig:vcpe_deploy}
\end{figure}

In this picture, each green area is a local network domain of customer. At the gateway of this domain, there's a SDN-enabled switch. The customer can subscribe to our vcpe service through our vcpe dashboard. after subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed. The customer only need to setup the gateway SDN switch to connect the SDN controller by the OpenFlow protocol, then the switch will handle these service.

\subsection{Architecture of the vCPE system} \label{ssec:vcpe_archi}
\subsubsection{System Overview}
\subsubsection{System Implementation}
\subsubsubsection{Infrastructure Controller}
% shipyard

\subsubsubsection{Infrastructure Orchestrator}
% api server

\subsubsubsection{VNF Controllers}
% sdn controller

\subsubsubsection{VNF Orchestrator}
% web server

\section{Virtula CPE Services}

\newpage

\bibliographystyle{ieeetr}
\bibliography{paper}

\end{document}

### 2017-02-15 paper.tex
update

@@
 \ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures.
-The former is mainly responsible for dealing with stateful processing, and the latter is used for stateless processing component.
+The former is a VNF controller, mainly responsible for dealing with stateful processing.
+The latter is a SDN switch, used for stateless processing.
 
-\subsubsection{Stateful Processing Componemt}
+\subsubsection{Stateful Processing component (VNF controller in container)}
 This component have to perform more complex algorithm, keep the state associated with the VNF and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component, since software is good at these tasks.
-It's worth noting that we use southbound APIs of SDN controller to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
+We use SDN controller to implement the NFV controller and it's worth noting that we use southbound APIs of SDN controller to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
 
-\subsubsection{Stateless Processing Componemt}
+\subsubsection{Stateless Processing component (SDN datapath)}
 Stateless processing component, are implemented by SDN datapath resources, which is optimized for data plane traffic processing.
 Since SDN datapath have decoupled the control plane and data plane, so it can accept the control message from the stateful processing component.
+
+Using the advantages of this architecture, we can assign stateless or light-weight state work to the SDN switch, for example, packet filtering and packet counting, to load-off the computing resources.
+If we want to update our service, we just need to update the statful component, since the stateless component just follow the command from stateful components.
 
@@
 
-In this picture, each green area is a local network domain of customer.
+With architecure mentioned in \ref{ssec:service_design}, we come up with a network function service deployment model.
+Because the algorithm and policies handled by computing infrastructures, and the generic network devices, that is, SDN switches, only do stateless processing.
+The customer only need to buy a general SDN switch at their home gateway and subscribe different NFV controller through our vCPE platform, they will have a different network function service.
+
+In figure \ref{fig:vcpe_deploy} illustrated the service deployment model, each green area is a local network domain of customer.
 At the gateway of this domain, there's a SDN-enabled switch.
@@
 \subsubsection{System Overview}
-\subsubsection{System Implementation}
-\subsubsubsection{Infrastructure Controller}
+
+\subsubsection{Infrastructure Controller}
 % shipyard
+The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images.
+The infrastructure does'nt handle the customer authentication or maintaining the state of running service, it just follow the request from the infrastrcure orchestrator to create, delete, start, stop and inspect containers.
 
-\subsubsubsection{Infrastructure Orchestrator}
+\subsubsection{Infrastructure Orchestrator}
+% api server
+The infrasctructure orchestrator plays the key role of our system.
+It connecting and automating of workflows when we deploy our services.
+When a customer subscribes, the infrasctructure orchestrator authenticates the customer first, next it will call the infrastructure controllerto create a container for this customer, and update information in database afterwards.
+It handle the entire lifecycle of our vCPE service.
+
+\subsubsection{Cloud Database}
 % api server
 
-\subsubsubsection{VNF Controllers}
+\subsubsection{VNF Orchestrator}
+% web server
+
+\subsubsection{VNF Controllers}
 % sdn controller
-
-\subsubsubsection{VNF Orchestrator}
-% web server
 

### 2017-02-16 paper.tex
update paper

@@
   \centering
-  \includegraphics[width=3in]{./figures/service_design_overview}
+  \includegraphics[width=3in]{./figures/system_overview_v2}
   \caption{vCPE Service Design Architecture}
@@
 \subsubsection{System Overview}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/system_overview_v2}
+\caption{Service Syetem Overview}
+\label{fig:vcpe_system}
+\end{figure}
+
+The architecture as shown in Fig \ref{fig:vcpe_system} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
+The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers running on virtual machines hosting in the cloud using Amazon Web Services (AWS) Data Center also the Infrastructure Controller is a powerful physical blade server running in our laboratory.
+Each component is introduced in the subsection below.
 
@@
 \subsubsection{Cloud Database}
-% api server
-
-\subsubsection{VNF Orchestrator}
-% web server
+%
+The cloud database is used for restoreing the of our vCPE services, which include each customer's credential, customer's container settings and virtual CPE service states.
+The cloud database is using PostgreSQL, which is a open source, easily customized and object-relational database system.
+Only Infrastructure Orchestrator has read and write permissions to access cloud database.
 
@@
 
-\section{Virtula CPE Services}
+VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module.
+The SDN controller does not have a remote launcher module to remotely execute a SDN controller.
+We built a light-weight server as a launcher module to resolve the remotely execution issue.
+The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand.
+When the infrastructure controller once create the container, the remote module will run up initiallly, waiting request from VNF VNF Orchestrator.
+The details of SDN controller desgin will be presented at section \ref{ssec:vcpe_services}
+
+\subsubsection{VNF Orchestrator}
+% web server
+The VNF Orchestrator is a Web application server hosting on Amazon Web server, being online for customer and provide a dashboard for virtual CPE and containers management and configuration.
+
+Through the web UI provided by the VNF Orchestrator, the customers can subscribe to the desired service and without typing any command via the command line interface (CLI).
+After receiving the subscribing message, the VNF orchestrator will request the infrastructure orchestrator to create a new VNF controller, and then send the virtual CPE configuration to the new VNF controller.
+Based on configuration demands under different conditions, the network administrator is able to select any of the listed services on the dashboard such as NAT, DHCP, Firewall and QoS management.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/vnf_orche_view}
+\caption{Virtual CPE Dashboard User Interface for Container Management}
+\label{fig:vcpe_dashboard}
+\end{figure}
+
+\section{Virtual CPE Services} \label{ssec:vcpe_services}
 

### 2017-02-20 paper.tex
fix vcep archi figure
add chtex to check linter

@@
 %
-\ifCLASSINFOpdf
+\ifCLASSINFOpdf{}
   % \usepackage[pdftex]{graphicx}
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
+\IEEEpeerreviewmaketitle{}
 % Introduction
@@
 This section describes our vCPE system architecture and how we achieve our goal.
-In the subsection \ref{ssec:service_design}, we will introduce the overview architecture of our virtual CPE Service.
-Then in subsection \ref{ssec:vcpe_deploy}, we will explain that through the advantages of service architecture, our vCPE system can deploy our service to the customer easily.
-In the subsection \ref{ssec:vcpe_archi}, we will give details of the whole vCPE system.
+In the subsection\ref{ssec:service_design}, we will introduce the overview architecture of our virtual CPE Service.
+Then in subsection\ref{ssec:vcpe_deploy}, we will explain that through the advantages of service architecture, our vCPE system can deploy our service to the customer easily.
+In the subsection\ref{ssec:vcpe_archi}, we will give details of the whole vCPE system.
 
-\subsection{vCPE Service Design Overview} \label{ssec:service_design}
+\subsection{vCPE Service Design Overview}\label{ssec:service_design}
 \begin{figure}[!t]
   \centering
-  \includegraphics[width=3in]{./figures/system_overview_v2}
+  \includegraphics[width=3in]{./figures/service_design_overview}
   \caption{vCPE Service Design Architecture}
@@
 \end{figure}
-With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig.
-\ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures.
+With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig.\ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures.
 The former is a VNF controller, mainly responsible for dealing with stateful processing.
@@
 
-\subsection{Service Deployment Model} \label{ssec:vcpe_deploy}
+\subsection{Service Deployment Model}\label{ssec:vcpe_deploy}
 
@@
 
-With architecure mentioned in \ref{ssec:service_design}, we come up with a network function service deployment model.
+With architecure mentioned in\ref{ssec:service_design}, we come up with a network function service deployment model.
 Because the algorithm and policies handled by computing infrastructures, and the generic network devices, that is, SDN switches, only do stateless processing.
@@
 
-In figure \ref{fig:vcpe_deploy} illustrated the service deployment model, each green area is a local network domain of customer.
+In figure\ref{fig:vcpe_deploy} illustrated the service deployment model, each green area is a local network domain of customer.
 At the gateway of this domain, there's a SDN-enabled switch.
 The customer can subscribe to our vcpe service through our vcpe dashboard.
-after subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed.
+After subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed.
 The customer only need to setup the gateway SDN switch to connect the SDN controller by the OpenFlow protocol, then the switch will handle these service.
 
-\subsection{Architecture of the vCPE system} \label{ssec:vcpe_archi}
+\subsection{Architecture of the vCPE system}\label{ssec:vcpe_archi}
 \subsubsection{System Overview}
@@
 
-The architecture as shown in Fig \ref{fig:vcpe_system} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
+The architecture as shown in Fig\ref{fig:vcpe_system} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
 The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers running on virtual machines hosting in the cloud using Amazon Web Services (AWS) Data Center also the Infrastructure Controller is a powerful physical blade server running in our laboratory.
@@
 When the infrastructure controller once create the container, the remote module will run up initiallly, waiting request from VNF VNF Orchestrator.
-The details of SDN controller desgin will be presented at section \ref{ssec:vcpe_services}
+The details of SDN controller desgin will be presented at section\ref{ssec:vcpe_services}
 
@@
 
-\section{Virtual CPE Services} \label{ssec:vcpe_services}
+\section{Virtual CPE Services}\label{ssec:vcpe_services}
+\subsection{Multiple Flow Flow Tables}
 

### 2017-02-20 paper.tex
add decription of multi-table

--- 2017-02-16 paper.tex
@@
 % cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% version 5.0 (2009-03-20) and later if using hype rref.sty.
 % The latest version can be obtained at:
@@
 
-\subsection{vCPE Service Design Overview} \label{ssec:service_design}
+\subsection{vCPE Service Design Overview}\label{ssec:service_design}
 \begin{figure}[!t]
   \centering
-  \includegraphics[width=3in]{./figures/system_overview_v2}
+  \includegraphics[width=3in]{./figures/service_design_overview}
   \caption{vCPE Service Design Architecture}
@@
 \end{figure}
-With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig.
+With the concept of SDN-enabled \cite{sdn-enabled} VNFs in Fig.
 \ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures.
@@
 The customer can subscribe to our vcpe service through our vcpe dashboard.
-after subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed.
+After subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed.
 The customer only need to setup the gateway SDN switch to connect the SDN controller by the OpenFlow protocol, then the switch will handle these service.
 
-\subsection{Architecture of the vCPE system} \label{ssec:vcpe_archi}
+\subsection{Architecture of the vCPE system}\label{ssec:vcpe_archi}
 \subsubsection{System Overview}
@@
 
-\section{Virtual CPE Services} \label{ssec:vcpe_services}
+\section{vCPE Services}\label{ssec:vcpe_services}
+\subsection{Multiple Flow Flow Tables Strategy}
+In subection \ref{ssec:service_design}, the vCPE service design architecture have been introduced.
+The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway.
+The controller transform the network functions to series of OpenFlow rules and send rules requests to SDN switch.
+Following the command from controller, the SDN switch insert rules to flow tables, checks incoming packets against the flow entry match fields, excute the actions in matching rules.
+The flow tabe defines all matching and processing, playing an important role to executive network function.
+Since the restricttion of single table have been discussed in \cite{onf-multi-tables}, we use multiple flow tables strategy to implement our vCPE service.
+
+In multiple flow tables strategy, the most important question is: which flow table should we insert rules into?
+We use the network function as a demarcation, that is, SDN applications which are responsible for specific network functions will only insert rules to one specific flow table.
+So we can focus on the design of the network function itself.
+In this way, howerver, the order of flow table become crucial.
+Should we put flow table of this network function at first, or the other?
+The answer is about the type of match and action in the rules generated by the network function.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/multi-table-sequence}
+\caption{The flow table order of our vCPE service}
+\label{fig:table-seq}
+\end{figure}
+
+The network functions of our vCPE services including Forwarding, Firewall, NAT, DHCP and QoS.
+We have determined the order of each function, shown in \ref{fig:table-seq}.
+In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decistion of the order of flow tables.
+
+\subsection{Forwarding}
+\subsection{Firewall}
+\subsection{NAT}
+\subsection{DHCP}
+\subsection{QoS}
 

### 2017-02-23 paper.tex
before 3

--- 2017-02-20 paper.tex
@@
 % First paragraph of paper need be big Alhabet
-% \section{Introduction}
-% \IEEEPARstart{T}{his}
+\section{Introduction}
+\IEEEPARstart{T}{his} document is a template for Microsoft Word versions 6.0 or later. If you are reading a paper or PDF version of this doconference. (By Eric)
+
+\section{Related Work}
+(By Eric)
 
@@
 \section{vCPE System Overview}
-Our object is to demonstrate that our vCPE system can help the telco to reduce the Capex and Opex when deploying, maintaining and updating CPE service.
-This section describes our vCPE system architecture and how we achieve our goal.
-In the subsection\ref{ssec:service_design}, we will introduce the overview architecture of our virtual CPE Service.
-Then in subsection\ref{ssec:vcpe_deploy}, we will explain that through the advantages of service architecture, our vCPE system can deploy our service to the customer easily.
-In the subsection\ref{ssec:vcpe_archi}, we will give details of the whole vCPE system.
-
-\subsection{vCPE Service Design Overview}\label{ssec:service_design}
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=3in]{./figures/service_design_overview}
-  \caption{vCPE Service Design Architecture}
-\label{fig:service_overview}
-\end{figure}
-With the concept of SDN-enabled\cite{sdn-enabled} VNFs in Fig.\ref{fig:service_overview}, the network functions have been achived by the synergies between compute and network infrastructures.
+\subsection{Overview of Network Function}\label{ssec:nfv_overview}
+With the concept of SDN-enabled\cite{sdn-enabled} VNFs, SDN technology work not only a for traffic steering but also as a part of network functions.
+In this idea, network function have been achieved by the synergies between compute and network infrastructures.
 The former is a VNF controller, mainly responsible for dealing with stateful processing.
@@
 \subsubsection{Stateful Processing component (VNF controller in container)}
-This component have to perform more complex algorithm, keep the state associated with the VNF and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component, since software is good at these tasks.
-We use SDN controller to implement the NFV controller and it's worth noting that we use southbound APIs of SDN controller to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
+This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
+We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
 
@@
 Stateless processing component, are implemented by SDN datapath resources, which is optimized for data plane traffic processing.
-Since SDN datapath have decoupled the control plane and data plane, so it can accept the control message from the stateful processing component.
+Since SDN switch have decoupled the control plane and data plane, so it can accept the control message from the stateful processing component.
 
@@
 If we want to update our service, we just need to update the statful component, since the stateless component just follow the command from stateful components.
+
+\begin{figure}[!t]
+\centering
+\caption{Overview of network function}
+\includegraphics[width=3in]{./figures/nfv_overview}
+\label{fig:nfv_overview}
+\end{figure}
 
@@
 
-With architecure mentioned in\ref{ssec:service_design}, we come up with a network function service deployment model.
-Because the algorithm and policies handled by computing infrastructures, and the generic network devices, that is, SDN switches, only do stateless processing.
-The customer only need to buy a general SDN switch at their home gateway and subscribe different NFV controller through our vCPE platform, they will have a different network function service.
+With architecture mentioned in \ref{ssec:nfv_overview}, we come up with a network function service deployment model.
+Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different NFV controller through our vCPE platform.
 
-In figure\ref{fig:vcpe_deploy} illustrated the service deployment model, each green area is a local network domain of customer.
-At the gateway of this domain, there's a SDN-enabled switch.
-The customer can subscribe to our vcpe service through our vcpe dashboard.
+Figure \ref{fig:vcpe_deploy} illustrates the service deployment model.
+Each green area is a local network domain of customer.
+At the gateway of this domain, there’s a SDN-enabled switch.
+The customer can subscribe to our vCPE service through our dashboard.
 After subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed.
@@
 
-\subsection{Architecture of the vCPE system}\label{ssec:vcpe_archi}
+\subsection{Architecture of the vCPE framework}
 \subsubsection{System Overview}
@@
 \centering
-\includegraphics[width=3in]{./figures/system_overview_v2}
-\caption{Service Syetem Overview}
-\label{fig:vcpe_system}
+\includegraphics[width=3in]{./figures/vcpe_framework_overview}
+\caption{Overview of vCPE framework}
+\label{fig:vcpe_framework}
 \end{figure}
 
-The architecture as shown in Fig\ref{fig:vcpe_system} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
-The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers running on virtual machines hosting in the cloud using Amazon Web Services (AWS) Data Center also the Infrastructure Controller is a powerful physical blade server running in our laboratory.
+The architecture as shown in Fig \ref{fig:vcpe_framework} including of a Infrastructure Controller,
+% Fig lable to change
+Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
+The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
 Each component is introduced in the subsection below.
@@
 \subsubsection{Infrastructure Controller}
-% shipyard
-The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images.
-The infrastructure does'nt handle the customer authentication or maintaining the state of running service, it just follow the request from the infrastrcure orchestrator to create, delete, start, stop and inspect containers.
+The infrastructure controller is a composed Docker management server
+with the ability to manage the Docker resources like containers and images.
+The infrastructure doesn't handle the customer authentication or maintaining the state of running service,
+it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
 
 \subsubsection{Infrastructure Orchestrator}
-% api server
-The infrasctructure orchestrator plays the key role of our system.
+The infrastructure orchestrator plays the key role of our system.
 It connecting and automating of workflows when we deploy our services.
-When a customer subscribes, the infrasctructure orchestrator authenticates the customer first, next it will call the infrastructure controllerto create a container for this customer, and update information in database afterwards.
-It handle the entire lifecycle of our vCPE service.
+When a customer subscribes, the infrastructure orchestrator authenticates the customer first,
+next it will call the infrastructure controller to create a container for this customer,
+and update information in database afterwards. It handle the entire lifecycle of our vCPE service.
 
 \subsubsection{Cloud Database}
-%
-The cloud database is used for restoreing the of our vCPE services, which include each customer's credential, customer's container settings and virtual CPE service states.
+The cloud database is used for restoring the of our vCPE services,
+which include each customer’s credential, customer’s container settings and virtual CPE service states.
 The cloud database is using PostgreSQL, which is a open source, easily customized and object-relational database system.
-Only Infrastructure Orchestrator has read and write permissions to access cloud database.
+Only Infrastructure Orchestrator has permissions to access cloud database.
 
 \subsubsection{VNF Controllers}
-% sdn controller
-
 VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module.
@@
 We built a light-weight server as a launcher module to resolve the remotely execution issue.
-The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand.
-When the infrastructure controller once create the container, the remote module will run up initiallly, waiting request from VNF VNF Orchestrator.
-The details of SDN controller desgin will be presented at section\ref{ssec:vcpe_services}
+The remote launcher module monitor the SDN controller process ID (PID)
+and properly kill the SDN controller process ID when on demand.
+When the infrastructure controller once create the container, the remote module will run up initially, waiting request  from VNF Orchestrator.
+The details of SDN controller design will be presented at section \ref{sec:nf_mft}.
 
 \subsubsection{VNF Orchestrator}
-% web server
-The VNF Orchestrator is a Web application server hosting on Amazon Web server, being online for customer and provide a dashboard for virtual CPE and containers management and configuration.
+The VNF Orchestrator is a Web application server hosting on Amazon Web server,
+being online for customer and provide a dashboard for virtual CPE and containers management and configuration.
 
-Through the web UI provided by the VNF Orchestrator, the customers can subscribe to the desired service and without typing any command via the command line interface (CLI).
-After receiving the subscribing message, the VNF orchestrator will request the infrastructure orchestrator to create a new VNF controller, and then send the virtual CPE configuration to the new VNF controller.
-Based on configuration demands under different conditions, the network administrator is able to select any of the listed services on the dashboard such as NAT, DHCP, Firewall and QoS management.
+Through the web UI provided by the VNF Orchestrator,
+the customers can subscribe to the desired service and without typing any command via the command line interface (CLI).
+After receiving the subscribing message, the VNF orchestrator will request the infrastructure orchestrator to create a new VNF controller,
+and then send the virtual CPE configuration to the new VNF controller.
+Based on configuration demands under different conditions,
+the network administrator is able to select any of the listed network functions on the dashboard
+such as Firewall, NAT, DHCP and QoS management.
+
+\subsection{Network Functions}
+\subsubsection{Firewall}
+The firewall service could filter the packets based on packet header fields, including MAC address, IP, and layer4 protocols.
+The network manager can add new rules or remove rules to the access control list through our vCPE GUI.
+
+\subsubsection{NAT}
+The NAT service is a network function that can remap  IP address to another one.
+The Source NAT (SNAT) is typically used by internal users (inside private network) to access the Internet (outside network).
+The network function uses the action “Set-Field”, which defined by OpenFlow protocol for rewriting packet header fields.
+Via vCPE GUI interface, the network manager can set up the WAN port of SDN switch,
+public IP, default gateway, and local network address when using this function.
+
+\subsubsection{DHCP}
+% The DHCP Service automatically provide the IP address to DHCP client.
+% To implement the function, the controller handle the DCHP packets ( UDP protocol with source port 68 and destination port67)
+% and the workflow is as following:
+% (1) Waiting for DHCP client send DHCP discover request.
+% (2) DHCP server (SDN controller) generate DHCP offer packet and send IP address to DHCP client.
+% (3) Server Receive the DHCP request from client, and then generate the DHCP acknowledgement send to client.
+
+\subsubsection{Forwarding}
+Forwarding Service is a basic service that forward traffic to its destination
+and we use the Mac address learning concept to implement our forwarding function.
+
+\subsubsection{QoS}
+Quality of Service (QoS) are always used to control the traffic flows of a network
+and prevent the traffic to exceed the network capacity and cause traffic congestion.
+Therefore we implement the bandwidth management using meter
+which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
+Beside achieving network functions virtualization with SDN technology,
+we also make the network administrator manage and monitor a network more easily.
+As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
+In this paper, our QoS integrates with a flow classification engine
+and offers the three ways of bandwidth management:
+\begin{itemize}
+\item For a specific host..
+\item For a specific host.
+\item For a specific application from a host or a domain.
+\end{itemize}
+
+\subsection{Application Identification}
+Application identification is to identify each flow
+as an application name to enable QoS management system to do bandwidth control or distribution at application level.
+A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
+Applications include desktop applications, native mobile applications, and web applications,
+such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
+We use supervised machine learning and a method based on inspecting domain name service (DNS) responses to do flow classification.
+After application identification system classifies a flow as an application name,
+it sends the classification result to a server with database.
+The server stores the classification result into database, and waits for query with 5-tuple from QoS management system.
+The detail will be described in section \ref{sec:app_classification}.
+
+\section{Network function with multiple table management model}\label{sec:nf_mft}
+\subsection{Multiple Flow Tables Strategy}
+In subsection \ref{ssec:nfv_overview}, the vCPE service design architecture have been introduced.
+The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway.
+The controller transform the network functions to series of OpenFlow rules requests and send to SDN switch.
+Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules.
+The flow table defines all matching and corresponding processing, thus playing an important role to executive network function.
+
+Since the flow table is crucial component, and we find that single table binds us to implement our network functions.
+The \cite{onf-multi-tables} also mentioned two condition for single table is too restrictive.
+The first is a single packet need to perform independent actions based on matching different fields.
+The second is that the packet needs two-stage processing.
+Involves into both situation, our network functions implemented by multiple flow tables strategy.
+
+In multiple flow tables strategy, the most important question is: which flow table should we insert rules into?
+We use the network function as a demarcation, that is, SDN applications which are responsible for specific network functions will only insert rules to one specific flow table, so we can focus on the design of the network function itself.
+In this way, however, the order of flow table become crucial.
+Should we put this network function at first, or the other?
+The answer is about the type of match and action in the rules generated by the network function
+
+The network functions of our vCPE services including Forwarding, Firewall, NAT, DHCP and QoS.
+We have determined the order of each function, shown in \ref{fig:table-seq}.
+In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.
 
@@
 \centering
-\includegraphics[width=3in]{./figures/vnf_orche_view}
-\caption{Virtual CPE Dashboard User Interface for Container Management}
-\label{fig:vcpe_dashboard}
+\includegraphics[width=3in]{./figures/multi_table}
+\caption{The flow table order of our vCPE service}
+\label{fig:table-seq}
 \end{figure}
 
-\section{Virtual CPE Services}\label{ssec:vcpe_services}
-\subsection{Multiple Flow Flow Tables}
+\subsection{Service Control}
+Service control is used to enable or disable service.
+To enable a service, we need to modify the table-miss rule.
+We always put a packet-in rule in the table of the last active service as a table-miss in case that there isn't any corresponding rule.
+To make our service chain possible, the rules of each service except the last service contains an additional action, go to next table, so the packets can continue to pass through all active services.
+
+To disable a service, we not only need to modify the table-miss rule but also have to add an enforce rule.
+Each enforce rules has maximum priority and the action is goto next table.
+It means that packets will still pass through the disabled service's table, and the only thing they do in this table is ignoring other rules and go to next table.
+
+\subsection{Firewall}
+
+Firewall service is able to block traffic dynamically, and in this service, the packets will not cause any packet-in event.
+On the dashboard, we can specify the blocking policies. There are 4 kinds of policies:
+\begin{itemize}
+\item Block any traffic from a certain source IP.
+\item Block all traffic to a certain destination IP.
+\item Block traffic based on known layer 4 protocols, such as SSH, HTTP, etc.
+\item Block traffic to any layer 4 ports of a host.
+\end{itemize}
+
+For different policies, the controller applies corresponding rules to the SDN switch.
+After the policies are set, the blocking rules will be installed immediately.
+Then any traffic that hit the blocking rules will be dropped.
+For normal traffic, they will not be affected.
+
+As shown in Table  , all the actions of flow entries are drop.
+The 1st rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
+The 2nd rule shows the flow entry would block the Telnet protocol.
+
+In our multiple table model, the firewall service is located in the table 1, since once packets are caught by the blocking rules, they doesn't need to apply any other services.
+The packets which match the rules will be dropped immediately, and their journey in the flow table ends here.
+To other no-blocked packets, they pass all blocking rules and finally match the table-miss rule, which will let the packets go on the next table.
+The action of firewall is different from other services, since in other services, no matter what actions are taken to the packets, the packets have to go to the next table
+
+\begin{table*}[]
+\centering
+\caption{Firewall table entry}
+\label{table:firewall}
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+IP proto         & IP Src     & IP Dst & L4 sport & L4 dport & Action                                                                              \\ \hline
+TCP        192.168.2.1        & * & *         & 22     & 2000     & \begin{tabular}[c]{@{}l@{}}IP Dst $\,\to\,$ 192.168.8.40; \\ L4 dport $\,\to\,$ 5566\end{tabular} \\ \hline
+140.114.71.178 & 10.10.10.1 & TCP         & 8976     & 2001     & \begin{tabular}[c]{@{}l@{}}IP Src $\,\to\,$ 192.168.8.80; \\ L4 sport $\,\to\,$ 6979\end{tabular}   \\ \hline
+\end{tabular}
+\end{table*}
+
+\subsection{DHCP}
+\subsection{NAT}
+\subsection{QoS}
+\subsection{Forwarding}
+
+\section{Application Identifier method} \label{sec:app_classification}
 

### 2017-02-23 paper.tex
class

@@
 \subsubsection{System Overview}
+
 \begin{figure}[!t]
@@
 \subsubsection{DHCP}
-% The DHCP Service automatically provide the IP address to DHCP client.
-% To implement the function, the controller handle the DCHP packets ( UDP protocol with source port 68 and destination port67)
-% and the workflow is as following:
-% (1) Waiting for DHCP client send DHCP discover request.
-% (2) DHCP server (SDN controller) generate DHCP offer packet and send IP address to DHCP client.
-% (3) Server Receive the DHCP request from client, and then generate the DHCP acknowledgement send to client.
+DHCP service allocates IP addresses to hosts dynamically.
+To implement the function, the SDN controller cope with UDP packets which use port 67 and 68.
+It generates DHCP offer and DHCP acknowledge to reply DHCP discovery and DHCP request received from the hosts.
 
@@
 \centering
-\includegraphics[width=3in]{./figures/multi_table}
+\includegraphics[width=3in]{./figures/multiple_table}
 \caption{The flow table order of our vCPE service}
@@
 \subsection{Firewall}
-
 Firewall service is able to block traffic dynamically, and in this service, the packets will not cause any packet-in event.
@@
 
-As shown in Table  , all the actions of flow entries are drop.
+As shown in Table \ref{table:fw}, all the actions of flow entries are drop.
 The 1st rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
@@
 \centering
-\caption{Firewall table entry}
-\label{table:firewall}
+\caption{Firewall rules in Flow Entry}
+\begin{threeparttable}
+\label{table:fw}
 \begin{tabular}{|l|l|l|l|l|l|}
@@
 IP proto & IP Src      & IP Dst       & L4 sport & L4 dport & Action \\ \hline
-TCP        192.168.2.1        & * & *         & 22     & 2000     & \begin{tabular}[c]{@{}l@{}}IP Dst $\,\to\,$ 192.168.8.40; \\ L4 dport $\,\to\,$ 5566\end{tabular} \\ \hline
-140.114.71.178 & 10.10.10.1 & TCP         & 8976     & 2001     & \begin{tabular}[c]{@{}l@{}}IP Src $\,\to\,$ 192.168.8.80; \\ L4 sport $\,\to\,$ 6979\end{tabular}   \\ \hline
+TCP      & 192.168.2.1 & *            & *        & 22       & Drop   \\ \hline
+TCP      & *           & *            & *        & 23       & Drop   \\ \hline
+
+\end{tabular}
+\begin{tablenotes}
+  \small
+  \item Symbol * represents wildcard (match any value).
+\end{tablenotes}
+\end{threeparttable}
+\end{table*}
+
+\subsection{DHCP}
+
+\subsection{NAT}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/nat_illustrate}
+\caption{Illustration of NAT service}
+\label{fig:nat_illustration}
+\end{figure}
+The NAT service could allow a lot of hosts to use one public IP address to connect the network.
+In order to achieve this thing, SDN controller have to set the packet header filed.
+Because the SDN switch would set the field, the first packet have to go to controller.
+And controller would add the flow to SDN switch, after that the packet would not go to controller.
+It can decrease the burdens of the controller.
+
+Below is a examples to show how the NAT service modify the IP address and port number,
+as shown in Fig \ref{fig:nat_illustration}.
+
+For outgoing packet, SDN switch doesn’t have any flow entry in flow table,
+so the Packet-in event will be triggered at the beginning.
+The packet that is sent by private network host will be sent to SDN controller,
+and the packet header fields are modified by Set-Field action.
+The source IP address and source port number of outgoing packet will be modified to public IP address
+and remaped a new port number for NAT.
+For ingoing packet, the destination IP and destination port number are modified to fit private IP and port number.
+And then SDN controller add these flow entries to SDN switch, it can’t avoid that all the packet sent to controller.
+Fig.
+\ref{fig:nat_illustration} show the public IP address of NAT is 140.114.71.178 and a host private IP is 192.168.8.254 and port number 7878.
+The client sent the packet to a server with IP address 140.114.71.177 and port number 9898.
+
+As shown in Table \ref{table:nat}, when host sent the packet to server (outgoing),
+the Packet-in will be trigger, and then packet to controller.
+The Set-Field action would modify the Source IP to public IP address of NAT is 140.114.71.178 and source port to 2000.
+when the server sends back to the client (ingoing), the packet header field would be modified.
+The destination IP address and destination port number would be modified to 192.168.8.254 and 7788.
+
+\begin{table*}[]
+\centering
+\caption{Flow entry for modifying the packet header fields of packets}
+\label{table:nat}
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+            &IP Src          & IP Dst          & L4 src port  & L4 dst port & Action                                                                            \\ \hline
+1. outgoing &192.168.8.254   &140.114.71.177   & 7878         & 9898        & \begin{tabular}[c]{@{}l@{}}IP Src $\,\to\,$ 140.114.71.178; \\ L4 src port $\,\to\,$ 2000\end{tabular} \\ \hline
+2. ingoing  &140.114.71.177  &140.114.71.178   & 9898         & 2000        & \begin{tabular}[c]{@{}l@{}}IP Dst $\,\to\,$ 192.168.8.254; \\ L4 dst port $\,\to\,$ 7878\end{tabular} \\ \hline
 \end{tabular}
@@
 
-\subsection{DHCP}
-\subsection{NAT}
+In the single table framework, we have to add the two rules to SDN switch to match the outgoing and ingoing situation.
+At the first, we predict the NAT service to be put one the last table in the multiple table framework.
+Because the NAT service need to set the packet header fields and play a role of connection to the outside network.
+And the most important thing is that the SDN switch is according to order of table to match.
+We have to consider the outgoing and ingoing situations.
+As a result of all the above factors combined,
+the NAT service is located at the first and the last table in our multiple table framework.
+
 \subsection{QoS}
 \subsection{Forwarding}
+In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule.
+When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address.
+With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again.
+The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.
+
+In order to gather per-session statistics information, 5-tuple rules are needed.
+This is why we don’t add rules  based on mac address.
+The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
+In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
 
 \section{Application Identifier method} \label{sec:app_classification}
+In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
+In other words, the system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
+We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
+Except for DNS responses, the system only analyzes transport layer information of packets without inspecting their payload
+
+\subsection{Architecture of our application identification system}
+There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig \ref{fig:classifcation_training} and Fig \ref{fig:classifcation_classifying} respectively.
+These architectures can be integrated, and do training and classifying in the same time.
+The detail will be mentioned in the following paragraph
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/classification_training}
+\caption{Architecture of our application identification system in training phase}
+\label{fig:classifcation_training}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/classification_classifying}
+\caption{Architecture of our application identification system in classifying phase}
+\label{fig:classifcation_classifying}
+\end{figure}
+
+\subsection{Overall procedure of application identification}
+In training phase, we generate some data needed by ML and the method based on inspecting DNS responses.
+In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify; otherwise, we use ML to classify.
+
+\subsection{Procedure of Supervised ML in our system}
+In training phase, the architecture is show in Fig I.
+Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes.
+Trainer is to analyze traffic from mirror port to get flow attributes.
+After Trainer finishes calculating flow attributes of a flow, it gets ground truth of the flow from Scanner or App Meta Server to generate training data, and sends training data to flow classification engine.
+App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
+Scanner is to get mappings of 5-tuple and ground truth from OS.
+In classifying phase, the architecture is shown in Fig.
+Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier.
+Classifier is to analyze traffic from mirror port to get flow attributes.
+After Classifier finishes calculating flow attributes of a flow, it use flow attributes to ask flow classification engine for classification result if needed.
+
+\subsection{Flow attributes we adopted in ML}
+In ML, when system calculates flow attributes, we only use transport layer information of packets which have payload.
+We use Application Round (APPR) proposed by [] to analyze flow behavior.
+We use number of packets, packet sizes, transmission time, transmission direction, throughput, and APPR to define flow attributes.
+There are 69 attributes in total, as defined in our previous work [].
+
+\subsection{Algorithms we adopted in ML}
+We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato.
+We call Weka Java API to build classification model.
+We use three algorithms, namely RandomSupSpace with RandomTree [], FilterClassifier with discretization and RandomTree [], and RandomCommittee with RandomTree [].
+
+\subsection{Procedure of a method based on inspecting DNS response in our system}
+In training phase, we collect the mappings of server IP and application name.
+A mapping of server IP and application name means the application has ever establish connection with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
+In classifying phase, we only use those mappings which have been used by one application to classify.
+When system detect a flow, we check whether source IP or destination IP of the flow match any server IP of those mappings.
+If it matches any server IP, we regard corresponding application name as classification result; otherwise, we use flow attributes of the flow and classification model to classify.
+
+\section{Performance Evaluation}
+\subsection{Multiple Table Performance}
+
+\subsection{Accuracy of Application Identification }
+
+\subsubsection{Testing data set}
+Testing data set are mappings of flow attributes and ground truth (also called rules).
+This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan in 2016.
+We manually operated applications to generate traffic.
+After the system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on the testing data set.
+There are 14659 rules in total, and there are 137 applications if we view each platform version of an application as one application.
+(提fig 1)
+
+\subsubsection{Validation method}
+Although the system can do online training and classifying, we do offline training and classifying.
+More specifically, when we did online training to analyze traffic, get ground truth, and export the rules into a file.
+We do 10-fold cross validation on the rules.
+There are 10 rounds in 10-fold cross validation.
+Each round, we split testing data set into training dataset and classifying dataset.
+
+\subsubsection{Mapping of category names}
+We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
+The main reason is that some application have different ground truth in different operating system.
+
+\subsubsection{Accuracy matrices}
+To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq.
+(1), Eq.
+(2), and Eq.
+(3) [].
+In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category.
+After ten rounds, we calculate average
+
+%%
 

### 2017-02-23 paper.tex
add dhcp

@@
 \subsection{DHCP}
+DHCP service implements DHCP protocol to dynamically assign IP addresses to hosts.
+DHCP operation uses UDP protocol. The clients use port 68 as the source port and 67 as the destination port.
+On the contrary, the server use port 67 as the source port and 68 as the destination port.
+Our system is able to handle these packets  to realize DHCP service.
+
+The service follows these steps:
+\begin{enumerate}
+\item The controller adds a DHCP rule for DHCP packets when the service is enabled.
+\item All packets match this DHCP rule cause packet-in.
+\item The controller checks if a packet is a DHCP discovery packet.
+  \begin{enumerate}
+    \item If so, the controller assigns an IP address, and generate a DHCP offer then do packet-out.
+    \item If not, the controller then checks whether it's a DHCP request. If the result is positive, the controller generate a DHCP acknowledge then do packet-out.
+  \end{enumerate}
+\end{enumerate}
+
+Our system support multitable, but a specific table for DHCP service is not required.
+The reason is that only one rule will be installed for all hosts who request for DHCP service.
+When the service is disabled, the DHCP rule will be deleted,
+and the packets will continue to pass through our service chain.
+Following DHCP packets can reach other DHCP servers without entering our service chain
+since our controller will automatically flood out broadcast packets.
 

### 2017-02-23 paper.tex
nat

@@
 % \setlength{\columnsep}{10mm}
-% \setlength{\textwidth}{180mm}
+% \setlength{\textwidth}4.0180mm}
 % \setlength{\textheight}{250mm}
@@
 
-% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not adjust lengths that control margins, column widths4.0 etc. ***
 % *** Do not use packages that alter fonts (such as pslatex).         ***
@@
 %\centering
-%\includegraphics[width=2.5in]{myfigure}
+%\includegraphics[width=4.0.5in]{myfigure}
 % where an .eps filename suffix will be assumed under latex,
@@
 % \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a
-% line do not exceed the text width or a line break will occur.
+% Watch out that the combined width 4.0f all the subfigures on a
+% line do not exceed the text width 4.0r a line break will occur.
 %
@@
 %\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+%\subfloat[Case I]{\includegraphics[width=4.0.5in]{box}%
 %\label{fig_first_case}}
 %\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+%\subfloat[Case II]{\includegraphics[width=4.0.5in]{box}%
 %\label{fig_second_case}}
@@
 \caption{Overview of network function}
-\includegraphics[width=3in]{./figures/nfv_overview}
+\includegraphics[width=4.0in]{./figures/nfv_overview}
 \label{fig:nfv_overview}
@@
 \centering
-\includegraphics[width=3in]{./figures/deployment}
+\includegraphics[width=4.0in]{./figures/deployment}
 \caption{Service Deployment Model}
@@
 \centering
-\includegraphics[width=3in]{./figures/vcpe_framework_overview}
+\includegraphics[width=4.0in]{./figures/vcpe_framework_overview}
 \caption{Overview of vCPE framework}
@@
 and prevent the traffic to exceed the network capacity and cause traffic congestion.
-Therefore we implement the bandwidth management using meter
-which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
-Beside achieving network functions virtualization with SDN technology,
+Therefore we implement the bandwidth 4.0anagement using meter
+which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.4.0Beside achieving network functions virtualization with SDN technology,
 we also make the network administrator manage and monitor a network more easily.
@@
 In this paper, our QoS integrates with a flow classification engine
-and offers the three ways of bandwidth management:
+and offers the three ways of bandwidth 4.0anagement:
 \begin{itemize}
@@
 Application identification is to identify each flow
-as an application name to enable QoS management system to do bandwidth control or distribution at application level.
+as an application name to enable QoS management system to do bandwidth 4.0ontrol or distribution at application level.
 A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
@@
 \centering
-\includegraphics[width=3in]{./figures/multiple_table}
+\includegraphics[width=4.0in]{./figures/multiple_table}
 \caption{The flow table order of our vCPE service}
@@
 \centering
-\includegraphics[width=3in]{./figures/nat_illustrate}
+\includegraphics[width=4.0in]{./figures/nat_illustrate}
 \caption{Illustration of NAT service}
@@
 The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
-In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
+In this way, we can get the real-time bandwidth 4.0tatistics of each connection by just subtracting the byte count from byte count of last second.
 
 \section{Application Identifier method} \label{sec:app_classification}
-In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
+In order to let QoS management system be able to control or distribute bandwidth 4.0t application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
 In other words, the system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
@@
 \centering
-\includegraphics[width=3in]{./figures/classification_training}
+\includegraphics[width=4.0in]{./figures/classification_training}
 \caption{Architecture of our application identification system in training phase}
@@
 \centering
-\includegraphics[width=3in]{./figures/classification_classifying}
+\includegraphics[width=4.0in]{./figures/classification_classifying}
 \caption{Architecture of our application identification system in classifying phase}
@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=4.0in]{./figures/nat_evaluation}
+\caption{Multiple Table Performance Evaluation Scenario}
+\label{fig:nat_evaluation}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=4.0in]{./figures/nat_evaluation_result}
+\caption{Result of Multiple Table Performance Evaluation}
+\label{fig:nat_evaluation_result}
+\end{figure}
+
+The single table framework implementation is easier than multiple table framework, but the multiple table framework is more flexible.
+To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
+To begin with, an overview of the experiment environment illustrated in Fig.
+\ref{fig:nat_evaluation}.
+In this experiment, the controller is Ryu SDN controller, and run on the Dell PowerEdge R630 Rack Server.
+The SDN switch employ Pica8 P-3290 switch.
+We used the tool that iPerf2.0 could generate the network traffic.
+The iPerf server would be set a public IP address.
+And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
+We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth 4.0t 100Mbps.
+These experiments would use diffrent payload sizes to inspect their performances.
+As shown in Fig.
+\ref{fig:nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
+Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.
+We can see that the throughput value of multiple table framework is close to single table framework.
+So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other.
+
 \subsection{Accuracy of Application Identification }
-
 \subsubsection{Testing data set}
@@
 Each round, we split testing data set into training dataset and classifying dataset.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=4.0in]{./figures/classification_classifying}
+\caption{Architecture of our application identification system in classifying phase}
+\label{fig:classifcation_evaluation}
+\end{figure}
 

### 2017-02-23 paper.tex
blah

@@
 % \setlength{\columnsep}{10mm}
-% \setlength{\textwidth}4.0180mm}
+% \setlength{\textwidth}2.5180mm}
 % \setlength{\textheight}{250mm}
@@
 
-% *** Do not adjust lengths that control margins, column widths4.0 etc. ***
+% *** Do not adjust lengths that control margins, column widths2.5 etc. ***
 % *** Do not use packages that alter fonts (such as pslatex).         ***
@@
 %\centering
-%\includegraphics[width=4.0.5in]{myfigure}
+%\includegraphics[width=2.5.5in]{myfigure}
 % where an .eps filename suffix will be assumed under latex,
@@
 % \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width 4.0f all the subfigures on a
-% line do not exceed the text width 4.0r a line break will occur.
+% Watch out that the combined width 2.5f all the subfigures on a
+% line do not exceed the text width 2.5r a line break will occur.
 %
@@
 %\centering
-%\subfloat[Case I]{\includegraphics[width=4.0.5in]{box}%
+%\subfloat[Case I]{\includegraphics[width=2.5.5in]{box}%
 %\label{fig_first_case}}
 %\hfil
-%\subfloat[Case II]{\includegraphics[width=4.0.5in]{box}%
+%\subfloat[Case II]{\includegraphics[width=2.5.5in]{box}%
 %\label{fig_second_case}}
@@
 \caption{Overview of network function}
-\includegraphics[width=4.0in]{./figures/nfv_overview}
+\includegraphics[width=2.5in]{./figures/nfv_overview}
 \label{fig:nfv_overview}
@@
 \centering
-\includegraphics[width=4.0in]{./figures/deployment}
+\includegraphics[width=2.5in]{./figures/deployment}
 \caption{Service Deployment Model}
@@
 \centering
-\includegraphics[width=4.0in]{./figures/vcpe_framework_overview}
+\includegraphics[width=2.5in]{./figures/vcpe_framework_overview}
 \caption{Overview of vCPE framework}
@@
 and prevent the traffic to exceed the network capacity and cause traffic congestion.
-Therefore we implement the bandwidth 4.0anagement using meter
-which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.4.0Beside achieving network functions virtualization with SDN technology,
+Therefore we implement the bandwidth 2.5anagement using meter
+which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.2.5Beside achieving network functions virtualization with SDN technology,
 we also make the network administrator manage and monitor a network more easily.
@@
 In this paper, our QoS integrates with a flow classification engine
-and offers the three ways of bandwidth 4.0anagement:
+and offers the three ways of bandwidth 2.5anagement:
 \begin{itemize}
@@
 Application identification is to identify each flow
-as an application name to enable QoS management system to do bandwidth 4.0ontrol or distribution at application level.
+as an application name to enable QoS management system to do bandwidth 2.5ontrol or distribution at application level.
 A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
@@
 \centering
-\includegraphics[width=4.0in]{./figures/multiple_table}
+\includegraphics[width=2.5in]{./figures/multiple_table}
 \caption{The flow table order of our vCPE service}
@@
 \centering
-\includegraphics[width=4.0in]{./figures/nat_illustrate}
+\includegraphics[width=2.5in]{./figures/nat_illustrate}
 \caption{Illustration of NAT service}
@@
 The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
-In this way, we can get the real-time bandwidth 4.0tatistics of each connection by just subtracting the byte count from byte count of last second.
+In this way, we can get the real-time bandwidth 2.5tatistics of each connection by just subtracting the byte count from byte count of last second.
 
 \section{Application Identifier method} \label{sec:app_classification}
-In order to let QoS management system be able to control or distribute bandwidth 4.0t application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
+In order to let QoS management system be able to control or distribute bandwidth 2.5t application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
 In other words, the system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
@@
 \centering
-\includegraphics[width=4.0in]{./figures/classification_training}
+\includegraphics[width=2.5in]{./figures/classification_training}
 \caption{Architecture of our application identification system in training phase}
@@
 \centering
-\includegraphics[width=4.0in]{./figures/classification_classifying}
+\includegraphics[width=2.5in]{./figures/classification_classifying}
 \caption{Architecture of our application identification system in classifying phase}
@@
 \centering
-\includegraphics[width=4.0in]{./figures/nat_evaluation}
+\includegraphics[width=2.5in]{./figures/nat_evaluation}
 \caption{Multiple Table Performance Evaluation Scenario}
@@
 \centering
-\includegraphics[width=4.0in]{./figures/nat_evaluation_result}
+\includegraphics[width=2.5in]{./figures/nat_evaluation_result}
 \caption{Result of Multiple Table Performance Evaluation}
@@
 And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
-We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth 4.0t 100Mbps.
+We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth 2.5t 100Mbps.
 These experiments would use diffrent payload sizes to inspect their performances.

### 2017-02-23 paper.tex
fix width fault

--- 2017-02-23 paper.tex
@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/nat_evaluation}
+\caption{Multiple Table Performance Evaluation Scenario}
+\label{fig:nat_evaluation}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/nat_evaluation_result}
+\caption{Result of Multiple Table Performance Evaluation}
+\label{fig:nat_evaluation_result}
+\end{figure}
+
+The single table framework implementation is easier than multiple table framework, but the multiple table framework is more flexible.
+To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
+To begin with, an overview of the experiment environment illustrated in Fig.
+\ref{fig:nat_evaluation}.
+In this experiment, the controller is Ryu SDN controller, and run on the Dell PowerEdge R630 Rack Server.
+The SDN switch employ Pica8 P-3290 switch.
+We used the tool that iPerf2.0 could generate the network traffic.
+The iPerf server would be set a public IP address.
+And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
+We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
+These experiments would use diffrent payload sizes to inspect their performances.
+As shown in Fig.
+\ref{nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
+Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.
+We can see that the throughput value of multiple table framework is close to single table framework.
+So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other.
+
 \subsection{Accuracy of Application Identification }
-
 \subsubsection{Testing data set}
@@
 Each round, we split testing data set into training dataset and classifying dataset.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/classification_classifying}
+\caption{Architecture of our application identification system in classifying phase}
+\label{fig:classifcation_evaluation}
+\end{figure}
 

### 2017-02-23 paper.tex
blah

@@
 \begin{itemize}
-\item For a specific host..
+\item For a specific host.
 \item For a specific host.
@@
 \centering
-\includegraphics[width=3in]{./figures/nat_evaluation}
+\includegraphics[width=3in]{./figures/nat_evaluation_scenario}
 \caption{Multiple Table Performance Evaluation Scenario}
@@
 To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
-To begin with, an overview of the experiment environment illustrated in Fig.
-\ref{fig:nat_evaluation}.
-In this experiment, the controller is Ryu SDN controller, and run on the Dell PowerEdge R630 Rack Server.
-The SDN switch employ Pica8 P-3290 switch.
-We used the tool that iPerf2.0 could generate the network traffic.
-The iPerf server would be set a public IP address.
-And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
-We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
+;;We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
 These experiments would use diffrent payload sizes to inspect their performances.
 As shown in Fig.
-\ref{nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
+\ref{fig:nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
 Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.

### 2017-02-23 paper.tex
qos 1,2

@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/multiple_table}
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=6in]{./figures/multiple_table}
 \caption{The flow table order of our vCPE service}
 \label{fig:table-seq}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{table*}[]
+\begin{table*}[!t]
 \centering
@@
 \subsection{QoS}
+QoS service is mainly for traffic control and we provide three management funtion for QoS service.
+We will introduce these three strategy first and then discuss the table order of QoS service in multiple table model.
+
+\subsubsection{Rate limitation of hosts}
+When some hosts take up a lot of bandwidth of network, it will make other hosts in slow speed or make traffic congestion.
+To prevent this, rate limiting is used to control the rate of traffic from a host.
+For implementing the host rate limitation, we create a meter for desired bandwidth first and then add a flow, of which match is host’s mac address and action is the meter we just created.
+
+The concept of this option is shown in Fig.
+\ref{fig:rate_host} and Table \ref{table:rate_host}.
+In T0, host 1 and host 2 are not limited yet.
+Since host 2 takes up a lot of bandwidth from network in T0~T1, the network administrator sets host 2 rate-limited under 400 Kbps.
+When controller receive this request, marked as (a), it will create a new meter  with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = HOST1 MAC and meter = 1.
+According to our flow table, it will limit the rate of the target host.
+Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately.
+The similar situation also occurs to Host 1 in T2.
+The administrator chooses to set Host1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/rate_host}
+\caption{Illustration of rate-limiting for a certain host}
+\label{fig:rate_host}
+\end{figure}
+
+% Table 1
+\begin{table*}[]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+Request  & Match                                             & Action                             \\ \hline
+(a)      & Destination MAC Address = MAC address of Host 1   & Goto Meter 1 (400Kbps), Next Table \\ \hline
+(b)      & Destination MAC Address = MAC address of Host 2   & Goto Meter 2 (600Kbps), Next Table \\ \hline
+\end{tabular}
+\caption{Flow entry for modifying the packet header fields of packets}
+\label{table:rate_host}
+\end{table*}
+
+\subsubsection{Rate limitation of applications}
+There are more and more network’s applications used such as online games, video streaming, conference call, etc.
+Therefore, there are massive traffic working in the network.
+Consequently, we integrate with a flow classification engine to identify the flow belongs which application is.
+However, an application may have many connections, we will equally distribute the bandwidth to each connection.
+
+For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine.
+If we want to limit this application to 1000Kbps.
+As Figure.
+\ref{fig:rate_app} and Table \ref{table:rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps.
+In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps.
+In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore.
+Whereas, the sum of bandwidth from this application is always being 1000Kbps.
+That is, the bandwidth will dynamically adjust basic on the algorithm 1 if we want to set the bandwidth of application to B Kbps and there are N connections from the application.
+The algorithm is shown as Algorithm 1.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/rate_app_algo}
+% \caption{Illustration of rate-limiting for a certain host}
+\label{fig:rate_app_algo}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/rate_app}
+\caption{Illustration of rate-limiting for a certain host}
+\label{fig:rate_app}
+\end{figure}
+
+% Table 2
+\begin{table*}[]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+Condition                                      & Meter Bandwidth                \\ \hline
+At T0, there are three connection initially.   & 1000 / 3 = 333 Kbps.           \\ \hline
+At T1, Two new connection (D, E) come up.      & 1000 / 5 = 200 Kbps.           \\ \hline
+At T2, A connection (E) is closed.             & 1000 / 4 = 250 Kbps.           \\ \hline
+\end{tabular}
+\caption{Meter bandwidth changing based on the number of application connections}
+\label{table:rate_app}
+\end{table*}
+
+\subsubsection{Rate limitation for a certain application of certain host}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/rate_host_app}
+\caption{Illustration of rate-limiting for a certain application of certain host}
+\label{fig:rate_app}
+\end{figure}
+
+\subsubsection{The table order of QoS service}
+QoS service is located at table 2, because the location of NAT/DHCP, firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
+Let's consider the scenario that we put the QoS table after the forwarding table.
+Plus, we have only two services enabled, forwarding and QoS, then suppose a host is not limited by QoS policies.
+The very first packet will not be affected in both arrangement.
+For the following packets, the difference can be observed.
+The packets which has matched the rules of the forwarding table will still cause packet-ins when they go to QoS table.
+This is not supposed to happen, since the host is not restrained by QoS policies and any packet-in increase the controller's load.
+To reduce the burden of the controller, we put QoS table ahead of forwarding table.
+In this scenario, all packets that pass through QoS table will continue to go to forwarding table without matching any QoS rules.
+Then the packets except the very first packet will just be forwarded by forwarding service instead of causing packet-ins.
+Hence the controller's load will decrease.
+To use our system, the forwarding service is necessary, so there is no such scenario that users enable QoS and disable forwarding.
+
 \subsection{Forwarding}
@@
 
-%%
-
 \newpage

### 2017-02-23 paper.tex
raw final

@@
 \begin{figure*}[!t]
+\label{fig:table-seq}
 \centering
@@
 \caption{The flow table order of our vCPE service}
-\label{fig:table-seq}
 \end{figure*}
@@
 \centering
-\caption{Firewall rules in Flow Entry}
 \begin{threeparttable}
@@
 \end{threeparttable}
+\caption{Firewall rules in Flow Entry}
 \end{table*}
@@
 \begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/nat_illustrate}
+\label{fig:nat_illustration}
+\centering
+\includegraphics[width=3in]{./figures/nat_illustration}
 \caption{Illustration of NAT service}
-\label{fig:nat_illustration}
 \end{figure}
@@
 \centering
-\caption{Flow entry for modifying the packet header fields of packets}
 \label{table:nat}
@@
 \end{tabular}
+\caption{Flow entry for modifying the packet header fields of packets}
 \end{table*}
@@
 
+By way of flow classification, we can know the 5 tuple (IP protocol, source IP, destination IP, source port, destination port) from each connection between an application and a host.
+Consequently, the network administrator can use those 5-tuple and dynamically adjust the bandwidth of meter, according the algorithm mentioned in above, to limit the bandwidth of each application from a host.
+As shown in figure.
+\ref{fig:rate_host_app}.
+and Table.
+\ref{table:rate_host_app}.
+In T0, we want to limit the application B to the Host with 600 Kbps and we will add the rules matching each 5 tuples from application A and set Meter 1 to those rule.
+In the meantime, the bandwidth of Meter 1 is set to 600/N Kbps if there are N connections built from application B of the host.
+In T1, marked as (a), If we want to limit the application A to the Host with 300 Kbps, we will add the rules matching each 5 tuples from application A and set Meter 2 to those rule.
+Then in T2, marked as (b), application B has already been limited since T0 and we want to change the bandwidth of application B from 600Kbps to 1000 Kbps.
+However, We would not change the rule in flow table, we only change the bandwidth of the correspond meter in the meter table.
+That is, the bandwidth of Meter 1 will be set from 600/N to 1000/N.
+Therefore, there only have a little overhead between switch and controller.
+That is, if there are Ni connections in time Ti, then the bandwidth will be set as shown as following.
+Similarly, we can use the same way to limit the whole network while not only to the specific host.
+
 \begin{figure}[!t]
@@
 \caption{Illustration of rate-limiting for a certain application of certain host}
-\label{fig:rate_app}
-\end{figure}
+\label{fig:rate_host_app}
+\end{figure}
+
+% Table 3
+\begin{table*}[]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+Request  & Match                                                   & Action                                \\ \hline
+Initial  & 5 tuples from an application B connection of the Host   & Goto Meter 1 (600 Kbps), Next Table   \\ \hline
+(a)      & 5 tuples from an application A connection of the Host   & Goto Meter 1 (300 Kbps), Next Table   \\ \hline
+(b)      & 5 tuples from an application B connection of the Host   & Goto Meter 2 (1000 Kbps), Next Table  \\ \hline
+\end{tabular}
+\caption{Flow entry of rate-limiting for a certain application of certain host}
+\label{table:rate_host_app}
+\end{table*}
 
@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/qos_evaluation}
+\label{fig:qos_evaluation}
+\end{figure}
+
+\section{Limit host bandwidth}
+We choose a way to verify our function is downloading the file in that it is a situation always takes up the network recourse in real world.
+We decide to download the image of Ubuntu 14.04 which is about 1GB size.
+As Figure \ref{fig:qos_evaluation}(a),We used a desktop computer to be the experimental host and record the bandwidth in every 2 seconds.
+In the beginning, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps.
+At 10th seconds, we wanted to limit this host’s bandwidth to 1024Kbps and we added the rule the destination MAC address is matching this desktop computer with a meter of 1024Kbps.
+Then we can find out the bandwidth from this host is decrease and be limited to about 1024Kbps immediately.
+At 36th seconds, we cancel the limit to this host.
+That is, removing the meter field from the rule in the flow table.
+Obviously, we also observed the bandwidth of download from this host is rising rapidly and without limiting.
+
+\section{Limit application bandwidth}
+There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source.
+We integrated with application identification to classify each flow belongs what the application is, consequently.
+As Figure \ref{fig:qos_evaluation}(b),Then we choose YouTube to verify our limitation function of applications.
+In the beginning without limitation, the bandwidth is between 190000 Kbps and 360000 Kbps.
+At 10th seconds, we limited the Youtube to 8192 Kbps by adding the rule of 5 tuples to flow table.
+Therefore, we can find out the traffic of Youtube from this host is reducing immediately and the total traffic will not exceed the limited bandwidth since then.
+The relationship between total traffic from Youtube and bandwidth of meter to each connection with time diagram is show as following Table \ref{fig:qos_final_table}.
+The bandwidth of meter will change dynamically according the number of connection at that time.
+
+% Table QoS
+\begin{table}[]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+Time     & \begin{tabular}[c]{@{}l@{}} Bandwidth of the meter to each\\connection from Youtube (Kbps)\end{tabular}    & \begin{tabular}[c]{@{}l@{}}Total Bandwidth from\\Youtube (Kbps)\end{tabular}           \\ \hline
+0        & Unlimited                                                                                                  & 358896   \\ \hline
+4        & Unlimited                                                                                                  & 292512   \\ \hline
+8        & Unlimited                                                                                                  & 290464   \\ \hline
+12       & 8192                                                                                                       & 1544   \\ \hline
+16       & 4096                                                                                                       & 1544   \\ \hline
+20       & 4096                                                                                                       & 24   \\ \hline
+24       & 8192                                                                                                       & 4584   \\ \hline
+28       & 8192                                                                                                       & 4552   \\ \hline
+32       & 2730                                                                                                       & 24   \\ \hline
+36       & 4096                                                                                                       & 584   \\ \hline
+40       & 4096                                                                                                       & 576   \\ \hline
+44       & 8192                                                                                                       & 2096   \\ \hline
+48       & 4096                                                                                                       & 576   \\ \hline
+52       & 4096                                                                                                       & 584   \\ \hline
+56       & 2730                                                                                                       & 536   \\ \hline
+60       & 4096                                                                                                       & 2616   \\ \hline
+\end{tabular}
+\caption{Limit the throughput of Skype to all hosts from a network domain.}
+\label{fig:qos_final_table}
+\end{table}
+
+As we known from the above, when we want to limit the application from a host, we used the 5 tuple from application to a host.
+Now we can use the similar concept to extend this limitation from a whole network domain instead of a host.
+That is, we didn’t just limit the application from a host, we were limiting the 5 tuples of each hosts from this network domain.
+The bandwidth dynamically adjust is also basic on the algorithm 1. But the number of connections of the application should include the whole hosts from this network domain instead of a host.
+As the figure \ref{fig:qos_final}, there are 3 hosts in the same network domain and we choose Skype to do the experiment.
+In the beginning without limitation, the bandwidths are almost 900000 Kbps to 1200000 Kbps in whole network.
+At 10th seconds, we limited the Skype to 16384 Kbps by adding the rule of 5 tuples from all hosts to flow table.
+Therefore, we can find out the traffic of Skype from this network domain is reducing immediately and the total traffic will not exceed the limited bandwidth since then.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/qos_final}
+\label{fig:qos_final}
+\end{figure}
+
 \newpage

### 2017-02-24 netsoft_paper.tex
section 2,4 ok

--- 2017-02-23 paper.tex
@@
-%% bare_jrnl.tex
+%% netsoft_paper.tex
 %% V1.4b
-%% 2015/08/26
-%% by Michael Shell
+%% 2017/02/24
+%% by HSNL, NTHU
 %% see http://www.michaelshell.org/
 %% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
 \documentclass[journal]{IEEEtran}
 
-\usepackage{techrep}
 \usepackage{indentfirst}
 \usepackage{graphicx}
+\usepackage{caption}
 \usepackage{subfigure}
 \usepackage{enumerate}
-\usepackage{subfigure}
-
-% \setlength{\columnsep}{10mm}
-% \setlength{\textwidth}{180mm}
-% \setlength{\textheight}{250mm}
-% \addtolength{\oddsidemargin}{-9mm}
-% \addtolength{\topmargin}{-25mm}
+\usepackage{epstopdf}
+\usepackage{csquotes}
+\usepackage{hyperref}
+\usepackage{url}
+\usepackage{amsmath}
+\interdisplaylinepenalty=2500
 
 \graphicspath{{figures/}}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hype rref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf{}
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and
-% Axel Sommerfeldt. This package may be useful when used in conjunction with
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead  reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
 
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
+
+% title
 % Linebreaks \\ can be used within to get better formatting as desired.
 % Do not put math or special symbols in the title.
+\title{Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch}
 
-% title
-% \title{Bare Demo of IEEEtran.cls\\ for IEEE Journals}
-
-%
-%
 % author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-% auther
-% \author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-%         John~Doe,~\IEEEmembership{Fellow,~OSA,}
-%         and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-% \thanks{M. Shell was with the Department
-% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-% GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-% \thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-
-% note the % following the last \IEEEmembership and also \thanks -
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-%
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
+% \author{
+% \IEEEauthorblockN{
+% I-Ju Liao\IEEEauthorrefmark{1},
+% Chi-Hsuan Li\IEEEauthorrefmark{1},
+% I-Hsien Hsu\IEEEauthorrefmark{1},
+% Chia-Chi Chen\IEEEauthorrefmark{1},
+% Ching-Hsuan Chen\IEEEauthorrefmark{2},
+% Che-Wei Lin\IEEEauthorrefmark{2},
+% Sheng-Jung Wu\IEEEauthorrefmark{1} and
+% Nen-Fu Huang\IEEEauthorrefmark{1}
+% }
+% \IEEEauthorblockA{
+% \IEEEauthorrefmark{1}
+% Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan\\
+% }
+% \IEEEauthorblockA{\IEEEauthorrefmark{2}
+% Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan\\
+% }
+% }
 
@@
 
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-%
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
 % make the title area
-% \maketitle
+\maketitle
 
@@
 % in the abstract or keywords.
-% \begin{abstract}
-% The abstract goes here.
-% \end{abstract}
+\begin{abstract}
+This Article is about a system how to optimize a service chain in SMB Network.
+There are many vCPE researches on Internet but a few to discuss about organization of Openflow switch and NFVs.
+This paper will propose a framework to optimize and manage NFVs with multi tables of Openflow switch.
+Most of paper talking about how to build architecture in Core Network of ISP, this paper will focus on how to use tables in SDN switches to maximum efficiency on Internet.
+\end{abstract}
 
 % Note that keywords are not normally used for peerreview papers.
-% \begin{IEEEkeywords}
-% IEEE, IEEEtran, journal, \LaTeX, paper, template.
-% \end{IEEEkeywords}
+\begin{IEEEkeywords}
+Software defined networking, vCPE
+\end{IEEEkeywords}
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle{}
+
 % Introduction
@@
 \section{Introduction}
-\IEEEPARstart{T}{his} document is a template for Microsoft Word versions 6.0 or later. If you are reading a paper or PDF version of this doconference. (By Eric)
+\IEEEPARstart{T}{his} document is a template for Microsoft Word versions 6.0 or later. If you are reading a paper or PDF version of this doconference.
+By Eric
 
 \section{Related Work}
-(By Eric)
+By Eric
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex,
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-%  reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively.
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-
-\section{vCPE System Overview}
-\subsection{Overview of Network Function}\label{ssec:nfv_overview}
-With the concept of SDN-enabled\cite{sdn-enabled} VNFs, SDN technology work not only a for traffic steering but also as a part of network functions.
-In this idea, network function have been achieved by the synergies between compute and network infrastructures.
+\section{System Description}
+\subsection{Overview of Network Function}
+With the concept of SDN-enabled VNFs, SDN technology work not only for traffic steering but also as a part of network functions.
+In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig.
+\ref{fig:desc_nfv_overview}.
 The former is a VNF controller, mainly responsible for dealing with stateful processing.
@@
 Using the advantages of this architecture, we can assign stateless or light-weight state work to the SDN switch, for example, packet filtering and packet counting, to load-off the computing resources.
-If we want to update our service, we just need to update the statful component, since the stateless component just follow the command from stateful components.
+If we want to update our service, we just need to update the stateful component, since the stateless component just follow the command from stateful components
 
@@
 \centering
-\caption{Overview of network function}
-\includegraphics[width=3in]{./figures/nfv_overview}
-\label{fig:nfv_overview}
+\includegraphics[width=3in]{./figures/desc_nfv_overview}
+\caption{Overview of network function.}
+\label{fig:desc_nfv_overview}
 \end{figure}
 
-\subsection{Service Deployment Model}\label{ssec:vcpe_deploy}
+\subsection{Service Deployment Model}
+With architecture mentioned in Fig.
+\ref{fig:desc_nfv_overview}, we come up with a network function service deployment model.
+Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/deployment}
-\caption{Service Deployment Model}
-\label{fig:vcpe_deploy}
-\end{figure}
-
-With architecture mentioned in \ref{ssec:nfv_overview}, we come up with a network function service deployment model.
-Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different NFV controller through our vCPE platform.
-
-Figure \ref{fig:vcpe_deploy} illustrates the service deployment model.
+Fig.
+\ref{fig:desc_service_deployment} illustrates the service deployment model.
 Each green area is a local network domain of customer.
@@
 
-\subsection{Architecture of the vCPE framework}
-\subsubsection{System Overview}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/desc_service_deployment}
+\caption{Service deployment model.}
+\label{fig:desc_service_deployment}
+\end{figure}
+
+\subsection{Architecture of the vCPE system}
+The architecture as shown in Fig \ref{fig:desc_vcpe_framework} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
+The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
+Each component is introduced in the subsection below.
 
@@
 \centering
-\includegraphics[width=3in]{./figures/vcpe_framework_overview}
-\caption{Overview of vCPE framework}
-\label{fig:vcpe_framework}
+\includegraphics[width=3in]{./figures/desc_vcpe_framework}
+\caption{Architecture of the vCPE framework.}
+\label{fig:desc_vcpe_framework}
 \end{figure}
 
-The architecture as shown in Fig \ref{fig:vcpe_framework} including of a Infrastructure Controller,
-% Fig lable to change
-Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
-The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
-Each component is introduced in the subsection below.
+\subsubsection{Infrastructure Controller}
 
-\subsubsection{Infrastructure Controller}
-The infrastructure controller is a composed Docker management server
-with the ability to manage the Docker resources like containers and images.
-The infrastructure doesn't handle the customer authentication or maintaining the state of running service,
-it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
+The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images.
+The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
 
 \subsubsection{Infrastructure Orchestrator}
+
 The infrastructure orchestrator plays the key role of our system.
 It connecting and automating of workflows when we deploy our services.
-When a customer subscribes, the infrastructure orchestrator authenticates the customer first,
-next it will call the infrastructure controller to create a container for this customer,
-and update information in database afterwards. It handle the entire lifecycle of our vCPE service.
+When a customer subscribes, the infrastructure orchestrator authenticates the customer first, next it will call the infrastructure controller to create a container for this customer, and update information in database afterwards.
+It handle the entire lifecycle of our vCPE service.
 
 \subsubsection{Cloud Database}
-The cloud database is used for restoring the of our vCPE services,
-which include each customer’s credential, customer’s container settings and virtual CPE service states.
+
+The cloud database is used for restoring the of our vCPE services, which include each customer’s credential, customer’s container settings and virtual CPE service states.
 The cloud database is using PostgreSQL, which is a open source, easily customized and object-relational database system.
@@
 \subsubsection{VNF Controllers}
+
 VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module.
@@
 We built a light-weight server as a launcher module to resolve the remotely execution issue.
-The remote launcher module monitor the SDN controller process ID (PID)
-and properly kill the SDN controller process ID when on demand.
+The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand.
 When the infrastructure controller once create the container, the remote module will run up initially, waiting request from VNF Orchestrator.
-The details of SDN controller design will be presented at section \ref{sec:nf_mft}.
+The details of SDN controller design will be presented at section \ref{sec:mft}.
 
 \subsubsection{VNF Orchestrator}
-The VNF Orchestrator is a Web application server hosting on Amazon Web server,
-being online for customer and provide a dashboard for virtual CPE and containers management and configuration.
 
-Through the web UI provided by the VNF Orchestrator,
-the customers can subscribe to the desired service and without typing any command via the command line interface (CLI).
-After receiving the subscribing message, the VNF orchestrator will request the infrastructure orchestrator to create a new VNF controller,
-and then send the virtual CPE configuration to the new VNF controller.
-Based on configuration demands under different conditions,
-the network administrator is able to select any of the listed network functions on the dashboard
-such as Firewall, NAT, DHCP and QoS management.
+The VNF Orchestrator is a Web application server hosting on Amazon Web server, being online for customer and provide a dashboard for virtual CPE and containers management and configuration.
+Through the web UI provided by the VNF Orchestrator, the customers can subscribe to the desired service and without typing any command via the command line interface (CLI).
+After receiving the subscribing message, the VNF orchestrator will request the infrastructure orchestrator to create a new VNF controller, and then send the virtual CPE configuration to the new VNF controller.
+Based on configuration demands under different conditions, the network administrator is able to select any of the listed network functions on the dashboard such as Firewall, NAT, DHCP and QoS management.
 
 \subsection{Network Functions}
+The proposed vCPE service provides following network functions.
+
 \subsubsection{Firewall}
@@
 The network manager can add new rules or remove rules to the access control list through our vCPE GUI.
-
-\subsubsection{NAT}
-The NAT service is a network function that can remap  IP address to another one.
-The Source NAT (SNAT) is typically used by internal users (inside private network) to access the Internet (outside network).
-The network function uses the action “Set-Field”, which defined by OpenFlow protocol for rewriting packet header fields.
-Via vCPE GUI interface, the network manager can set up the WAN port of SDN switch,
-public IP, default gateway, and local network address when using this function.
 
@@
 
-\subsubsection{Forwarding}
-Forwarding Service is a basic service that forward traffic to its destination
-and we use the Mac address learning concept to implement our forwarding function.
+\subsubsection{NAT}
+The NAT service is a network function that can remap  IP address to another one.
+The Source NAT (SNAT) is typically used by internal users (inside private network) to access the Internet (outside network).
+The network function uses the action “Set-Field”, which defined by OpenFlow protocol for rewriting packet header fields.
+Via vCPE GUI interface, the network manager can set up the WAN port of SDN switch, public IP, default gateway, and local network address when using this function.
 
 \subsubsection{QoS}
-Quality of Service (QoS) are always used to control the traffic flows of a network
-and prevent the traffic to exceed the network capacity and cause traffic congestion.
-Therefore we implement the bandwidth management using meter
-which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
-Beside achieving network functions virtualization with SDN technology,
-we also make the network administrator manage and monitor a network more easily.
+Quality of Service (QoS) are always used to control the traffic flows of a network and prevent the traffic to exceed the network capacity and cause traffic congestion.
+Therefore we implement the bandwidth management using meter which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
+Beside achieving network functions virtualization with SDN technology, we also make the network administrator manage and monitor a network more easily.
 As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
-In this paper, our QoS integrates with a flow classification engine
-and offers the three ways of bandwidth management:
-\begin{itemize}
+In this paper, our QoS integrates with a flow classification engine and offers the three ways of bandwidth management.
+
+\begin{itemize}[\IEEEsetlabelwidth{Z}]
 \item For a specific host.
-\item For a specific host.
+\item For a specific application.
 \item For a specific application from a host or a domain.
@@
 
-\subsection{Application Identification}
-Application identification is to identify each flow
-as an application name to enable QoS management system to do bandwidth control or distribution at application level.
+\subsubsection{Forwarding}
+Forwarding Service is a basic service that forward traffic to its destination and we use the Mac address learning concept to implement our forwarding function.
+
+\subsection{Application Identifier}
+Application identification is to identify each flow as an application name to enable QoS management system to do bandwidth control or distribution at application level.
 A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
-Applications include desktop applications, native mobile applications, and web applications,
-such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
+Applications include desktop applications, native mobile applications, and web applications, such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
 We use supervised machine learning and a method based on inspecting domain name service (DNS) responses to do flow classification.
-After application identification system classifies a flow as an application name,
-it sends the classification result to a server with database.
+After application identification system classifies a flow as an application name, it sends the classification result to a server with database.
 The server stores the classification result into database, and waits for query with 5-tuple from QoS management system.
-The detail will be described in section \ref{sec:app_classification}.
+The detail will be described in section \ref{sec:app_identification}.
 
-\section{Network function with multiple table management model}\label{sec:nf_mft}
+\section{Network Function With Multiple Flow Table Management Model} \label{sec:mft}
 \subsection{Multiple Flow Tables Strategy}
-In subsection \ref{ssec:nfv_overview}, the vCPE service design architecture have been introduced.
-The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway.
-The controller transform the network functions to series of OpenFlow rules requests and send to SDN switch.
-Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules.
-The flow table defines all matching and corresponding processing, thus playing an important role to executive network function.
-
-Since the flow table is crucial component, and we find that single table binds us to implement our network functions.
-The \cite{onf-multi-tables} also mentioned two condition for single table is too restrictive.
-The first is a single packet need to perform independent actions based on matching different fields.
-The second is that the packet needs two-stage processing.
-Involves into both situation, our network functions implemented by multiple flow tables strategy.
-
-In multiple flow tables strategy, the most important question is: which flow table should we insert rules into?
-We use the network function as a demarcation, that is, SDN applications which are responsible for specific network functions will only insert rules to one specific flow table, so we can focus on the design of the network function itself.
-In this way, however, the order of flow table become crucial.
-Should we put this network function at first, or the other?
-The answer is about the type of match and action in the rules generated by the network function
-
-The network functions of our vCPE services including Forwarding, Firewall, NAT, DHCP and QoS.
-We have determined the order of each function, shown in \ref{fig:table-seq}.
-In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/multiple_table}
-\caption{The flow table order of our vCPE service}
-\label{fig:table-seq}
-\end{figure}
-
 \subsection{Service Control}
-Service control is used to enable or disable service.
-To enable a service, we need to modify the table-miss rule.
-We always put a packet-in rule in the table of the last active service as a table-miss in case that there isn't any corresponding rule.
-To make our service chain possible, the rules of each service except the last service contains an additional action, go to next table, so the packets can continue to pass through all active services.
-
-To disable a service, we not only need to modify the table-miss rule but also have to add an enforce rule.
-Each enforce rules has maximum priority and the action is goto next table.
-It means that packets will still pass through the disabled service's table, and the only thing they do in this table is ignoring other rules and go to next table.
-
 \subsection{Firewall}
-Firewall service is able to block traffic dynamically, and in this service, the packets will not cause any packet-in event.
-On the dashboard, we can specify the blocking policies. There are 4 kinds of policies:
-\begin{itemize}
-\item Block any traffic from a certain source IP.
-\item Block all traffic to a certain destination IP.
-\item Block traffic based on known layer 4 protocols, such as SSH, HTTP, etc.
-\item Block traffic to any layer 4 ports of a host.
-\end{itemize}
-
-For different policies, the controller applies corresponding rules to the SDN switch.
-After the policies are set, the blocking rules will be installed immediately.
-Then any traffic that hit the blocking rules will be dropped.
-For normal traffic, they will not be affected.
-
-As shown in Table \ref{table:fw}, all the actions of flow entries are drop.
-The 1st rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
-The 2nd rule shows the flow entry would block the Telnet protocol.
-
-In our multiple table model, the firewall service is located in the table 1, since once packets are caught by the blocking rules, they doesn't need to apply any other services.
-The packets which match the rules will be dropped immediately, and their journey in the flow table ends here.
-To other no-blocked packets, they pass all blocking rules and finally match the table-miss rule, which will let the packets go on the next table.
-The action of firewall is different from other services, since in other services, no matter what actions are taken to the packets, the packets have to go to the next table
-
-\begin{table*}[]
-\centering
-\caption{Firewall rules in Flow Entry}
-\begin{threeparttable}
-\label{table:fw}
-\begin{tabular}{|l|l|l|l|l|l|}
-\hline
-IP proto & IP Src      & IP Dst       & L4 sport & L4 dport & Action \\ \hline
-TCP      & 192.168.2.1 & *            & *        & 22       & Drop   \\ \hline
-TCP      & *           & *            & *        & 23       & Drop   \\ \hline
-
-\end{tabular}
-\begin{tablenotes}
-  \small
-  \item Symbol * represents wildcard (match any value).
-\end{tablenotes}
-\end{threeparttable}
-\end{table*}
-
 \subsection{DHCP}
-DHCP service implements DHCP protocol to dynamically assign IP addresses to hosts.
-DHCP operation uses UDP protocol. The clients use port 68 as the source port and 67 as the destination port.
-On the contrary, the server use port 67 as the source port and 68 as the destination port.
-Our system is able to handle these packets  to realize DHCP service.
-
-The service follows these steps:
-\begin{enumerate}
-\item The controller adds a DHCP rule for DHCP packets when the service is enabled.
-\item All packets match this DHCP rule cause packet-in.
-\item The controller checks if a packet is a DHCP discovery packet.
-  \begin{enumerate}
-    \item If so, the controller assigns an IP address, and generate a DHCP offer then do packet-out.
-    \item If not, the controller then checks whether it's a DHCP request. If the result is positive, the controller generate a DHCP acknowledge then do packet-out.
-  \end{enumerate}
-\end{enumerate}
-
-Our system support multitable, but a specific table for DHCP service is not required.
-The reason is that only one rule will be installed for all hosts who request for DHCP service.
-When the service is disabled, the DHCP rule will be deleted,
-and the packets will continue to pass through our service chain.
-Following DHCP packets can reach other DHCP servers without entering our service chain
-since our controller will automatically flood out broadcast packets.
-
 \subsection{NAT}
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/nat_illustrate}
-\caption{Illustration of NAT service}
-\label{fig:nat_illustration}
-\end{figure}
-The NAT service could allow a lot of hosts to use one public IP address to connect the network.
-In order to achieve this thing, SDN controller have to set the packet header filed.
-Because the SDN switch would set the field, the first packet have to go to controller.
-And controller would add the flow to SDN switch, after that the packet would not go to controller.
-It can decrease the burdens of the controller.
-
-Below is a examples to show how the NAT service modify the IP address and port number,
-as shown in Fig \ref{fig:nat_illustration}.
-
-For outgoing packet, SDN switch doesn’t have any flow entry in flow table,
-so the Packet-in event will be triggered at the beginning.
-The packet that is sent by private network host will be sent to SDN controller,
-and the packet header fields are modified by Set-Field action.
-The source IP address and source port number of outgoing packet will be modified to public IP address
-and remaped a new port number for NAT.
-For ingoing packet, the destination IP and destination port number are modified to fit private IP and port number.
-And then SDN controller add these flow entries to SDN switch, it can’t avoid that all the packet sent to controller.
-Fig.
-\ref{fig:nat_illustration} show the public IP address of NAT is 140.114.71.178 and a host private IP is 192.168.8.254 and port number 7878.
-The client sent the packet to a server with IP address 140.114.71.177 and port number 9898.
-
-As shown in Table \ref{table:nat}, when host sent the packet to server (outgoing),
-the Packet-in will be trigger, and then packet to controller.
-The Set-Field action would modify the Source IP to public IP address of NAT is 140.114.71.178 and source port to 2000.
-when the server sends back to the client (ingoing), the packet header field would be modified.
-The destination IP address and destination port number would be modified to 192.168.8.254 and 7788.
-
-\begin{table*}[]
-\centering
-\caption{Flow entry for modifying the packet header fields of packets}
-\label{table:nat}
-\begin{tabular}{|l|l|l|l|l|l|}
-\hline
-            &IP Src          & IP Dst          & L4 src port  & L4 dst port & Action                                                                            \\ \hline
-1. outgoing &192.168.8.254   &140.114.71.177   & 7878         & 9898        & \begin{tabular}[c]{@{}l@{}}IP Src $\,\to\,$ 140.114.71.178; \\ L4 src port $\,\to\,$ 2000\end{tabular} \\ \hline
-2. ingoing  &140.114.71.177  &140.114.71.178   & 9898         & 2000        & \begin{tabular}[c]{@{}l@{}}IP Dst $\,\to\,$ 192.168.8.254; \\ L4 dst port $\,\to\,$ 7878\end{tabular} \\ \hline
-\end{tabular}
-\end{table*}
-
-In the single table framework, we have to add the two rules to SDN switch to match the outgoing and ingoing situation.
-At the first, we predict the NAT service to be put one the last table in the multiple table framework.
-Because the NAT service need to set the packet header fields and play a role of connection to the outside network.
-And the most important thing is that the SDN switch is according to order of table to match.
-We have to consider the outgoing and ingoing situations.
-As a result of all the above factors combined,
-the NAT service is located at the first and the last table in our multiple table framework.
-
 \subsection{QoS}
 \subsection{Forwarding}
-In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule.
-When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address.
-With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again.
-The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.
 
-In order to gather per-session statistics information, 5-tuple rules are needed.
-This is why we don’t add rules  based on mac address.
-The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
-In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
-
-\section{Application Identifier method} \label{sec:app_classification}
+\section{Application Identification Method}\label{sec:app_identification}
 In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
@@
 We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
-Except for DNS responses, the system only analyzes transport layer information of packets without inspecting their payload
+Except for DNS responses, the system only analyzes transport layer information of packets without inspecting their payload.
 
-\subsection{Architecture of our application identification system}
-There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig \ref{fig:classifcation_training} and Fig \ref{fig:classifcation_classifying} respectively.
+\subsection{Architecture of application identification system}
+There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig \ref{fig:class_training} and Fig \ref{fig:class_classifying} respectively.
 These architectures can be integrated, and do training and classifying in the same time.
-The detail will be mentioned in the following paragraph
 
@@
 \includegraphics[width=3in]{./figures/classification_training}
-\caption{Architecture of our application identification system in training phase}
-\label{fig:classifcation_training}
+\caption{Architecture of our application identification system in training phase.}
+\label{fig:class_training}
 \end{figure}
@@
 \includegraphics[width=3in]{./figures/classification_classifying}
-\caption{Architecture of our application identification system in classifying phase}
-\label{fig:classifcation_classifying}
+\caption{Architecture of our application identification system in classifying phase.}
+\label{fig:class_classifying}
 \end{figure}
@@
 \subsection{Procedure of Supervised ML in our system}
-In training phase, the architecture is show in Fig I.
+In training phase, the architecture is show in Fig \ref{fig:class_training}.
 Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes.
@@
 Scanner is to get mappings of 5-tuple and ground truth from OS.
-In classifying phase, the architecture is shown in Fig.
+In classifying phase, the architecture is shown in Fig \ref{class_classifying}.
 Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier.
@@
 We use number of packets, packet sizes, transmission time, transmission direction, throughput, and APPR to define flow attributes.
-There are 69 attributes in total, as defined in our previous work [].
+There are 69 attributes in total, as defined in our previous work
 
@@
 
-\section{Performance Evaluation}
-\subsection{Multiple Table Performance}
+\section{PERFORMANCE EVALUATION}
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/nat_evaluation_scenario}
-\caption{Multiple Table Performance Evaluation Scenario}
-\label{fig:nat_evaluation}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/nat_evaluation_result}
-\caption{Result of Multiple Table Performance Evaluation}
-\label{fig:nat_evaluation_result}
-\end{figure}
-
-The single table framework implementation is easier than multiple table framework, but the multiple table framework is more flexible.
-To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
-;;We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
-These experiments would use diffrent payload sizes to inspect their performances.
-As shown in Fig.
-\ref{fig:nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
-Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.
-We can see that the throughput value of multiple table framework is close to single table framework.
-So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other.
-
-\subsection{Accuracy of Application Identification }
-\subsubsection{Testing data set}
-Testing data set are mappings of flow attributes and ground truth (also called rules).
-This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan in 2016.
-We manually operated applications to generate traffic.
-After the system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on the testing data set.
-There are 14659 rules in total, and there are 137 applications if we view each platform version of an application as one application.
-(提fig 1)
-
-\subsubsection{Validation method}
-Although the system can do online training and classifying, we do offline training and classifying.
-More specifically, when we did online training to analyze traffic, get ground truth, and export the rules into a file.
-We do 10-fold cross validation on the rules.
-There are 10 rounds in 10-fold cross validation.
-Each round, we split testing data set into training dataset and classifying dataset.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/classification_classifying}
-\caption{Architecture of our application identification system in classifying phase}
-\label{fig:classifcation_evaluation}
-\end{figure}
-
-\subsubsection{Mapping of category names}
-We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
-The main reason is that some application have different ground truth in different operating system.
-
-\subsubsection{Accuracy matrices}
-To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq.
-(1), Eq.
-(2), and Eq.
-(3) [].
-In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category.
-After ten rounds, we calculate average
-
-%%
+\section{Conclusion and future works}
 
 \newpage
-
 \bibliographystyle{ieeetr}

### 2017-02-24 netsoft_paper.tex
fix figure wrong ref
firewall nat

@@
 \usepackage{csquotes}
+\usepackage[flushleft]{threeparttable}
 \usepackage{hyperref}
@@
 
-\subsubsection{DHCP}
-DHCP service allocates IP addresses to hosts dynamically.
-To implement the function, the SDN controller cope with UDP packets which use port 67 and 68.
-It generates DHCP offer and DHCP acknowledge to reply DHCP discovery and DHCP request received from the hosts.
-
 \subsubsection{NAT}
@@
 Via vCPE GUI interface, the network manager can set up the WAN port of SDN switch, public IP, default gateway, and local network address when using this function.
+
+\subsubsection{DHCP}
+DHCP service allocates IP addresses to hosts dynamically.
+To implement the function, the SDN controller cope with UDP packets which use port 67 and 68.
+It generates DHCP offer and DHCP acknowledge to reply DHCP discovery and DHCP request received from the hosts.
 
@@
 \subsection{Multiple Flow Tables Strategy}
+In subsection A , the vCPE service design architecture have been introduced.
+The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway.
+The controller transform the network functions to series of OpenFlow rules requests and send to SDN switch.
+Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules.
+The flow table defines all matching and corresponding processing, thus playing an important role to executive network function.
+
+Since the flow table is a crucial component, and we find that single flow table binds us to implement our network functions.
+The [] also mentioned two condition for single flow table is too restrictive.
+The first is a single packet need to perform independent actions based on matching different fields.
+The second is that the packet needs two-stage processing.
+Involves into both situation, our network functions implemented by multiple flow tables strategy.
+
+In multiple flow tables strategy, the most important question is: which flow table should we insert rules into?
+We use the network function as a demarcation, that is, SDN applications which are responsible for specific network functions will only insert rules to one specific flow table, so we can focus on the design of the network function itself.
+In this way, however, the order of flow table become crucial.
+Should we put this network function at first, or the other?
+The answer is about the type of match and action in the rules generated by the network function
+
+The network functions of vCPE services including Firewall, NAT, DHCP, QoS and Forwarding.
+We have determined the order of each function, shown in \ref{fig:mft_table_overview}.
+(Notice that the flow tables are counting from zero) In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=6in]{./figures/mft_table_overview}
+\caption{The flow table order of vCPE service.}
+\label{fig:mft_table_overview}
+\end{figure*}
+
 \subsection{Service Control}
+Service control is about which service we want to enable or disable.
+To enable a service, we need to modify the table-miss rule.
+We always put a packet-in rule in the flow table of the last active service as a table-miss in case that there isn't any corresponding rule.
+To make our service chain possible, the rules of each service except the last service contains an additional action, go to next flow table, so the packets can continue to pass through all active services.
+
+To disable a service, we not only need to modify the table-miss rule but also have to add an enforce rule.
+Each enforce rules has maximum priority and the action is goto next flow table.
+It means that packets will still pass through the disabled service's table, and the only thing they do in this flow table is ignoring other rules and go to next flow table.
+
 \subsection{Firewall}
+Firewall service is able to block traffic dynamically, and in this service, the packets will not cause any packet-in event.
+
+On the dashboard, we can specify the blocking policies. There are 3 kinds of policies:
+\begin{itemize}[\IEEEsetlabelwidth{Z}]
+\item Block any traffic from a certain source IP or destination IP.
+\item Block traffic based on known layer 4 protocols, such as SSH, HTTP, etc.
+\item Block traffic to customize layer 4 ports of a host.
+\end{itemize}
+
+For different policies, the controller applies corresponding rules to the SDN switch.
+After the policies are set, the blocking rules will be installed immediately.
+Then any traffic that hit the blocking rules will be dropped.
+For normal traffic, they will not be affected.
+
+As shown in Table \ref{table:fw}, all the actions of flow entries are drop.
+The 1[st] rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
+The 2[nd] rule shows the flow entry would block the Telnet protocol.
+
+In our multiple flow tables model, the firewall service is located in the flow table 1, since once packets are caught by the blocking rules, they doesn't need to apply any other services.
+The packets which match the rules will be dropped immediately, and their journey in the flow table ends here.
+To other no-blocked packets, they pass all blocking rules and finally match the table-miss rule, which will let the packets go on the next flow table.
+The action of firewall is different from other services, since in other services, no matter what actions are taken to the packets, the packets have to go to the next flow table.
+
+% firewall example table
+\begin{table*}[!t]
+\caption{Firewall rules in Flow Entry}
+\label{table:fw}
+\centering
+\begin{threeparttable}
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+IP proto & IP Src      & IP Dst       & L4 sport & L4 dport & Action \\ \hline
+TCP      & 192.168.2.1 & *            & *        & 22       & Drop   \\ \hline
+TCP      & *           & *            & *        & 23       & Drop   \\ \hline
+\end{tabular}
+  \begin{tablenotes}
+    \item[] Symbol * represents wildcard (match any value).
+  \end{tablenotes}
+\end{threeparttable}
+\end{table*}
+
+\subsection{NAT}
+The NAT service could allow a lot of hosts to use one public IP address to connect the network.
+In order to achieve this thing, SDN controller have to set the packet header filed.
+Because the SDN switch would set the field, the first packet have to go to controller.
+And controller would add the flow to SDN switch, after that the packet would not go to controller.
+It can decrease the burdens of the controller.
+
+Below is a examples to show how the NAT service modify the IP address and port number, as shown in Fig.
+\ref{mft_nat}.
+For outgoing packet, the SDN switch doesn’t have any flow entry in flow table, so the Packet-in event will be triggered at the beginning.
+The packet that is sent by private network host will be sent to SDN controller, and the packet header fields are modified by Set-Field action.
+The source IP address and source port number of outgoing packet will be modified to public IP address and remaped a new port number for NAT.
+For ingoing packet, the destination IP and destination port number are modified to fit private IP and port number.
+And then SDN controller add these flow entries to SDN switch, it can’t avoid that all the packet sent to controller.
+
+Fig.
+\ref{mft_nat} show the public IP address of NAT is 140.114.71.178 and a host private IP is 192.168.8.254 and port number 7878.
+The client sent the packet to a server with IP address 140.114.71.177 and port number 9898.
+
+As shown in Table \ref{table:nat}, when host sent the packet to server (outgoing), the Packet-in will be trigger, and then packet to controller.
+The Set-Field action would modify the Source IP to public IP address of NAT is 140.114.71.178 and source port to 2000.
+when the server sends back to the client (ingoing), the packet header field would be modified.
+The destination IP address and destination port number would be modified to 192.168.8.254 and 7788.
+
+In the single flow table framework, we have to add the two rules to SDN switch to match the outgoing and ingoing situation.
+At the first, we predict the NAT service to be put one the last table in the multiple flow tables framework.
+Because the NAT service need to set the packet header fields and play a role of connection to the outside network.
+And the most important thing is that the SDN switch is according to order of table to match.
+We have to consider the outgoing and ingoing situations.
+As a result of all the above factors combined, the NAT service is located at the first and the last table in our multiple flow table framework.
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=6in]{./figures/mft_table_overview}
+\caption{The flow table order of vCPE service.}
+\label{fig:mft_nat}
+\end{figure*}
+
+% NAT example table
+\begin{table*}[!t]
+\caption{Flow entry for modifying the packet header fields of packets}
+\label{table:nat}
+\centering
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+            &IP Src          & IP Dst          & L4 src port  & L4 dst port & Action                                                                            \\ \hline
+1. outgoing &192.168.8.254   &140.114.71.177   & 7878         & 9898        & \begin{tabular}[c]{@{}l@{}}IP Src $\,\to\,$ 140.114.71.178; \\ L4 src port $\,\to\,$ 2000\end{tabular} \\ \hline
+2. ingoing  &140.114.71.177  &140.114.71.178   & 9898         & 2000        & \begin{tabular}[c]{@{}l@{}}IP Dst $\,\to\,$ 192.168.8.254; \\ L4 dst port $\,\to\,$ 7878\end{tabular} \\ \hline
+\end{tabular}
+\end{table*}
+
 \subsection{DHCP}
-\subsection{NAT}
 \subsection{QoS}
@@
 Scanner is to get mappings of 5-tuple and ground truth from OS.
-In classifying phase, the architecture is shown in Fig \ref{class_classifying}.
+In classifying phase, the architecture is shown in Fig \ref{fig:class_classifying}.
 Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier.

### 2017-02-24 netsoft_paper.tex
nat dhcp forwarding

@@
 \begin{itemize}[\IEEEsetlabelwidth{Z}]
-\item Block any traffic from a certain source IP or destination IP.
+\item Block any traffic from a source IP or destination IP.
 \item Block traffic based on known layer 4 protocols, such as SSH, HTTP, etc.
@@
 As shown in Table \ref{table:fw}, all the actions of flow entries are drop.
-The 1[st] rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
-The 2[nd] rule shows the flow entry would block the Telnet protocol.
+The first rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
+The second rule shows the flow entry would block the Telnet protocol.
 
@@
 Below is a examples to show how the NAT service modify the IP address and port number, as shown in Fig.
-\ref{mft_nat}.
+\ref{fig:mft_nat}.
 For outgoing packet, the SDN switch doesn’t have any flow entry in flow table, so the Packet-in event will be triggered at the beginning.
@@
 Fig.
-\ref{mft_nat} show the public IP address of NAT is 140.114.71.178 and a host private IP is 192.168.8.254 and port number 7878.
+\ref{fig:mft_nat} show the public IP address of NAT is 140.114.71.178 and a host private IP is 192.168.8.254 and port number 7878.
 The client sent the packet to a server with IP address 140.114.71.177 and port number 9898.
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 \centering
-\includegraphics[width=6in]{./figures/mft_table_overview}
+\includegraphics[width=6in]{./figures/mft_nat}
 \caption{The flow table order of vCPE service.}
 \label{fig:mft_nat}
-\end{figure*}
+\end{figure}
 
@@
 \subsection{DHCP}
+DHCP service implements DHCP protocol to dynamically assign IP addresses to hosts.
+DHCP operation uses UDP protocol. The clients use port 68 as the source port and 67 as the destination port.
+On the contrary, the server use port 67 as the source port and 68 as the destination port.
+Our system is able to handle these packets  to realize DHCP service.
+
+The service follows these steps:
+\begin{enumerate}
+\item The controller adds a DHCP rule for DHCP packets when the service is enabled.
+\item All packets match this DHCP rule cause packet-in.
+\item The controller checks if a packet is a DHCP discovery packet.
+  \begin{enumerate}
+    \item If so, the controller assigns an IP address, and generate a DHCP offer then do packet-out.
+    \item If not, the controller then checks whether it's a DHCP request. If the result is positive, the controller generate a DHCP acknowledge then do packet-out.
+  \end{enumerate}
+\end{enumerate}
+
+Our system support multitable, but a specific table for DHCP service is not required.
+The reason is that only one rule will be installed for all hosts who request for DHCP service.
+When the service is disabled, the DHCP rule will be deleted,
+and the packets will continue to pass through our service chain.
+Following DHCP packets can reach other DHCP servers without entering our service chain
+since our controller will automatically flood out broadcast packets.
+
 \subsection{QoS}
+
 \subsection{Forwarding}
+In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule.
+When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address.
+With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again.
+The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.
+
+In order to gather per-session statistics information, 5-tuple rules are needed.
+This is why we don’t add rules  based on mac address.
+The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
+In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
 

### 2017-02-24 netsoft_paper.tex
flow table naming fix
modify figure and table
add dot adter 'Fig'

@@
 \subsection{Architecture of the vCPE system}
-The architecture as shown in Fig \ref{fig:desc_vcpe_framework} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
+The architecture as shown in Fig. \ref{fig:desc_vcpe_framework} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
 The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
@@
 \section{Network Function With Multiple Flow Table Management Model} \label{sec:mft}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=6in]{./figures/mft_table_overview}
+\caption{The flow table order of vCPE service.}
+\label{fig:mft_table_overview}
+\end{figure*}
+
 \subsection{Multiple Flow Tables Strategy}
@@
 (Notice that the flow tables are counting from zero) In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=6in]{./figures/mft_table_overview}
-\caption{The flow table order of vCPE service.}
-\label{fig:mft_table_overview}
-\end{figure*}
 
@@
 \centering
-\includegraphics[width=6in]{./figures/mft_nat}
+\includegraphics[width=3in]{./figures/mft_nat}
 \caption{The flow table order of vCPE service.}
@@
 
-Our system support multitable, but a specific table for DHCP service is not required.
+Our system support multiple flow table, but a specific flow table for DHCP service is not required.
 The reason is that only one rule will be installed for all hosts who request for DHCP service.
@@
 \subsection{Architecture of application identification system}
-There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig \ref{fig:class_training} and Fig \ref{fig:class_classifying} respectively.
+There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig.
+\ref{fig:class_training} and Fig.
+\ref{fig:class_classifying} respectively.
 These architectures can be integrated, and do training and classifying in the same time.
@@
 \subsection{Procedure of Supervised ML in our system}
-In training phase, the architecture is show in Fig \ref{fig:class_training}.
+In training phase, the architecture is show in Fig.
+\ref{fig:class_training}.
 Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes.
@@
 Scanner is to get mappings of 5-tuple and ground truth from OS.
-In classifying phase, the architecture is shown in Fig \ref{fig:class_classifying}.
+In classifying phase, the architecture is shown in Fig.
+\ref{fig:class_classifying}.
 Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier.
@@
 \section{PERFORMANCE EVALUATION}
+\subsection{Multiple Table Performance}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/evaluation_nat_scenario}
+\caption{Multiple Table Performance Evaluation Scenario}
+\label{fig:evaluation_nat_scenario}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/evaluation_nat_result}
+\caption{Result of Multiple Table Performance Evaluation}
+\label{fig:evaluation_nat_result}
+\end{figure}
+
+The single flow table framework implementation is easier than multiple flow table framework, but the multiple flow table framework is more flexible.
+To verify the efficacy of multiple flow table vCPE framework, this experiment use the NAT service to compare the throughput between single flow table vCPE and multiple flow table vCPE.
+;;We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
+These experiments would use diffrent payload sizes to inspect their performances.
+As shown in Fig.
+\ref{fig:evaluation_nat_scenario}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
+Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.
+We can see that the throughput value of multiple table framework is close to single table framework.
+So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other, which shown as \ref{fig:evaluation_nat_result}.
+
+\subsection{Accuracy of Application Identification }
+\subsubsection{Testing data set}
+Testing data set are mappings of flow attributes and ground truth (also called rules).
+This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan in 2016.
+We manually operated applications to generate traffic.
+After the system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on the testing data set.
+There are 14659 rules in total, and there are 137 applications if we view each platform version of an application as one application.
+
+\subsubsection{Validation method}
+Although the system can do online training and classifying, we do offline training and classifying, shown as Fig.
+\ref{fig:classifcation_evaluation}.
+More specifically, when we did online training to analyze traffic, get ground truth, and export the rules into a file.
+We do 10-fold cross validation on the rules.
+There are 10 rounds in 10-fold cross validation.
+Each round, we split testing data set into training dataset and classifying dataset.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/classifcation_evaluation}
+\caption{Architecture of application identification system in classifying phase}
+\label{fig:classifcation_evaluation}
+\end{figure}
+
+\subsubsection{Mapping of category names}
+We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
+The main reason is that some application have different ground truth in different operating system.
+
+\subsubsection{Accuracy matrices}
+To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq.
+(1), Eq.
+(2), and Eq.
+(3) [].
+In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category.
+After ten rounds, we calculate average
+
+\begin{equation}
+\label{eqn_1}
+Precision = \dfrac{True\ positive}{True\ positive\ +\ False\ positive}
+\end{equation}
+
+\begin{equation}
+\label{eqn_2}
+Recall = \dfrac{True\ positive}{True\ positive\ +\ False\ negative}
+\end{equation}
+
+\begin{equation}
+\label{eqn_3}
+F1\ score = \dfrac{2\times Precision\times Recall}{Precsion + Recall}
+\end{equation}
+
+\subsubsection{Accuracy analysis}
+
+\subsection{QoS Evaluation Limit Host bandwidth}
+
+\subsection{QoS Evaluation Limit application bandwidth}
 

### 2017-02-24 netsoft_paper.tex
the second final version

@@
 \item The controller checks if a packet is a DHCP discovery packet.
-  \begin{enumerate}
-    \item If so, the controller assigns an IP address, and generate a DHCP offer then do packet-out.
-    \item If not, the controller then checks whether it's a DHCP request. If the result is positive, the controller generate a DHCP acknowledge then do packet-out.
-  \end{enumerate}
+If so, the controller assigns an IP address, and generate a DHCP offer then do packet-out.
+If not, the controller then checks whether it's a DHCP request.
+If the result is positive, the controller generate a DHCP acknowledge then do packet-out.
 \end{enumerate}
@@
 \subsection{QoS}
+QoS service is mainly for traffic control and we provide three management funtion for QoS service.
+We will introduce these three strategy first and then discuss the flow table order of QoS service in multiple table model.
+
+\subsubsection{Rate limitation of hosts}
+When some hosts take up a lot of bandwidth of network, it will make other hosts in slow speed or make traffic congestion.
+To prevent this, rate limiting is used to control the rate of traffic from a host.
+For implementing the host rate limitation, we create a meter for desired bandwidth first and then add a flow, of which match is host’s mac address and action is the meter we just created.
+
+The concept of this option is shown in Fig.
+\ref{fig:mft_qos_rate_host}.
+In T0, host 1 and host 2 are not limited yet.
+Since host 2 takes up a lot of bandwidth from network in T0~T1, the network administrator sets host 2 rate-limited under 400 Kbps.
+When controller receive this request, marked as (a), it will create a new meter  with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = HOST1 MAC and meter = 1.
+According to our flow table, it will limit the rate of the target host.
+Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately.
+The similar situation also occurs to Host 1 in T2.
+The administrator chooses to set Host1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/mft_qos_rate_host}
+\caption{Illustration of rate-limiting for a certain host}
+\label{fig:mft_qos_rate_host}
+\end{figure}
+
+\subsubsection{Rate limitation of applications}
+There are more and more network’s applications used such as online games, video streaming, conference call, etc.
+Therefore, there are massive traffic working in the network.
+Consequently, we integrate with a flow classification engine to identify the flow belongs which application is.
+However, an application may have many connections, we will equally distribute the bandwidth to each connection.
+
+For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine.
+If we want to limit this application to 1000Kbps.
+As Figure.
+\ref{fig:mft_qos_rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps.
+In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps.
+In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore.
+Whereas, the sum of bandwidth from this application is always being 1000 Kbps.
+That is, the bandwidth will be dynamically adjusted.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/mft_qos_rate_app}
+\caption{Illustration of rate-limiting for a certain host}
+\label{fig:mft_qos_rate_app}
+\end{figure}
+
+\subsubsection{Rate limitation for a certain application of certain host}
+
+By way of flow classification, we can know the 5 tuple (IP protocol, source IP, destination IP, source port, destination port) from each connection between an application and a host.
+Consequently, the network administrator can use those 5-tuple and dynamically adjust the bandwidth of meter, according the algorithm mentioned in above, to limit the bandwidth of each application from a host.
+As shown in figure.
+\ref{fig:mft_qos_rate_host_app}.
+In T0, we want to limit the application B to the Host with 600 Kbps and we will add the rules matching each 5 tuples from application A and set Meter 1 to those rule.
+In the meantime, the bandwidth of Meter 1 is set to 600/N Kbps if there are N connections built from application B of the host.
+In T1, marked as (a), If we want to limit the application A to the Host with 300 Kbps, we will add the rules matching each 5 tuples from application A and set Meter 2 to those rule.
+Then in T2, marked as (b), application B has already been limited since T0 and we want to change the bandwidth of application B from 600Kbps to 1000 Kbps.
+However, We would not change the rule in flow table, we only change the bandwidth of the correspond meter in the meter table.
+That is, the bandwidth of Meter 1 will be set from 600/N to 1000/N.
+Therefore, there only have a little overhead between switch and controller.
+That is, if there are Ni connections in time Ti, then the bandwidth will be set as shown as following.
+Similarly, we can use the same way to limit the whole network while not only to the specific host.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/mft_qos_rate_host_app}
+\caption{Illustration of rate-limiting for a certain application of certain host}
+\label{fig:mft_qos_rate_host_app}
+\end{figure}
+
+\subsubsection{The flow table order of QoS service}
+QoS service is located at flow table 2, because the location of NAT/DHCP, firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
+Let's consider the scenario that we put the QoS flow table after the forwarding flow table.
+Plus, we have only two services enabled, forwarding and QoS, then suppose a host is not limited by QoS policies.
+The very first packet will not be affected in both arrangement.
+For the following packets, the difference can be observed.
+The packets which has matched the rules of the forwarding flow table will still cause packet-ins when they go to QoS flow table.
+This is not supposed to happen, since the host is not restrained by QoS policies and any packet-in increase the controller's load.
+To reduce the burden of the controller, we put QoS flow table ahead of forwarding flow table.
+In this scenario, all packets that pass through QoS flow table will continue to go to forwarding flow table without matching any QoS rules.
+Then the packets except the very first packet will just be forwarded by forwarding service instead of causing packet-ins.
+Hence the controller's load will decrease.
+To use our system, the forwarding service is necessary, so there is no such scenario that users enable QoS and disable forwarding.
 
@@
 Although the system can do online training and classifying, we do offline training and classifying, shown as Fig.
-\ref{fig:classifcation_evaluation}.
+\ref{fig:evaluation_classification}.
 More specifically, when we did online training to analyze traffic, get ground truth, and export the rules into a file.
@@
 \centering
-\includegraphics[width=3in]{./figures/classifcation_evaluation}
-\caption{Architecture of application identification system in classifying phase}
-\label{fig:classifcation_evaluation}
+\includegraphics[width=3in]{./figures/evaluation_classification}
+\caption{Result of Multiple Table Performance Evaluation}
+\label{fig:evaluation_classification}
 \end{figure}

### 2017-02-24 netsoft_paper.tex
fix nat and add qos exp part

@@
 \usepackage{amsmath}
+\usepackage[super]{nth}
 \interdisplaylinepenalty=2500
@@
 
-The single flow table framework implementation is easier than multiple flow table framework, but the multiple flow table framework is more flexible.
-To verify the efficacy of multiple flow table vCPE framework, this experiment use the NAT service to compare the throughput between single flow table vCPE and multiple flow table vCPE.
-;;We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
+The single flow table framework implementation is easier than multiple flow table framework,
+but the multiple flow table framework is more flexible.
+To verify the efficacy of multiple flow table vCPE framework,
+this experiment use the NAT service to compare the throughput between single flow table vCPE and multiple flow table vCPE.
+
+To begin with, an overview of the experiment environment is shown in Fig. \ref{fig:evaluation_nat_scenario}.
+The NFV controller run on the Dell PowerEdge R630 Rack Server,
+and the SDN switch use the Pica8 P-3290 switch.
+We use the iPerf2 to generate the network traffic.
+The iperf server would connect the public IP address with 140.114.71.178, and then the iperf client connect to the SDN switch, and is controlled by NFV controller.
+NFV controller run the NAT service, but use the different framework that are single flow table and multiple flow table.
+
+We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
 These experiments would use diffrent payload sizes to inspect their performances.
 As shown in Fig.
-\ref{fig:evaluation_nat_scenario}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
+\ref{fig:evaluation_nat_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
 Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.
 We can see that the throughput value of multiple table framework is close to single table framework.
-So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other, which shown as \ref{fig:evaluation_nat_result}.
+So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other, which shown as Fig.
+\ref{fig:evaluation_nat_result}.
 
@@
 
+We choose a way to verify our function is downloading the file in that it is a situation always takes up the network recourse in real world.
+We decide to download the image of Ubuntu 14.04 which is about 1GB size.
+
+As shown in Fig.
+\ref{fig:qos_limit_host}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service.
+And the OpenFlow-enable switch use the the Edge-Core AS5712-54X switch that operating system is PicOS TM r2.6.
+
+We used a desktop computer to be the experimental host and record the bandwidth in every 2 seconds.
+In the beginning, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps.
+At \nth{10} seconds, we wanted to limit this host’s bandwidth to 1024Kbps and we added the rule the destination MAC address is matching this desktop computer with a meter of 1024Kbps.
+Then we can find out the bandwidth from this host is decrease and be limited to about 1024Kbps immediately.
+
+At \nth{36} seconds, we cancel the limit to this host.
+That is, removing the meter field from the rule in the flow table.
+Obviously, we also observed the bandwidth of download from this host is rising rapidly and without limiting.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/qos_limit_host}
+\caption{Limit the download rate to a host.}
+\label{fig:qos_limit_host}
+\end{figure}
+
 \subsection{QoS Evaluation Limit application bandwidth}

### 2017-02-24 netsoft_paper.tex
modify QoS decription

--- 2017-02-24 netsoft_paper.tex
@@
 \section{System Description}
-\subsection{Overview of Network Function}
+\subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
 With the concept of SDN-enabled VNFs, SDN technology work not only for traffic steering but also as a part of network functions.
@@
 
+\subsubsection{Forwarding}
+Forwarding Service is a basic service that forward traffic to its destination and we use the Mac address learning concept to implement our forwarding function.
+
 \subsubsection{QoS}
@@
 \item For a specific application.
-\item For a specific application from a host or a domain.
 \end{itemize}
-
-\subsubsection{Forwarding}
-Forwarding Service is a basic service that forward traffic to its destination and we use the Mac address learning concept to implement our forwarding function.
 
@@
 \subsection{Multiple Flow Tables Strategy}
-In subsection A , the vCPE service design architecture have been introduced.
+In subsection \ref{ssec:desc_nfv_overview}, the vCPE service design architecture have been introduced.
 The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway.
@@
 
-The network functions of vCPE services including Firewall, NAT, DHCP, QoS and Forwarding.
+The network functions of vCPE services including Firewall, NAT, DHCP, Forwarding and QoS.
 We have determined the order of each function, shown in \ref{fig:mft_table_overview}.
@@
 
+\subsection{Forwarding} \label{ssec:forwarding}
+In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule.
+When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address.
+With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again.
+The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.
+
+In order to gather per-session statistics information, 5-tuple rules are needed.
+This is why we don’t add rules  based on mac address.
+The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
+In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
+
 \subsection{QoS}
@@
 Consequently, we integrate with a flow classification engine to identify the flow belongs which application is.
-However, an application may have many connections, we will equally distribute the bandwidth to each connection.
+The integration scenario will be shown as Fig.
+\ref{fig:class_classifying}.
 
-For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine.
-If we want to limit this application to 1000Kbps.
+In order to rate limit for a certain application, we need to gathering per-flow statistics information first. When
+a connection is created, the first packet of this connection will be handled by the forwarding service and add 5-tuple rules into SDN switch, so we can get the bandwidth information of per-flow connection.
+(See subsection \ref{ssec:forwarding} for details).
+With the classified result of application identification, we can know the application type of each connection.
+
+When network administrator request to rate limit a certain application to a certain bandwidth, we will equally distribute the bandwidth to each connection of the application.
+The controller set all flows belong to the same application into the same meter, and modifying the bandwidth of meter to achive our goal.
+For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine and we want to limit this application to 1000Kbps.
 As Figure.
@@
 
-\subsubsection{Rate limitation for a certain application of certain host}
-
-By way of flow classification, we can know the 5 tuple (IP protocol, source IP, destination IP, source port, destination port) from each connection between an application and a host.
-Consequently, the network administrator can use those 5-tuple and dynamically adjust the bandwidth of meter, according the algorithm mentioned in above, to limit the bandwidth of each application from a host.
-As shown in figure.
-\ref{fig:mft_qos_rate_host_app}.
-In T0, we want to limit the application B to the Host with 600 Kbps and we will add the rules matching each 5 tuples from application A and set Meter 1 to those rule.
-In the meantime, the bandwidth of Meter 1 is set to 600/N Kbps if there are N connections built from application B of the host.
-In T1, marked as (a), If we want to limit the application A to the Host with 300 Kbps, we will add the rules matching each 5 tuples from application A and set Meter 2 to those rule.
-Then in T2, marked as (b), application B has already been limited since T0 and we want to change the bandwidth of application B from 600Kbps to 1000 Kbps.
-However, We would not change the rule in flow table, we only change the bandwidth of the correspond meter in the meter table.
-That is, the bandwidth of Meter 1 will be set from 600/N to 1000/N.
-Therefore, there only have a little overhead between switch and controller.
-That is, if there are Ni connections in time Ti, then the bandwidth will be set as shown as following.
-Similarly, we can use the same way to limit the whole network while not only to the specific host.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{./figures/mft_qos_rate_host_app}
-\caption{Illustration of rate-limiting for a certain application of certain host}
-\label{fig:mft_qos_rate_host_app}
-\end{figure}
-
-\subsubsection{The flow table order of QoS service}
-QoS service is located at flow table 2, because the location of NAT/DHCP, firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
+\subsubsection{The flow table order of forwarding and QoS service}
+Since the location of NAT, DHCP and firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
 Let's consider the scenario that we put the QoS flow table after the forwarding flow table.
@@
 To use our system, the forwarding service is necessary, so there is no such scenario that users enable QoS and disable forwarding.
-
-\subsection{Forwarding}
-In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule.
-When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address.
-With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again.
-The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.
-
-In order to gather per-session statistics information, 5-tuple rules are needed.
-This is why we don’t add rules  based on mac address.
-The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
-In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
 
@@
 \section{Conclusion and future works}
+(Eric)
 

### 2017-02-24 netsoft_paper.tex
Limit Youtube Domain

@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/mft_qos_rate_domain_app}
+\caption{Limit the Youtube rate to a network domain.}
+\label{fig:mft_qos_rate_domain_app}
+\end{figure}
+
 \subsection{QoS Evaluation Limit application bandwidth}
+
+There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source.
+We integrated with application identification to classify each flow belongs what the application is, consequently.
+We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.
+Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
+As shown in Figure.?
+In the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps.
+At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain.
+Therefore, we can find out the total traffic of Youtube from this network domain is reducing immediately.
+Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
+When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.
 

### 2017-02-24 netsoft_paper.tex
add app-identification part

--- 2017-02-24 netsoft_paper.tex
@@
 
-\subsection{Application Identifier}
-Application identification is to identify each flow as an application name to enable QoS management system to do bandwidth control or distribution at application level.
+\subsection{Application Identification}
+Application identification is to identify each flow as an application name to enable QoS management system to do bandwidth control or distribution at application level \cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
+The application name means the name of application which establishes the flow.
 A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
@@
 After application identification system classifies a flow as an application name, it sends the classification result to a server with database.
-The server stores the classification result into database, and waits for query with 5-tuple from QoS management system.
+The server stores the classification result into the database, and waits for requests from QoS management system.
 The detail will be described in section \ref{sec:app_identification}.
@@
 In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
-In other words, the system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
+In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
+The corresponding application name of a flow means the name of the application which establishes the flow.
 We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
-Except for DNS responses, the system only analyzes transport layer information of packets without inspecting their payload.
+The system analyzes the packets whose transport protocol are TCP or UDP.
+Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.
 
@@
 \subsection{Overall procedure of application identification}
-In training phase, we generate some data needed by ML and the method based on inspecting DNS responses.
-In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify; otherwise, we use ML to classify.
+In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
+In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
+The corresponding application name of a flow means the name of the application which establishes the flow.
+We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
+The system analyzes the packets whose transport protocol are TCP or UDP.
+Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.
 
@@
 
-\subsection{Flow attributes we adopted in ML}
+\subsection{Flow attributes we adopted in supervised ML}
 In ML, when system calculates flow attributes, we only use transport layer information of packets which have payload.
-We use Application Round (APPR) proposed by [] to analyze flow behavior.
+We use Application Round (APPR) proposed by \cite{classfication-cloud} to analyze flow behavior.
 We use number of packets, packet sizes, transmission time, transmission direction, throughput, and APPR to define flow attributes.
-There are 69 attributes in total, as defined in our previous work
+There are 69 attributes in total, as defined in our previous work \cite{Chia-Chin-master}.
 
-\subsection{Algorithms we adopted in ML}
+\subsection{Algorithms we adopted in supervised ML}
 We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato.
 We call Weka Java API to build classification model.
-We use three algorithms, namely RandomSupSpace with RandomTree [], FilterClassifier with discretization and RandomTree [], and RandomCommittee with RandomTree [].
+We use three algorithms, namely RandomSupSpace with RandomTree, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
 
@@
 In training phase, we collect the mappings of server IP and application name.
-A mapping of server IP and application name means the application has ever establish connection with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
-In classifying phase, we only use those mappings which have been used by one application to classify.
-When system detect a flow, we check whether source IP or destination IP of the flow match any server IP of those mappings.
-If it matches any server IP, we regard corresponding application name as classification result; otherwise, we use flow attributes of the flow and classification model to classify.
+A mapping of server IP and application name means the application has ever established connection with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
+In classifying phase, we do not use those server IPs which have more than two corresponding applications among the mappings to classify.
+We only use server IPs which have one corresponding application in the mappings to classify.
+When system detect a flow, we check whether source IP or destination IP of the flow match any of these server IPs.
+If it matches, we regard corresponding application name as classification result; otherwise, we use flow attributes of the flow and classification model of supervised ML to classify.
 
@@
 
-\subsection{Accuracy of Application Identification }
+\subsection{Accuracy of Application Identification}
 \subsubsection{Testing data set}
-Testing data set are mappings of flow attributes and ground truth (also called rules).
-This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan in 2016.
+Testing data set are mappings of flow attributes and ground truth.
+These mappings are also called rules.
+This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan.
 We manually operated applications to generate traffic.
-After the system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on the testing data set.
-There are 14659 rules in total, and there are 137 applications if we view each platform version of an application as one application.
+Each platform of an application took around 50 minutes.
+When the application identification system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on a testing data set.
+There are 14659 rules in total, and there are 137 applications if we count each platform version of an application as one application.
+The testing data set does not contain all of platform version of each application which is in this testing data set.
 
@@
 There are 10 rounds in 10-fold cross validation.
-Each round, we split testing data set into training dataset and classifying dataset.
+We split the data set into 10 subsets.
+At each round, we used 1 of 10 subsets as a classifying data set and the union of the other subsets as a training data set.
+Then we did 10 rounds, and each subset acted as the classifying data set exactly once.
+We implemented Classifier Light and Trainer Light, acting as Classifier and Trainer respectively without the function of analyzing traffic.
+Because there are labels in classifying data set, we can calculate accuracy.
 
@@
 \subsubsection{Mapping of category names}
-We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
+Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
 The main reason is that some application have different ground truth in different operating system.
+After name mapping, there are 99 categories in testing data set.
 
-\subsubsection{Accuracy matrices}
+\subsubsection{Accuracy matrices and results}
 To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq.
@@
 In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category.
-After ten rounds, we calculate average
+After ten rounds, we calculate average F1 score of each category in 10 rounds.
+Table I shows F1 score of each category in top 40 most popular applications in testing data set.
+Next, we calculate average F1 score of all categories in 10 rounds, and we get 0.9062.
+The result (Table.
+\ref{table:classification_result}) shows it achieved high accuracy, which makes QoS possible to do bandwidth control or distribution at application level.
 
@@
 
-\subsubsection{Accuracy analysis}
+\begin{table}[!t]
+\caption{40 POPULAR APPLICATIONS’ AVERAGE F1 SCORE IN 10 ROUNDS}
+\label{table:classification_result}
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+Application name    & Average F1 score    & Application name  & Average F1 score   \\ \hline
+OneDrive            & 0.991255            & Trello            & 0.988889           \\ \hline
+gamerAnimad         & 0.985714            & Dropbox           & 0.985714           \\ \hline
+AmazonMusi          & 0.977461            & MEGAsync          & 0.968889           \\ \hline
+MEGAsync            & 0.968889            & BattleNet         & 0.967812           \\  \hline
+Udacity             & 0.966667            & Lity              & 0.966427            \\ \hline
+Tumblr              & 0.964624            & Asana             & 0.963492            \\ \hline
+Skype               & 0.963117            & Twitch            & 0.963117            \\ \hline
+TeamViewer          & 0.946667            & FileZilla         & 0.946429            \\ \hline
+Agoda               & 0.944764            & TripAdvisor       & 0.942075            \\  \hline
+Pinterest           & 0.936026            & BBCNews           & 0.931049            \\  \hline
+LINE                & 0.923904            & Slack             & 0.920985            \\ \hline
+Twitter             & 0.917906            & Youku             & 0.913925            \\ \hline
+Evernote            & 0.912381            & Snapchat          & 0.912221            \\ \hline
+Weibo               & 0.910872            & WeChat            & 0.906349            \\ \hline
+GoogleDrive         & 0.896612            & Trivago           & 0.895406             \\ \hline
+iTunes              & 0.890464            & Netflix           & 0.876234             \\ \hline
+Facebook            & 0.868641            & Telegram          & 0.862222             \\ \hline
+Airbnb              & 0.857029            & Spotify           & 0.856971             \\ \hline
+Instagram           & 0.833465            & TED               & 0.829277             \\ \hline
+Tmall               & 0.799747            & YouTube           & 0.713084             \\ \hline
+\end{tabular}
+\end{table}
 

### 2017-02-24 netsoft_paper.tex
Limit Youtube Domain

--- 2017-02-24 netsoft_paper.tex
@@
 We integrated with application identification to classify each flow belongs what the application is, consequently.
+In our experiment environment, as shown in Fig.9.
+We use a mirror switch to replicate the whole traffic form SDN switch and provide the application identification system to classify the flows belong which applications.
+Application identification system will upload the result of identification to database.
+Then the controller will get the result from the database and update the flow information of application.
+Therefore, we can use the flow information (5 tuple and the result of identification) to complete our limitation to application.
 We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.

### 2017-02-24 netsoft_paper.tex

--- 2017-02-24 netsoft_paper.tex
@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{./figures/mft_qos_rate_domain_app}
+\caption{Limit the Youtube rate to a network domain.}
+\label{fig:mft_qos_rate_domain_app}
+\end{figure}
+
 \subsection{QoS Evaluation Limit application bandwidth}
+
+There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source.
+We integrated with application identification to classify each flow belongs what the application is, consequently.
+In our experiment environment, as shown in Fig.9.
+We use a mirror switch to replicate the whole traffic form SDN switch and provide the application identification system to classify the flows belong which applications.
+Application identification system will upload the result of identification to database.
+Then the controller will get the result from the database and update the flow information of application.
+Therefore, we can use the flow information (5 tuple and the result of identification) to complete our limitation to application.
+We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.
+Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
+As shown in Figure.?
+In the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps.
+At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain.
+Therefore, we can find out the total traffic of Youtube from this network domain is reducing immediately.
+Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
+When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.
 

### 2017-02-24 netsoft_paper.tex
add table

--- 2017-02-24 netsoft_paper.tex
@@
 \subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
-With the concept of SDN-enabled VNFs, SDN technology work not only for traffic steering but also as a part of network functions.
+With the concept of SDN-enabled VNFs \cite{sdn-enabled}, SDN technology work not only for traffic steering but also as a part of network functions.
 In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig.
@@
 Since the flow table is a crucial component, and we find that single flow table binds us to implement our network functions.
-The [] also mentioned two condition for single flow table is too restrictive.
+The \cite{onf-multi-tables} also mentioned two condition for single flow table is too restrictive.
 The first is a single packet need to perform independent actions based on matching different fields.

### 2017-02-24 netsoft_paper.tex
the third edition

@@
 \includegraphics[width=3in]{./figures/mft_qos_rate_app}
-\caption{Illustration of rate-limiting for a certain host}
+\caption{Illustration of rate-limiting for a certain application.}
 \label{fig:mft_qos_rate_app}
@@
 \includegraphics[width=3in]{./figures/evaluation_classification}
-\caption{Result of Multiple Table Performance Evaluation}
+\caption{Evaluation of Application Identification.}
 \label{fig:evaluation_classification}
@@
 As shown in Fig.
-\ref{fig:qos_limit_host}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service.
+\ref{fig:class_classifying}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service.
 And the OpenFlow-enable switch use the the Edge-Core AS5712-54X switch that operating system is PicOS TM r2.6.
@@
 We used a desktop computer to be the experimental host and record the bandwidth in every 2 seconds.
-In the beginning, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps.
+As shown in Fig \ref{fig:qos_limit_host}, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps in the beginning.
 At \nth{10} seconds, we wanted to limit this host’s bandwidth to 1024Kbps and we added the rule the destination MAC address is matching this desktop computer with a meter of 1024Kbps.
@@
 We integrated with application identification to classify each flow belongs what the application is, consequently.
-In our experiment environment, as shown in Fig.9.
+In our experiment environment, as shown in Fig.
+\ref{fig:class_classifying}.
 We use a mirror switch to replicate the whole traffic form SDN switch and provide the application identification system to classify the flows belong which applications.
@@
 Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
-As shown in Figure.?
-In the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps.
+As shown in Figure.
+\ref{fig:mft_qos_rate_domain_app}, in the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps.
 At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain.

### 2017-02-25 netsoft_paper.tex
fix some typing error

@@
 \subsection{QoS}
-QoS service is mainly for traffic control and we provide three management funtion for QoS service.
+QoS service is mainly for traffic control and we provide two management funtion for QoS service.
 We will introduce these three strategy first and then discuss the flow table order of QoS service in multiple table model.
@@
 \ref{fig:mft_qos_rate_host}.
-In T0, host 1 and host 2 are not limited yet.
-Since host 2 takes up a lot of bandwidth from network in T0~T1, the network administrator sets host 2 rate-limited under 400 Kbps.
-When controller receive this request, marked as (a), it will create a new meter  with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = HOST1 MAC and meter = 1.
+In T0, Host 1 and Host 2 are not limited yet.
+Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps.
+When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1.
 According to our flow table, it will limit the rate of the target host.
@@
 The similar situation also occurs to Host 1 in T2.
-The administrator chooses to set Host1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
+The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
 
@@
 We integrated with application identification to classify each flow belongs what the application is, consequently.
+
 In our experiment environment, as shown in Fig.
@@
 Therefore, we can use the flow information (5 tuple and the result of identification) to complete our limitation to application.
+
 We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.
 Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
+
 As shown in Figure.
@@
 Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
+
 When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.

### 2017-02-25 netsoft_paper.tex
cite frank's paper

--- 2017-02-24 netsoft_paper.tex
@@
 \subsection{Application Identification}
-Application identification is to identify each flow as an application name to enable QoS management system to do bandwidth control or distribution at application level \cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
+Application identification is to identify each flow as an application name to enable QoS management system
+to do bandwidth control or distribution at application level \cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
 The application name means the name of application which establishes the flow.
 A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
-Applications include desktop applications, native mobile applications, and web applications, such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
-We use supervised machine learning and a method based on inspecting domain name service (DNS) responses to do flow classification.
-After application identification system classifies a flow as an application name, it sends the classification result to a server with database.
+Applications include desktop applications, native mobile applications,
+and web applications, such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
+We use supervised machine learning and a method based on inspecting domain name service (DNS)
+responses to do flow classification.
+After application identification system classifies a flow as an application name,
+it sends the classification result to a server with database.
 The server stores the classification result into the database, and waits for requests from QoS management system.
@@
 \section{Application Identification Method}\label{sec:app_identification}
-In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
-In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
+In order to let QoS management system be able to control or distribute bandwidth at application level,
+we designed and implemented an application identification system (also called flow classification system)
+to judge each flow is established by what application.
+In other words, the application identification system can classify each flow as an application name in real time,
+rather than a rough category or a transport layer protocol.
 The corresponding application name of a flow means the name of the application which establishes the flow.
@@
 The system analyzes the packets whose transport protocol are TCP or UDP.
-Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.
+Except for DNS responses, the system only reads headers to get transport layer information of
+packets without inspecting their payload.
 
 \subsection{Architecture of application identification system}
-There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig.
-\ref{fig:class_training} and Fig.
-\ref{fig:class_classifying} respectively.
+There are training phase (also called preparation phase) and classifying phase,
+their architectures are shown in Fig. \ref{fig:class_training} and Fig. \ref{fig:class_classifying} respectively.
 These architectures can be integrated, and do training and classifying in the same time.
@@
 \subsection{Overall procedure of application identification}
-In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
-In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
-The corresponding application name of a flow means the name of the application which establishes the flow.
-We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
-The system analyzes the packets whose transport protocol are TCP or UDP.
-Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.
+In training phase, we generate some data needed by our proposed method.
+In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify;
+otherwise, we use supervised ML to classify.
 
 \subsection{Procedure of Supervised ML in our system}
-In training phase, the architecture is show in Fig.
-\ref{fig:class_training}.
-Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes.
+In training phase, the architecture is show in Fig. \ref{fig:class_training}.
+Flow classification engine is to build classification model by training data from Trainer,
+and update the model when new training data comes.
 Trainer is to analyze traffic from mirror port to get flow attributes.
-After Trainer finishes calculating flow attributes of a flow, it gets ground truth of the flow from Scanner or App Meta Server to generate training data, and sends training data to flow classification engine.
+After Trainer finishes calculating flow attributes of a flow,
+it gets ground truth of the flow from Scanner or App Meta Server to generate training data\cite{Iwai2016},
+and sends training data to flow classification engine.
 App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
-Scanner is to get mappings of 5-tuple and ground truth from OS.
-In classifying phase, the architecture is shown in Fig.
-\ref{fig:class_classifying}.
-Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier.
+Scanner is to get mappings of 5-tuple and ground truth from OS\cite{app-awareness-sdn}.
+In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}.
+Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result,
+and sends classification result to Classifier.
 Classifier is to analyze traffic from mirror port to get flow attributes.
-After Classifier finishes calculating flow attributes of a flow, it use flow attributes to ask flow classification engine for classification result if needed.
+After Classifier finishes calculating flow attributes of a flow,
+it use flow attributes to ask flow classification engine for classification result if needed.
 
@@
 We use Application Round (APPR) proposed by \cite{classfication-cloud} to analyze flow behavior.
-We use number of packets, packet sizes, transmission time, transmission direction, throughput, and APPR to define flow attributes.
+We use number of packets, packet sizes, transmission time,
+transmission direction, throughput, and APPR to define flow attributes.
 There are 69 attributes in total, as defined in our previous work \cite{Chia-Chin-master}.
@@
 We call Weka Java API to build classification model.
-We use three algorithms, namely RandomSupSpace with RandomTree, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
+We use three algorithms, namely RandomSupSpace with RandomTree\cite{TinKamHo1998},
+FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
 
@@
 In training phase, we collect the mappings of server IP and application name.
-A mapping of server IP and application name means the application has ever established connection with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
+A mapping of server IP and application name means the application has ever established connection
+with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
 In classifying phase, we do not use those server IPs which have more than two corresponding applications among the mappings to classify.
@@
 When system detect a flow, we check whether source IP or destination IP of the flow match any of these server IPs.
-If it matches, we regard corresponding application name as classification result; otherwise, we use flow attributes of the flow and classification model of supervised ML to classify.
+If it matches, we regard corresponding application name as classification result;
+otherwise, we use flow attributes of the flow and classification model of supervised ML to classify.
 
@@
 Each platform of an application took around 50 minutes.
-When the application identification system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on a testing data set.
-There are 14659 rules in total, and there are 137 applications if we count each platform version of an application as one application.
+When the application identification system generated rules, it exported them into a file,
+because we wanted to do 10-fold cross validation on a testing data set.
+There are 14659 rules in total,
+and there are 137 applications if we count each platform version of an application as one application.
 The testing data set does not contain all of platform version of each application which is in this testing data set.
@@
 \subsubsection{Validation method}
-Although the system can do online training and classifying, we do offline training and classifying, shown as Fig.
-\ref{fig:evaluation_classification}.
-More specifically, when we did online training to analyze traffic, get ground truth, and export the rules into a file.
-We do 10-fold cross validation on the rules.
-There are 10 rounds in 10-fold cross validation.
-We split the data set into 10 subsets.
+Although the system can do online training and classifying,
+we do offline training and classifying, shown as Fig. \ref{fig:evaluation_classification}.
+More specifically, when we did online training to analyze traffic,
+get ground truth, and export the rules into a file. We do 10-fold cross validation on the rules.
+There are 10 rounds in 10-fold cross validation. We split the data set into 10 subsets.
 At each round, we used 1 of 10 subsets as a classifying data set and the union of the other subsets as a training data set.
@@
 \subsubsection{Mapping of category names}
-Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
+Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset
+before we use training data set to build classification model,
+and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
 The main reason is that some application have different ground truth in different operating system.
@@
 \subsubsection{Accuracy matrices and results}
-To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq.
-(1), Eq.
-(2), and Eq.
-(3) [].
-In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category.
+To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
+as shown in Eq. (1), Eq. (2), and Eq. (3) \cite{muc4}. In each round in 10-fold cross validation,
+we calculate precision and recall of each category to calculate F1 score of each category.
 After ten rounds, we calculate average F1 score of each category in 10 rounds.

### 2017-02-25 netsoft_paper.tex
cite for service description

--- 2017-02-25 netsoft_paper.tex
@@
 \subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
-With the concept of SDN-enabled VNFs \cite{sdn-enabled}, SDN technology work not only for traffic steering but also as a part of network functions.
-In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig.
+With the concept of SDN-enabled VNFs \cite{sdn-enabled} \cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
+In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI) \cite{nfv2014-v121}\cite{nfv2014-v111}\cite{nfv2015}, shown in Fig.
 \ref{fig:desc_nfv_overview}.
 The former is a VNF controller, mainly responsible for dealing with stateful processing.
-The latter is a SDN switch, used for stateless processing.
+The latter is a SDN switch \cite{sp:openflow1.3}, used for stateless processing.
 
@@
 This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
-We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
+We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol \cite{onf}, which was originally designed for this.
 
@@
 
-The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images.
+The infrastructure controller is a composed Docker \ref{seo2014}\ref{compare-vm-container} management server with the ability to manage the Docker resources like containers and images.
 The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
@@
 
-VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module.
+VNF Controllers contains a SDN controller developed with ryu framework \cite{web:ryu} and a remote launcher module.
 The SDN controller does not have a remote launcher module to remotely execute a SDN controller.

### 2017-02-25 netsoft_paper.tex

@@
 The NFV controller run on the Dell PowerEdge R630 Rack Server,
-and the SDN switch use the Pica8 P-3290 switch.
-We use the iPerf2 to generate the network traffic.
+and the SDN switch use the Pica8 P-3290 switch\cite{pica8-switch}.
+We use the iPerf2\cite{iperf} to generate the network traffic.
 The iperf server would connect the public IP address with 140.114.71.178, and then the iperf client connect to the SDN switch, and is controlled by NFV controller.
@@
 \ref{fig:class_classifying}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service.
-And the OpenFlow-enable switch use the the Edge-Core AS5712-54X switch that operating system is PicOS TM r2.6.
+And the OpenFlow-enable switch use the the Edge-Core AS5712-54X\cite{edge-core-switch} switch that operating system is PicOS TM r2.6.
 

### 2017-02-25 netsoft_paper.tex
update

--- 2017-02-25 netsoft_paper.tex
@@
 \graphicspath{{figures/}}
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 \subsection{Service Deployment Model}
-With architecture mentioned in Fig.
-\ref{fig:desc_nfv_overview}, we come up with a network function service deployment model.
+Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig.
+\ref{fig:desc_nfv_overview}.
 Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.
@@
 
-The infrastructure controller is a composed Docker \ref{seo2014}\ref{compare-vm-container} management server with the ability to manage the Docker resources like containers and images.
+The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images \cite{seo2014}\cite{compare-vm-container}.
 The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.

### 2017-02-25 netsoft_paper.tex
the fourth version

@@
 \begin{table}[!t]
-\caption{40 POPULAR APPLICATIONS’ AVERAGE F1 SCORE IN 10 ROUNDS}
+\caption{40 POPULAR APPLICATIONS’ AVERAGE \\ F1 SCORE IN 10 ROUNDS}
 \label{table:classification_result}
@@
 \hline
-Application name    & Average F1 score    & Application name  & Average F1 score   \\ \hline
+Application name    & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}    & Application name  & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}   \\ \hline
 OneDrive            & 0.991255            & Trello            & 0.988889           \\ \hline

### 2017-02-26 netsoft_paper.tex
fix some typing error

--- 2017-02-25 netsoft_paper.tex
@@
 \graphicspath{{figures/}}
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 \subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
-With the concept of SDN-enabled VNFs \cite{sdn-enabled} \cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
-In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI) \cite{nfv2014-v121}\cite{nfv2014-v111}\cite{nfv2015}, shown in Fig.
+With the concept of SDN-enabled VNFs \cite{sdn-enabled}, SDN technology work not only for traffic steering but also as a part of network functions.
+In this idea, network functions have been achieved by the synergies between computer and network infrastructures, shown in Fig.
 \ref{fig:desc_nfv_overview}.
 The former is a VNF controller, mainly responsible for dealing with stateful processing.
-The latter is a SDN switch \cite{sp:openflow1.3}, used for stateless processing.
+The latter is a SDN switch, used for stateless processing.
 
@@
 This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
-We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol \cite{onf}, which was originally designed for this.
+We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
 
@@
 \subsection{Service Deployment Model}
-Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig.
-\ref{fig:desc_nfv_overview}.
+With architecture mentioned in Fig.
+\ref{fig:desc_nfv_overview}, we come up with a network function service deployment model.
 Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.
@@
 
-The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images \cite{seo2014}\cite{compare-vm-container}.
+The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images.
 The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
@@
 
-VNF Controllers contains a SDN controller developed with ryu framework \cite{web:ryu} and a remote launcher module.
+VNF Controllers contains a SDN controller developed with ryu framework and a remote launcher module.
 The SDN controller does not have a remote launcher module to remotely execute a SDN controller.
@@
 As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
-In this paper, our QoS integrates with a flow classification engine and offers the three ways of bandwidth management.
+In this paper, our QoS integrates with a flow classification engine and offers the two ways of bandwidth management.
 
@@
 \subsection{Application Identification}
-Application identification is to identify each flow as an application name to enable QoS management system
-to do bandwidth control or distribution at application level \cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
+Application identification is to identify each flow as an application name to enable QoS management system to do bandwidth control or distribution at application level \cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
 The application name means the name of application which establishes the flow.
 A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
-Applications include desktop applications, native mobile applications,
-and web applications, such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
-We use supervised machine learning and a method based on inspecting domain name service (DNS)
-responses to do flow classification.
-After application identification system classifies a flow as an application name,
-it sends the classification result to a server with database.
+Applications include desktop applications, native mobile applications, and web applications, such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
+We use supervised machine learning and a method based on inspecting domain name service (DNS) responses to do flow classification.
+After application identification system classifies a flow as an application name, it sends the classification result to a server with database.
 The server stores the classification result into the database, and waits for requests from QoS management system.
@@
 QoS service is mainly for traffic control and we provide two management funtion for QoS service.
-We will introduce these three strategy first and then discuss the flow table order of QoS service in multiple table model.
+We will introduce these two strategy first and then discuss the flow table order of QoS service in multiple table model.
 
@@
 In T0, Host 1 and Host 2 are not limited yet.
-Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps.
+Since Host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps.
 When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1.
@@
 Whereas, the sum of bandwidth from this application is always being 1000 Kbps.
-That is, the bandwidth will be dynamically adjusted.
+That is, the bandwidth will be dynamically adjusted according the numbers of connections.
 
+It is worth mentioning that we would not change any rules in flow table and we only change the bandwidth of the correspond meter in the meter table.
+Therefore, there only have a little overhead to switch and controller.
 \begin{figure}[!t]
@@
 \section{Application Identification Method}\label{sec:app_identification}
-In order to let QoS management system be able to control or distribute bandwidth at application level,
-we designed and implemented an application identification system (also called flow classification system)
-to judge each flow is established by what application.
-In other words, the application identification system can classify each flow as an application name in real time,
-rather than a rough category or a transport layer protocol.
+In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
+In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
 The corresponding application name of a flow means the name of the application which establishes the flow.
@@
 The system analyzes the packets whose transport protocol are TCP or UDP.
-Except for DNS responses, the system only reads headers to get transport layer information of
-packets without inspecting their payload.
+Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.
 
 \subsection{Architecture of application identification system}
-There are training phase (also called preparation phase) and classifying phase,
-their architectures are shown in Fig. \ref{fig:class_training} and Fig. \ref{fig:class_classifying} respectively.
+There are training phase (also called preparation phase) and classifying phase, their architectures are shown in Fig.
+\ref{fig:class_training} and Fig.
+\ref{fig:class_classifying} respectively.
 These architectures can be integrated, and do training and classifying in the same time.
@@
 \subsection{Overall procedure of application identification}
-In training phase, we generate some data needed by our proposed method.
-In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify;
-otherwise, we use supervised ML to classify.
+In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application.
+In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
+The corresponding application name of a flow means the name of the application which establishes the flow.
+We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
+The system analyzes the packets whose transport protocol are TCP or UDP.
+Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.
 
 \subsection{Procedure of Supervised ML in our system}
-In training phase, the architecture is show in Fig. \ref{fig:class_training}.
-Flow classification engine is to build classification model by training data from Trainer,
-and update the model when new training data comes.
+In training phase, the architecture is show in Fig.
+\ref{fig:class_training}.
+Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes.
 Trainer is to analyze traffic from mirror port to get flow attributes.
-After Trainer finishes calculating flow attributes of a flow,
-it gets ground truth of the flow from Scanner or App Meta Server to generate training data\cite{Iwai2016},
-and sends training data to flow classification engine.
+After Trainer finishes calculating flow attributes of a flow, it gets ground truth of the flow from Scanner or App Meta Server to generate training data, and sends training data to flow classification engine.
 App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
-Scanner is to get mappings of 5-tuple and ground truth from OS\cite{app-awareness-sdn}.
-In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}.
-Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result,
-and sends classification result to Classifier.
+Scanner is to get mappings of 5-tuple and ground truth from OS.
+In classifying phase, the architecture is shown in Fig.
+\ref{fig:class_classifying}.
+Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier.
 Classifier is to analyze traffic from mirror port to get flow attributes.
-After Classifier finishes calculating flow attributes of a flow,
-it use flow attributes to ask flow classification engine for classification result if needed.
+After Classifier finishes calculating flow attributes of a flow, it use flow attributes to ask flow classification engine for classification result if needed.
 
@@
 We use Application Round (APPR) proposed by \cite{classfication-cloud} to analyze flow behavior.
-We use number of packets, packet sizes, transmission time,
-transmission direction, throughput, and APPR to define flow attributes.
+We use number of packets, packet sizes, transmission time, transmission direction, throughput, and APPR to define flow attributes.
 There are 69 attributes in total, as defined in our previous work \cite{Chia-Chin-master}.
@@
 We call Weka Java API to build classification model.
-We use three algorithms, namely RandomSupSpace with RandomTree\cite{TinKamHo1998},
-FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
+We use three algorithms, namely RandomSupSpace with RandomTree, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
 
@@
 In training phase, we collect the mappings of server IP and application name.
-A mapping of server IP and application name means the application has ever established connection
-with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
+A mapping of server IP and application name means the application has ever established connection with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
 In classifying phase, we do not use those server IPs which have more than two corresponding applications among the mappings to classify.
@@
 When system detect a flow, we check whether source IP or destination IP of the flow match any of these server IPs.
-If it matches, we regard corresponding application name as classification result;
-otherwise, we use flow attributes of the flow and classification model of supervised ML to classify.
+If it matches, we regard corresponding application name as classification result; otherwise, we use flow attributes of the flow and classification model of supervised ML to classify.
 
@@
 Each platform of an application took around 50 minutes.
-When the application identification system generated rules, it exported them into a file,
-because we wanted to do 10-fold cross validation on a testing data set.
-There are 14659 rules in total,
-and there are 137 applications if we count each platform version of an application as one application.
+When the application identification system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on a testing data set.
+There are 14659 rules in total, and there are 137 applications if we count each platform version of an application as one application.
 The testing data set does not contain all of platform version of each application which is in this testing data set.
@@
 \subsubsection{Validation method}
-Although the system can do online training and classifying,
-we do offline training and classifying, shown as Fig. \ref{fig:evaluation_classification}.
-More specifically, when we did online training to analyze traffic,
-get ground truth, and export the rules into a file. We do 10-fold cross validation on the rules.
-There are 10 rounds in 10-fold cross validation. We split the data set into 10 subsets.
+Although the system can do online training and classifying, we do offline training and classifying, shown as Fig.
+\ref{fig:evaluation_classification}.
+More specifically, when we did online training to analyze traffic, get ground truth, and export the rules into a file.
+We do 10-fold cross validation on the rules.
+There are 10 rounds in 10-fold cross validation.
+We split the data set into 10 subsets.
 At each round, we used 1 of 10 subsets as a classifying data set and the union of the other subsets as a training data set.
@@
 \subsubsection{Mapping of category names}
-Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset
-before we use training data set to build classification model,
-and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
+Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset before we use training data set to build classification model, and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
 The main reason is that some application have different ground truth in different operating system.
@@
 \subsubsection{Accuracy matrices and results}
-To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
-as shown in Eq. (1), Eq. (2), and Eq. (3) \cite{muc4}. In each round in 10-fold cross validation,
-we calculate precision and recall of each category to calculate F1 score of each category.
+To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq.
+(1), Eq.
+(2), and Eq.
+(3) [].
+In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category.
 After ten rounds, we calculate average F1 score of each category in 10 rounds.

### 2017-02-26 netsoft_paper.tex
upper case to lower case

@@
 \ref{fig:mft_qos_rate_host}.
-In T0, Host 1 and Host 2 are not limited yet.
-Since Host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps.
-When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1.
+In T0, host 1 and host 2 are not limited yet.
+Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets host 2 rate-limited under 400 Kbps.
+When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of host 1 and meter = 1.
 According to our flow table, it will limit the rate of the target host.
-Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately.
-The similar situation also occurs to Host 1 in T2.
-The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
+Then the traffic from host 2 will reduce and be limited with 400Kbps immediately.
+The similar situation also occurs to host 1 in T2.
+The administrator chooses to set host 1 under 600 Kbps, marked as (b), and then traffic from host 1 will be limited with 600Kbps.
 
@@
 
-We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.
-Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
+We choose YouTube to verify our limitation function of applications and there are 3 Hosts (host 1, host 2 and host 3) in the same network domain.
+Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of host 1, host 2 and host 3.
 

### 2017-02-26 netsoft_paper.tex
upper case to lower case

--- 2017-02-25 netsoft_paper.tex
@@
 \ref{fig:mft_qos_rate_host}.
-In T0, Host 1 and Host 2 are not limited yet.
-Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps.
-When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1.
+In T0, host 1 and host 2 are not limited yet.
+Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets host 2 rate-limited under 400 Kbps.
+When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of host 1 and meter = 1.
 According to our flow table, it will limit the rate of the target host.
-Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately.
-The similar situation also occurs to Host 1 in T2.
-The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
+Then the traffic from host 2 will reduce and be limited with 400Kbps immediately.
+The similar situation also occurs to host 1 in T2.
+The administrator chooses to set host 1 under 600 Kbps, marked as (b), and then traffic from host 1 will be limited with 600Kbps.
 
@@
 
-We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.
-Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
+We choose YouTube to verify our limitation function of applications and there are 3 hosts (host 1, host 2 and host 3) in the same network domain.
+Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of host 1, host 2 and host 3.
 

### 2017-02-26 netsoft_paper.tex
remove inproper paper

@@
 As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
-In this paper, our QoS integrates with a flow classification engine and offers the two ways of bandwidth management.
+In this paper, our QoS integrates with a flow classification engine and offers the three ways of bandwidth management.
 
@@
 QoS service is mainly for traffic control and we provide two management funtion for QoS service.
-We will introduce these two strategy first and then discuss the flow table order of QoS service in multiple table model.
+We will introduce these three strategy first and then discuss the flow table order of QoS service in multiple table model.
 
@@
 \ref{fig:mft_qos_rate_host}.
-In T0, host 1 and host 2 are not limited yet.
-Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets host 2 rate-limited under 400 Kbps.
-When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of host 1 and meter = 1.
+In T0, Host 1 and Host 2 are not limited yet.
+Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets Host 2 rate-limited under 400 Kbps.
+When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of Host 1 and meter = 1.
 According to our flow table, it will limit the rate of the target host.
-Then the traffic from host 2 will reduce and be limited with 400Kbps immediately.
-The similar situation also occurs to host 1 in T2.
-The administrator chooses to set host 1 under 600 Kbps, marked as (b), and then traffic from host 1 will be limited with 600Kbps.
+Then the traffic from Host 2 will reduce and be limited with 400Kbps immediately.
+The similar situation also occurs to Host 1 in T2.
+The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then traffic from Host 1 will be limited with 600Kbps.
 
@@
 Whereas, the sum of bandwidth from this application is always being 1000 Kbps.
-That is, the bandwidth will be dynamically adjusted according the numbers of connections.
+That is, the bandwidth will be dynamically adjusted.
 
-It is worth mentioning that we would not change any rules in flow table and we only change the bandwidth of the correspond meter in the meter table.
-Therefore, there only have a little overhead to switch and controller.
 \begin{figure}[!t]
@@
 After Trainer finishes calculating flow attributes of a flow,
-it gets ground truth of the flow from Scanner or App Meta Server to generate training data\cite{Iwai2016},
+it gets ground truth of the flow from Scanner or App Meta Server to generate training data,
 and sends training data to flow classification engine.
 App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
-Scanner is to get mappings of 5-tuple and ground truth from OS\cite{app-awareness-sdn}.
+Scanner is to get mappings of 5-tuple and ground truth from OS.
 In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}.
@@
 
-We choose YouTube to verify our limitation function of applications and there are 3 hosts (host 1, host 2 and host 3) in the same network domain.
-Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of host 1, host 2 and host 3.
+We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain.
+Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
 

### 2017-02-26 netsoft_paper.tex
5 tuple -> 5-tuple
word to capitalize

@@
 
-\subsubsection{Stateful Processing component (VNF controller in container)}
+\subsubsection{Stateful Processing Component (VNF controller in container)}
 This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
@@
 
-\subsubsection{Stateless Processing component (SDN datapath)}
+\subsubsection{Stateless Processing Component (SDN datapath)}
 Stateless processing component, are implemented by SDN datapath resources, which is optimized for data plane traffic processing.
@@
 
-\subsection{Architecture of the vCPE system}
+\subsection{Architecture of the vCPE System}
 The architecture as shown in Fig. \ref{fig:desc_vcpe_framework} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
@@
 
-\subsubsection{Rate limitation of hosts}
+\subsubsection{Rate Limitation of Hosts}
 When some hosts take up a lot of bandwidth of network, it will make other hosts in slow speed or make traffic congestion.
@@
 
-\subsubsection{Rate limitation of applications}
+\subsubsection{Rate Limitation of Applications}
 There are more and more network’s applications used such as online games, video streaming, conference call, etc.
@@
 
-\subsubsection{The flow table order of forwarding and QoS service}
+\subsubsection{The Flow Table Order of Forwarding and QoS Service}
 Since the location of NAT, DHCP and firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
@@
 
-\subsection{Architecture of application identification system}
+\subsection{Architecture of Application Identification System}
 There are training phase (also called preparation phase) and classifying phase,
@@
 
-\subsection{Overall procedure of application identification}
+\subsection{Overall Procedure of Application Identification}
 In training phase, we generate some data needed by our proposed method.
@@
 
-\subsection{Procedure of Supervised ML in our system}
+\subsection{Procedure of Supervised ML}
 In training phase, the architecture is show in Fig. \ref{fig:class_training}.
@@
 
-\subsection{Flow attributes we adopted in supervised ML}
+\subsection{Flow ttributes of Supervised ML}
 In ML, when system calculates flow attributes, we only use transport layer information of packets which have payload.
@@
 
-\subsection{Algorithms we adopted in supervised ML}
+\subsection{Algorithms of Supervised ML}
 We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato.
@@
 
-\subsection{Procedure of a method based on inspecting DNS response in our system}
+\subsection{Procedure of a Method Based on Inspecting DNS Response}
 In training phase, we collect the mappings of server IP and application name.
@@
 
-\section{PERFORMANCE EVALUATION}
+\section{Performance Evaluation}
 \subsection{Multiple Table Performance}
@@
 \subsection{Accuracy of Application Identification}
-\subsubsection{Testing data set}
+\subsubsection{Testing Data Set}
 Testing data set are mappings of flow attributes and ground truth.
@@
 
-\subsubsection{Validation method}
+\subsubsection{Validation Method}
 Although the system can do online training and classifying,
@@
 
-\subsubsection{Mapping of category names}
+\subsubsection{Mapping of Category Names}
 Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset
@@
 
-\subsubsection{Accuracy matrices and results}
+\subsubsection{Accuracy Matrices and Results}
 To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
@@
 
-\subsection{QoS Evaluation Limit application bandwidth}
+\subsection{QoS Evaluation Limit Application Bandwidth}
 
@@
 Then the controller will get the result from the database and update the flow information of application.
-Therefore, we can use the flow information (5 tuple and the result of identification) to complete our limitation to application.
+Therefore, we can use the flow information (5-tuple and the result of identification) to complete our limitation to application.
 
@@
 
-\section{Conclusion and future works}
+\section{Conclusion and Future Works}
 (Eric)

### 2017-02-26 netsoft_paper.tex
rm un-talked fig

@@
 % Do not put math or special symbols in the title.
-\title{Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch}
+\title{Performance Optimization of Service Chain for vCPE in Small Size Network with OpenFlow Switch}
 
 % author names and IEEE memberships
-% \author{
-% \IEEEauthorblockN{
-% I-Ju Liao\IEEEauthorrefmark{1},
-% Chi-Hsuan Li\IEEEauthorrefmark{1},
-% I-Hsien Hsu\IEEEauthorrefmark{1},
-% Chia-Chi Chen\IEEEauthorrefmark{1},
-% Ching-Hsuan Chen\IEEEauthorrefmark{2},
-% Che-Wei Lin\IEEEauthorrefmark{2},
-% Sheng-Jung Wu\IEEEauthorrefmark{1} and
-% Nen-Fu Huang\IEEEauthorrefmark{1}
-% }
-% \IEEEauthorblockA{
-% \IEEEauthorrefmark{1}
-% Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan\\
-% }
-% \IEEEauthorblockA{\IEEEauthorrefmark{2}
-% Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan\\
-% }
-% }
+\author{
+\IEEEauthorblockN{
+Nen-Fu Huang\IEEEauthorrefmark{1}
+Chia-An Li\IEEEauthorrefmark{1},
+Chi-Hsuan Li\IEEEauthorrefmark{1},
+Chia-Chi Chen\IEEEauthorrefmark{1},
+I-Hsien Hsu\IEEEauthorrefmark{1},
+Che-Chuan Li \IEEEauthorrefmark{1},
+Ching-Hsuan Chen\IEEEauthorrefmark{2} and,
+I-Ju Liao\IEEEauthorrefmark{1}
+}
+\IEEEauthorblockA{
+\IEEEauthorrefmark{1}
+Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan\\
+}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}
+Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan\\
+}
+}
 
@@
 \begin{abstract}
-This Article is about a system how to optimize a service chain in SMB Network.
-There are many vCPE researches on Internet but a few to discuss about organization of Openflow switch and NFVs.
-This paper will propose a framework to optimize and manage NFVs with multi tables of Openflow switch.
-Most of paper talking about how to build architecture in Core Network of ISP, this paper will focus on how to use tables in SDN switches to maximum efficiency on Internet.
+In the last decade, along with the continuously developing of SDN, numerous SDN applications have played important roles in modern network.
+vCPE is one of potential applications can make game change because it can reduce OPEX and CAPEX in the same time.
+This service compose of many technologies with complex architecture like NFV, VNF and Service Chaining.
+Many researches discuss algorithm or mechanism to link any VNFs as a NFV then connect NFVs as a service chain in cloud.
+Nevertheless, the hardware resource and characteristic of SDN switch that never mention before may waste in this architecture.
+In this paper, a vCPE framework with table management based on cloud is implemented.
+The proposed of vCPE framework is to create a VNF using resource in SDN switch and coordinate with service chain on cloud.
+The system is also integrated with an application identification engine based on machine learning algorithms thus providing flow control in vCPE framework with confidence.
+Experimental results show that the framework provide high performance in VNF even compete over legacy equipment.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Software defined networking, vCPE
+SDN, vCPE, VNF, NFV, OpenFlow
 \end{IEEEkeywords}
@@
 \section{Introduction}
-\IEEEPARstart{T}{his} document is a template for Microsoft Word versions 6.0 or later. If you are reading a paper or PDF version of this doconference.
-By Eric
+\IEEEPARstart{S}{DN} has been developing almost a decade since the first Openflow article had be presented in 2008.
+Openflow gives a brand new viewpoint on network research, and makes innovation on industries.
+This technic proposed not just a novel architecture but also bring out more methods of flexible traffic engineering.
+After tons of implementations and researches had been proposed, this architecture exposed some weakness in performance.
+The main concept of this architecture is separating data plane and control plane that put smart control and multi-path into real world.
+But legacy hardware design eventually put this perfect design into reality.
+To achieve high speed packet exchange, ternary content-addressable memory (TCAM) plays an important role in legacy fabric switching.
+This hardware design speed up the packet switching but it also cause high cost and less size problems.
+In the beginning, most of SDN switch used legacy hardware design and just add software API support for temporary solution.
+The smaller TCAM size comes the less flow control rules but it can keep high performance in packet switching.
+It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
+At the same time as SDN was developed, Network Function Virtualization (NFV) has been introduced by Telco operators.
+Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years.
+To replace the old platform with high maintenance cost, they use virtual machine (VM) based on new computers as solutions.
+This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC.
+vCPE manage network functions on operation side to reduce cost which was deployed on cloud.
+Although both of technical ideas are perfect, it still address two critical problems.
+The first one is the lack of hardware support because these ideas need large size of tables to achieve multi VNF support.
+And the other is VM based on cloud may slow down the high speed etwork exchanging network.
+From Pica-8 finished their first OpenFlow switched, there are so many implementation method on a SDN switch.
+Even Open Network Foundation (ONF) has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance.
+Let us take flow entries as example, there are single table and multi table architectures much more based on hardware or software.
+Bandwidth control APIs have been an option in OpenFlow 1.3 but there are many switches still didn’t support these API.
+Even it did support, there are still at least two implementation methods should be noticed.
+Meters and per queue show different ways controlling bandwidth not mention to accuracy of bandwidth.
+Service chain is another concept with vCPE framework because enterprise will apply a bulk of network services.
+This technic inherit weakness of SDN switches and vCPE so there is no standard to unified interface to link all services.
+It’s hard to combine and link all switches and cloud service in such complex situation.
+Different services on cloud must be working fine with different SDN switches and we believe that’s why most of service chain was implemented in VM on the cloud.
+
+Therefore, the purpose of this paper can be summarized as follows:
+
+\begin{enumerate}
+\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus, Pica-8 and Edgecore.
+It supports single table and multi-table implementation in different switches and sends status and information message to Ryu controller.
+This mechanism brings out a novel implementation method of VNF that combine hardware and software operations.
+It not only makes hardware usage more efficiency but also stays maximum flexibility in NFV deployment.
+
+\item To cover most of NFV framework, this vCPE framework offer a multi cloud management feature.
+It can working with OpenDaylight on OpenStack and Ryu on Docker perfectly.
+Users can deploy their NFV features in any kind of VM system even in public cloud, and monitor it in same system.
+\item To control flows with confidence, an application identification algorithm might be in consideration.
+The first thing comes out must be Intrusion Detection System (IDS) or Intrusion Prevention System (IPS) but there are 2 major weakness of this two kind of technic.
+The first is it spends a lot of time to identify connections, and network speed may hang on IPS.
+The other is it may can’t figure out encryption connections because not all of IDS or IPS have key matching feature.
+Most of modern cloud applications use https protocol as basic communication method which makes matter even worse.
+This study gives an algorithm to identify applications with statistical method with machine learning.
+The algorithm only use connection “attributes” to train an identification models such as packet direction, packet length.
+Afterward, the algorithm can identify network applications by this model.
+Even encryption connection can be identified with high accuracy because the algorithm monitor packet in statistical way instead of trying to decode it.
+\item To analysis performance of this vCPE framework, this study integrate all of functions mention above to evaluate it even compare with the legacy network equipments.
+This paper is structured as follows.
+Section II introduce the overall architecture of the framework what this study proposed.
+Section III describe multi table management mechanism in the beginning.
+Rest of section will show how to implement VNF with the mechanism.
+Section IV considers application identification in SDN because system can do nothing if the system doesn’t know what kind of application running on the network.
+Section V analytically performance of vCPE framework what we proposed include comparison with traditional network devices.
+Conclusion and future works will summary in the last section.
+\end{enumerate}
 
@@
 
-Below is a examples to show how the NAT service modify the IP address and port number, as shown in Fig.
-\ref{fig:mft_nat}.
+Below is a examples to show how the NAT service modify the IP address and port number.
 For outgoing packet, the SDN switch doesn’t have any flow entry in flow table, so the Packet-in event will be triggered at the beginning.

### 2017-02-26 netsoft_paper.tex
fix some refernce warning

@@
 \usepackage[super]{nth}
-\interdisplaylinepenalty=2500
 
@@
 % Do not put math or special symbols in the title.
-\title{Performance Optimization of Service Chain for vCPE in Small Size Network with OpenFlow Switch}
+\title{Performance Optimization of Service Chain \\ for vCPE in Small Size Network with OpenFlow Switch}
 
@@
 To replace the old platform with high maintenance cost, they use virtual machine (VM) based on new computers as solutions.
-This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC.
+This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC.
 vCPE manage network functions on operation side to reduce cost which was deployed on cloud.
@@
 \hline
-Application name    & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}    & Application name  & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}   \\ \hline
+\begin{tabular}[c]{@{}l@{}} Application \\ name\end{tabular}    & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}    & \begin{tabular}[c]{@{}l@{}}Application \\ name\end{tabular}  & \begin{tabular}[c]{@{}l@{}}Average \\ F1 score\end{tabular}   \\ \hline
 OneDrive            & 0.991255            & Trello            & 0.988889           \\ \hline

### 2017-02-28 netsoft_paper.tex
fix style

@@
 % Do not put math or special symbols in the title.
-\title{Performance Optimization of Service Chain \\ for vCPE in Small Size Network with OpenFlow Switch}
+\title{Performance Optimization of Service Chain \\ for vCPE in Small Size Network \\ with OpenFlow Switch}
 
@@
 Chia-Chi Chen\IEEEauthorrefmark{1},
-I-Hsien Hsu\IEEEauthorrefmark{1},
+I-Hsien Hsu\IEEEauthorrefmark{1}, \\
 Che-Chuan Li \IEEEauthorrefmark{1},
@@
 }
+
 \IEEEauthorblockA{
@@
 \section{Introduction}
-\IEEEPARstart{S}{DN} has been developing almost a decade since the first Openflow article had be presented in 2008.
+\IEEEPARstart{S}{DN} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
 Openflow gives a brand new viewpoint on network research, and makes innovation on industries.
@@
 Therefore, the purpose of this paper can be summarized as follows:
-
 \begin{enumerate}
@@
 Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules.
-The flow table defines all matching and corresponding processing, thus playing an important role to executive network function.
+The flow table\cite{sdn-ft} defines all matching and corresponding processing, thus playing an important role to executive network function.
 

### 2017-02-28 netsoft_paper.tex
citation fin

@@
 \section{Introduction}
-\IEEEPARstart{S}{DN} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
-Openflow gives a brand new viewpoint on network research, and makes innovation on industries.
+\IEEEPARstart{S}{DN}\cite{sdn-new-norm} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
+Openflow\cite{sp:openflow1.3} gives a brand new viewpoint on network research, and makes innovation on industries.
 This technic proposed not just a novel architecture but also bring out more methods of flexible traffic engineering.
@@
 It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
-At the same time as SDN was developed, Network Function Virtualization (NFV) has been introduced by Telco operators.
+At the same time as SDN was developed, Network Function Virtualization (NFV) \cite{nfvwp}\cite{laptop-sdn} has been introduced by Telco operators.
 Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years.
 To replace the old platform with high maintenance cost, they use virtual machine (VM) based on new computers as solutions.
-This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC.
+This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC\cite{nec-vcpe}.
 vCPE manage network functions on operation side to reduce cost which was deployed on cloud.
@@
 The first one is the lack of hardware support because these ideas need large size of tables to achieve multi VNF support.
-And the other is VM based on cloud may slow down the high speed etwork exchanging network.
-From Pica-8 finished their first OpenFlow switched, there are so many implementation method on a SDN switch.
-Even Open Network Foundation (ONF) has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance.
+And the other is VM based on cloud may slow down the high speed network exchanging network \cite{nfv-placemet}, \cite{nfv-placement-model}.
+From Pica8 \cite{pica8-switch} finished their first OpenFlow switches, there are so many implementation method on a SDN switch.
+Even Open Network Foundation (ONF)\ref{onf} has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance.
 Let us take flow entries as example, there are single table and multi table architectures much more based on hardware or software.
@@
 Meters and per queue show different ways controlling bandwidth not mention to accuracy of bandwidth.
-Service chain is another concept with vCPE framework because enterprise will apply a bulk of network services.
+Service chain \cite{service-chain} is another concept with vCPE framework because enterprise will apply a bulk of network services.
 This technic inherit weakness of SDN switches and vCPE so there is no standard to unified interface to link all services.
@@
 \begin{enumerate}
-\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus, Pica-8 and Edgecore.
+\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus, Pica8 and Edgecore.
 It supports single table and multi-table implementation in different switches and sends status and information message to Ryu controller.
@@
 \item To cover most of NFV framework, this vCPE framework offer a multi cloud management feature.
-It can working with OpenDaylight on OpenStack and Ryu on Docker perfectly.
+It can working with OpenDaylight\cite{opendaylight} on OpenStack\cite{openstack} and Ryu\cite{web:ryu} on Docker\cite{docker} perfectly.
 Users can deploy their NFV features in any kind of VM system even in public cloud, and monitor it in same system.
@@
 \item To analysis performance of this vCPE framework, this study integrate all of functions mention above to evaluate it even compare with the legacy network equipments.
+\end{enumerate}
+
 This paper is structured as follows.
@@
 Conclusion and future works will summary in the last section.
-\end{enumerate}
 
@@
 Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig.
-\ref{fig:desc_nfv_overview}.
+\ref{fig:desc_nfv_overview} based on the NetFATE (Network Function at the Edge) approach \cite{netfate}.
 Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.

### 2017-03-01 netsoft_paper.tex
remove related work
add bigraphy for i-hsien, chia-chi, ching-hsuan

@@
 From Pica8 \cite{pica8-switch} finished their first OpenFlow switches, there are so many implementation method on a SDN switch.
-Even Open Network Foundation (ONF)\ref{onf} has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance.
+Even Open Network Foundation (ONF)\cite{onf} has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance.
 Let us take flow entries as example, there are single table and multi table architectures much more based on hardware or software.
@@
 Conclusion and future works will summary in the last section.
-
-\section{Related Work}
-By Eric
 
@@
 The Source NAT (SNAT) is typically used by internal users (inside private network) to access the Internet (outside network).
-The network function uses the action “Set-Field”, which defined by OpenFlow protocol for rewriting packet header fields.
+The network function uses the action “Set-Field”, which deined by OpenFlow protocol for rewriting packet header fields.
 Via vCPE GUI interface, the network manager can set up the WAN port of SDN switch, public IP, default gateway, and local network address when using this function.
@@
 
+\begin{IEEEbiography}
+{Nen-Fu Huang}
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+{Chia-An Lee} was born in 1988. He received the B.S. degree in Undergraduate Program of Computer Science in 2010 from National Tsing Hua University, Hsinchu, Taiwan.
+Currently he is a Ph.D student of the Department of Computer Science in National Tsing Hua University.
+His research include Software Define Network ,Network Function Virtualization, Moocs, and data analytics.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+{Chi-Hsuan Li} received the B.S.
+degree in Undergraduate Program of Electrical Engineering and Computer Science in 2015 from National Tsing Hua University, Hsinchu, Taiwan.
+Currently she is a graduate student of the Department of Computer Science in National Tsing Hua University.
+Her research interest is Software Define Network and Network Function Virtualization.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/chia-chi.jpg}}]
+{Chia-Chi Chen} was born in 1994 and  received the B.S. degree in Computer Science in 2016 from National Tsing Hua University, Taiwan.
+He is a graduate student and major in Computer Science from National Tsing Hua University now.
+Mr. Chen research chiefly focuses on Software Defined Network in High Speed Network Lab at National Tsing Hua University.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/i-hsien.jpg}}]
+{I-Hsien Hsu} was born in 1994 and  received the B.S. degree in Computer Science in 2016 from National Tsing Hua University, Taiwan.
+He is a graduate student and major in Computer Science from National Tsing Hua University now.
+His research mainly focuses on Software Defined Network in High Speed Network Lab at National Tsing Hua University.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+{Che-Chuan Li}
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/chin-hsuan.jpg}}]
+{Ching-Hsuan Chen} received the bachelor degree in Computer Science department in 2016 from National Tsing Hua University, Hsinchu, Taiwan.
+Now he is a graduate student of the Institute of Communications Engineering in the same university, National Tsing Hua University.
+His research mainly focuses on Software Define Network and Network Function Virtualization.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}
+{I-Ju Liao}
+\end{IEEEbiography}
+
 \end{document}

### 2017-03-01 netsoft_paper.tex
add conclusion

@@
 This service compose of many technologies with complex architecture like NFV, VNF and Service Chaining.
-Many researches discuss algorithm or mechanism to link any VNFs as a NFV then connect NFVs as a service chain in cloud.
+Many researches discuss algorithm or mechanism to link multiple VNFs as a single NFV then connect NFVs as a service chain in cloud.
 Nevertheless, the hardware resource and characteristic of SDN switch that never mention before may waste in this architecture.
-In this paper, a vCPE framework with table management based on cloud is implemented.
-The proposed of vCPE framework is to create a VNF using resource in SDN switch and coordinate with service chain on cloud.
+In this paper, a vCPE framework with multiple flow table management based on cloud is implemented.
+The proposed of vCPE framework is to create a SDN-enabled VNF using both resoures in SDN switch and on cloud and these VNFs can be deployed as edge.
 The system is also integrated with an application identification engine based on machine learning algorithms thus providing flow control in vCPE framework with confidence.
-Experimental results show that the framework provide high performance in VNF even compete over legacy equipment.
+Experimental results show that the framework provide performance in VNF compete over single table SDN application.
 \end{abstract}
@@
 \section{Introduction}
-\IEEEPARstart{S}{DN}\cite{sdn-new-norm} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
-Openflow\cite{sp:openflow1.3} gives a brand new viewpoint on network research, and makes innovation on industries.
+\IEEEPARstart{S}{DN}\cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
+Openflow\cite{sp:openflow13} gives a brand new viewpoint on network research, and makes innovation on industries.
 This technic proposed not just a novel architecture but also bring out more methods of flexible traffic engineering.
@@
 It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
-At the same time as SDN was developed, Network Function Virtualization (NFV) \cite{nfvwp}\cite{laptop-sdn} has been introduced by Telco operators.
+At the same time as SDN was developed, Network Function Virtualization (NFV)\cite{nfvwp},\cite{nfv-survey},\cite{laptop-sdn} has been introduced by Telco operators.
 Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years.
@@
 Although both of technical ideas are perfect, it still address two critical problems.
-The first one is the lack of hardware support because these ideas need large size of tables to achieve multi VNF support.
-And the other is VM based on cloud may slow down the high speed network exchanging network \cite{nfv-placemet}, \cite{nfv-placement-model}.
-From Pica8 \cite{pica8-switch} finished their first OpenFlow switches, there are so many implementation method on a SDN switch.
+The first one is the lack of hardware support because these ideas need large size of flow tables to achieve multi VNF support.
+And the other is VM based on cloud may slow down the high speed network exchanging network\cite{nfv-placemet},\cite{nfv-placement-model}.
+From Pica8\cite{pica8-switch} finished their first OpenFlow switches, there are so many implementation method on a SDN switch.
 Even Open Network Foundation (ONF)\cite{onf} has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance.
-Let us take flow entries as example, there are single table and multi table architectures much more based on hardware or software.
+Let us take flow entries as example, there are single flow table and multiple flow table architectures much more based on hardware or software.
 Bandwidth control APIs have been an option in OpenFlow 1.3 but there are many switches still didn’t support these API.
@@
 Meters and per queue show different ways controlling bandwidth not mention to accuracy of bandwidth.
-Service chain \cite{service-chain} is another concept with vCPE framework because enterprise will apply a bulk of network services.
+Service chain\cite{service-chain} is another concept with vCPE framework because enterprise will apply a bulk of network services.
 This technic inherit weakness of SDN switches and vCPE so there is no standard to unified interface to link all services.
@@
 \begin{enumerate}
-\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus, Pica8 and Edgecore.
+\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus\cite{lagopus-switch}, Pica8\cite{pica8-switch} and Edgecore\cite{edge-core-switch}.
 It supports single table and multi-table implementation in different switches and sends status and information message to Ryu controller.
@@
 It not only makes hardware usage more efficiency but also stays maximum flexibility in NFV deployment.
-
 \item To cover most of NFV framework, this vCPE framework offer a multi cloud management feature.
@@
 Even encryption connection can be identified with high accuracy because the algorithm monitor packet in statistical way instead of trying to decode it.
-\item To analysis performance of this vCPE framework, this study integrate all of functions mention above to evaluate it even compare with the legacy network equipments.
+\item To analysis performance of this vCPE framework, this study integrate all of functions mention above to evaluate it compare with the single-table mechanism.
 \end{enumerate}
@@
 \subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
-With the concept of SDN-enabled VNFs \cite{sdn-enabled} \cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
-In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI) \cite{nfv2014-v121}\cite{nfv2014-v111}\cite{nfv2015}, shown in Fig.
+With the concept of SDN-enabled VNFs\cite{sdn-enabled}\cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
+In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI)\cite{nfv2014-v121}\cite{nfv2014-v111}\cite{nfv2015}, shown in Fig.
 \ref{fig:desc_nfv_overview}.
 The former is a VNF controller, mainly responsible for dealing with stateful processing.
-The latter is a SDN switch \cite{sp:openflow1.3}, used for stateless processing.
+The latter is a SDN switch used for stateless processing.
 
@@
 \subsection{Service Deployment Model}
-Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig.
-\ref{fig:desc_nfv_overview} based on the NetFATE (Network Function at the Edge) approach \cite{netfate}.
+Different from some related works are discussed about virtualizing network functions located in PE devices\cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig.
+\ref{fig:desc_nfv_overview} based on the NetFATE (Network Function at the Edge) approach\cite{netfate}.
 Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.
@@
 
-VNF Controllers contains a SDN controller developed with ryu framework \cite{web:ryu} and a remote launcher module.
+VNF Controllers contains a SDN controller developed with ryu framework\cite{web:ryu} and a remote launcher module.
 The SDN controller does not have a remote launcher module to remotely execute a SDN controller.
@@
 Application identification is to identify each flow as an application name to enable QoS management system
-to do bandwidth control or distribution at application level \cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
+to do bandwidth control or distribution at application level\cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
 The application name means the name of application which establishes the flow.
@@
 Since the flow table is a crucial component, and we find that single flow table binds us to implement our network functions.
-The \cite{onf-multi-tables} also mentioned two condition for single flow table is too restrictive.
+The\cite{onf-multi-tables} also mentioned two condition for single flow table is too restrictive.
 The first is a single packet need to perform independent actions based on matching different fields.
@@
 In ML, when system calculates flow attributes, we only use transport layer information of packets which have payload.
-We use Application Round (APPR) proposed by \cite{classfication-cloud} to analyze flow behavior.
+We use Application Round (APPR) proposed by\cite{classfication-cloud} to analyze flow behavior.
 We use number of packets, packet sizes, transmission time,
 transmission direction, throughput, and APPR to define flow attributes.
-There are 69 attributes in total, as defined in our previous work \cite{Chia-Chin-master}.
+There are 69 attributes in total, as defined in our previous work\cite{Chia-Chin-master}.
 
@@
 To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
-as shown in Eq. (1), Eq. (2), and Eq. (3) \cite{muc4}. In each round in 10-fold cross validation,
+as shown in Eq. (1), Eq. (2), and Eq. (3)\cite{muc4}. In each round in 10-fold cross validation,
 we calculate precision and recall of each category to calculate F1 score of each category.
@@
 
-\subsection{QoS Evaluation Limit Host bandwidth}
+\subsection{Integration Evaluation: QoS Limit Host bandwidth Evaluation}
 
@@
 
-\subsection{QoS Evaluation Limit Application Bandwidth}
+\subsection{Integration Evaluation: QoS Limit Application Bandwidth Evaluation}
 
@@
 
-\section{Conclusion and Future Works}
-(Eric)
+\section{Conclusion}
+The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implpemented with multiple flow table management model.
+In this way, the customers only need a SDN switch at local network, and some network functions that could not have been done by single table machanism are also resolved.
+The experimental results show that the framework provide performance in VNF compete over single table SDN application.
+The integration evaluation also show its flexibility to integrate with any bonus applicaion identification system, IDS or IPS.
 
@@
 \begin{IEEEbiography}
-{Che-Chuan Li}
+{Che-Chuan Li} was born in Tainan City, Taiwan, in 1993.
+He received the B.S.
+degree in computer science from National Tsing Hua University, Hsinchu, Taiwan, in 2015.
+He is currently pursuing the M.S.
+degree in computer science at National Tsing Hua University, Hsinchu, Taiwan.
 \end{IEEEbiography}

### 2017-03-01 netsoft_paper.tex
add che-chaun picture

@@
 This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC\cite{nec-vcpe}.
-vCPE manage network functions on operation side to reduce cost which was deployed on cloud.
+vCPE manage network functions on operation side to reduce cost which was deployed on cloud \cite{cloud4nfv}.
 Although both of technical ideas are perfect, it still address two critical problems.
@@
 With the concept of SDN-enabled VNFs\cite{sdn-enabled}\cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
-In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI)\cite{nfv2014-v121}\cite{nfv2014-v111}\cite{nfv2015}, shown in Fig.
+In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI)\cite{nfv2014-v121},\cite{nfv2015}, shown in Fig.
 \ref{fig:desc_nfv_overview}.
@@
 \subsection{Architecture of the vCPE System}
-The architecture as shown in Fig. \ref{fig:desc_vcpe_framework} including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
+The architecture of the vCPE system is adapted from \cite{nfv2014-v111}, shown in Fig.
+\ref{fig:desc_vcpe_framework}, including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
 The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
@@
 \begin{IEEEbiography}
+[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/che-chuan.jpg}}]
 {Che-Chuan Li} was born in Tainan City, Taiwan, in 1993.

### 2017-03-01 netsoft_paper.tex
some fi x

@@
 \usepackage{csquotes}
-\usepackage[flushleft]{threeparttable}
 \usepackage{hyperref}
+\usepackage{cite}
 \usepackage{url}
 \usepackage{amsmath}
+\usepackage[flushleft]{threeparttable}
 \usepackage[super]{nth}
@@
 % author names and IEEE memberships
-\author{
-\IEEEauthorblockN{
-Nen-Fu Huang\IEEEauthorrefmark{1}
+\author{\IEEEauthorblockN{
+Nen-Fu Huang\IEEEauthorrefmark{1},
 Chia-An Li\IEEEauthorrefmark{1},
@@
 I-Hsien Hsu\IEEEauthorrefmark{1}, \\
-Che-Chuan Li \IEEEauthorrefmark{1},
-Ching-Hsuan Chen\IEEEauthorrefmark{2} and,
-I-Ju Liao\IEEEauthorrefmark{1}
-}
+Che-Chuan Li\IEEEauthorrefmark{1},
+Ching-Hsuan Chen\IEEEauthorrefmark{2} and
+I-Ju Liao\IEEEauthorrefmark{1}}
 
@@
 \IEEEauthorrefmark{1}
-Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan\\
-}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}
-Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan\\
-}
+Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan}
+\IEEEauthorblockA{
+\IEEEauthorrefmark{2}
+Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan}
 }
@@
 \begin{abstract}
-In the last decade, along with the continuously developing of SDN, numerous SDN applications have played important roles in modern network.
-vCPE is one of potential applications can make game change because it can reduce OPEX and CAPEX in the same time.
-This service compose of many technologies with complex architecture like NFV, VNF and Service Chaining.
-Many researches discuss algorithm or mechanism to link multiple VNFs as a single NFV then connect NFVs as a service chain in cloud.
+In the last decade, along with the continuously developing of software defined network (SDN), numerous SDN applications have played important roles in modern network.
+Virtual Customer Premise Equipment (vCPE) is one of potential applications can make game change because it can reduce OPEX and CAPEX in the same time.
+This service compose of many technologies with complex architecture like Virtualized Network Function (VNFs) and Service Chaining.
+Many researches discuss algorithm or mechanism to link multiple VNFs as a single Network Function Virtualization (NFV) then connect NFVs as a service chain in cloud.
 Nevertheless, the hardware resource and characteristic of SDN switch that never mention before may waste in this architecture.
@@
 \begin{IEEEkeywords}
-SDN, vCPE, VNF, NFV, OpenFlow
+Software defined network, virtual customer premise equipment, VNF, NFV, OpenFlow
 \end{IEEEkeywords}
@@
 \section{Introduction}
-\IEEEPARstart{S}{DN}\cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
+\IEEEPARstart{S}{oftware} Define Network \cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
 Openflow\cite{sp:openflow13} gives a brand new viewpoint on network research, and makes innovation on industries.
@@
 It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
-At the same time as SDN was developed, Network Function Virtualization (NFV)\cite{nfvwp},\cite{nfv-survey},\cite{laptop-sdn} has been introduced by Telco operators.
+At the same time as SDN was developed, Network Function Virtualization (NFV) \cite{nfvwp}\cite{nfv-survey}\cite{laptop-sdn} has been introduced by Telco operators.
 Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years.
@@
 \subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
-With the concept of SDN-enabled VNFs\cite{sdn-enabled}\cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
+The use of SDN-enabled VNFs\cite{sdn-enabled}\cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
 In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI)\cite{nfv2014-v121},\cite{nfv2015}, shown in Fig.

### 2017-03-02 netsoft_paper.tex
fix some style
fix picture

@@
 
+\usepackage{graphicx}
 \usepackage{indentfirst}
-\usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subfigure}
-\usepackage{enumerate}
-\usepackage{epstopdf}
-\usepackage{csquotes}
-\usepackage{hyperref}
 \usepackage{cite}
 \usepackage{url}
+\usepackage{hyperref}
 \usepackage{amsmath}
+\usepackage{fixltx2e}
+\usepackage{caption}
+\usepackage{enumerate}
 \usepackage[flushleft]{threeparttable}
 \usepackage[super]{nth}
-
-\graphicspath{{figures/}}
 
@@
 \IEEEauthorrefmark{1}
-Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan}
+Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan} \\
 \IEEEauthorblockA{
@@
 \subsection{Architecture of the vCPE System}
-The architecture of the vCPE system is adapted from \cite{nfv2014-v111}, shown in Fig.
+The architecture of the vCPE system is adapted from the NFV-MANO architectural framework in \cite{nfv2014-v111}, shown in Fig.
 \ref{fig:desc_vcpe_framework}, including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
@@
 \centering
-\includegraphics[width=3in]{./figures/desc_vcpe_framework}
+\includegraphics[width=3.5in]{./figures/desc_vcpe_framework}
 \caption{Architecture of the vCPE framework.}
@@
 
-\newpage
 \bibliographystyle{ieeetr}

### 2017-03-02 netsoft_paper.tex
fix typo

@@
 % Do not put math or special symbols in the title.
-\title{Performance Optimization of Service Chain \\ for vCPE in Small Size Network \\ with OpenFlow Switch}
+\title{Performance Optimization of Service Chain \\ for vCPE in Small Networks \\ with OpenFlow Switch}
 
@@
 Virtual Customer Premise Equipment (vCPE) is one of potential applications can make game change because it can reduce OPEX and CAPEX in the same time.
-This service compose of many technologies with complex architecture like Virtualized Network Function (VNFs) and Service Chaining.
+This service compose of many technologies with complex architecture like Virtualized Network Functions (VNFs) and Service Chaining.
 Many researches discuss algorithm or mechanism to link multiple VNFs as a single Network Function Virtualization (NFV) then connect NFVs as a service chain in cloud.

### 2017-03-02 netsoft_paper.tex
wallace fix section III

@@
 \begin{IEEEkeywords}
-Software defined network, virtual customer premise equipment, VNF, NFV, OpenFlow
+Software defined network, virtual customer premise equipment, network function virtualization, OpenFlow
 \end{IEEEkeywords}
@@
 \section{Introduction}
-\IEEEPARstart{S}{oftware} Define Network \cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
+\IEEEPARstart{S} oftware Define Network \cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
 Openflow\cite{sp:openflow13} gives a brand new viewpoint on network research, and makes innovation on industries.
@@
 \section{System Description}
-\subsection{Overview of Network Function}\label{ssec:desc_nfv_overview}
-The use of SDN-enabled VNFs\cite{sdn-enabled}\cite{manage-nve}, SDN technology work not only for traffic steering but also as a part of network functions.
-In this idea, network functions have been achieved by the synergies between computer infrastructures(NFV) and network infrastructures(NFVI)\cite{nfv2014-v121},\cite{nfv2015}, shown in Fig.
-\ref{fig:desc_nfv_overview}.
-The former is a VNF controller, mainly responsible for dealing with stateful processing.
-The latter is a SDN switch used for stateless processing.
-
-\subsubsection{Stateful Processing Component (VNF controller in container)}
-This component have to control the workflow, keep the state associated with the VNF, and provide interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
-We use SDN controller to implement the NFV controller and it’s worth noting that we use southbound APIs of SDN controller framework to handle the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this.
-
-\subsubsection{Stateless Processing Component (SDN datapath)}
-Stateless processing component, are implemented by SDN datapath resources, which is optimized for data plane traffic processing.
-Since SDN switch have decoupled the control plane and data plane, so it can accept the control message from the stateful processing component.
-
-Using the advantages of this architecture, we can assign stateless or light-weight state work to the SDN switch, for example, packet filtering and packet counting, to load-off the computing resources.
-If we want to update our service, we just need to update the stateful component, since the stateless component just follow the command from stateful components
+\subsection{Overview of Network Functions} \label{ssec:desc_nfv_overview}
+Our network functions (Fig.
+\ref{fig:desc_nfv_overview}) are designed with SDN-enabled NFV architecture concept \cite{sdn-enabled}, using the synergies between computer infrastructures (NFVs) and network infrastructures (NFVIs) \cite{nfv2014-v121},\cite{nfv2015}.
+An NFV is a VNF controller, mainly used for addressing stateful processing and NFVI is an SDN switch used for stateless processing.
 
@@
 \centering
-\includegraphics[width=3in]{./figures/desc_nfv_overview}
-\caption{Overview of network function.}
+\includegraphics[width=2.5in]{./figures/desc_nfv_overview}
+\caption{Overview of network functions.}
 \label{fig:desc_nfv_overview}
@@
 
+\subsubsection{Stateful Processing Component (VNF Controller in VM/Container)}
+This component is used to control the workflow, maintain the state associated with the VNF, and provide an interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
+We used an SDN controller to implement the NFV controller; and notably, we use southbound APIs of the SDN controller framework to manage the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this purpose.
+
+\subsubsection{Stateless Processing Component (SDN Datapath)}
+Stateless processing component is implemented by SDN datapath resources and is optimized for data plane traffic processing.
+Because an SDN switch can be decoupled with control plane and data plane, the switch can accept the control messages from the stateful processing component.
+
+By using the advantages of this architecture, we can assign stateless or light-weight state work to the SDN switch (e.g., packet filtering and packet counting) to reduce the load on the computing resources.
+If we want to update our service, we are required to update only the stateful component, because the stateless component merely follows the commands from stateful component.
+
 \subsection{Service Deployment Model}
-Different from some related works are discussed about virtualizing network functions located in PE devices\cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig.
-\ref{fig:desc_nfv_overview} based on the NetFATE (Network Function at the Edge) approach\cite{netfate}.
-Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.
+Unlike a related study that explored the virtualization of network function in PE devices \cite{vcpe-enhance}, we introduced a network function service deployment model based on the NetFATE (Network Function at the Edge) approach \cite{netfate}; the archtecture of the model is presented in Fig.
+\ref{fig:desc_nfv_overview}.
+Because computing infrastructures involves algorithms and policies and the generic network devices perform only stateless processing, the customers need to simply purchase a general SDN switch for their home gateway.
+They can obtain a different network function service by subscribing to a different the NFV controller through our vCPE platform.
 
@@
 \ref{fig:desc_service_deployment} illustrates the service deployment model.
-Each green area is a local network domain of customer.
-At the gateway of this domain, there’s a SDN-enabled switch.
+Each green area is a local network domain of the customer.
+An SDN-enabled switch is presented at the gateway of this domain.
 The customer can subscribe to our vCPE service through our dashboard.
-After subscribing, the vCPE system will create a new docker container, in which running a SDN controller we developed.
-The customer only need to setup the gateway SDN switch to connect the SDN controller by the OpenFlow protocol, then the switch will handle these service.
+After subscription, the vCPE system creates a new Docker container in which an SDN controller is running.
+The customer only needs to set up the gateway SDN switch to connect the SDN controller through the OpenFlow protocol; thereafter, the switch will executes the service.
 
@@
 
-\subsection{Architecture of the vCPE System}
-The architecture of the vCPE system is adapted from the NFV-MANO architectural framework in \cite{nfv2014-v111}, shown in Fig.
-\ref{fig:desc_vcpe_framework}, including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
-The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
-Each component is introduced in the subsection below.
+\subsection{vCPE System Architecture}
+The architecture (Fig.
+\ref{fig:desc_vcpe_framework}) is adapted from the NFV-MANO architectural framework in \cite{nfv2014-v111}, including an infrastructure controller, an infrastructure orchestrator, a cloud database, VNF controllers and a VNF Orchestrator.
+The infrastructure orchestrator, VNF orchestrator and cloud database are web servers.
+Each component is introduced in the following subsection.
 
@@
 \centering
-\includegraphics[width=3.5in]{./figures/desc_vcpe_framework}
+\includegraphics[width=3in]{./figures/desc_vcpe_framework}
 \caption{Architecture of the vCPE framework.}
@@
 
-The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images.
-The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
+The infrastructure controller comprises a Docker management server that can manage the Docker resources like containers.
+The infrastructure does not manage  customer authentication or maintaining the state of the running service; however, it follows the request from the infrastructure orchestrator to create, delete, start, stop, and inspect containers and VMs.
 
@@
 
-The infrastructure orchestrator plays the key role of our system.
-It connecting and automating of workflows when we deploy our services.
-When a customer subscribes, the infrastructure orchestrator authenticates the customer first, next it will call the infrastructure controller to create a container for this customer, and update information in database afterwards.
-It handle the entire lifecycle of our vCPE service.
+The infrastructure orchestrator plays a key role in our system.
+It connects and automates the workflows when our services are deployed.
+When a customer subscribes to our service, the infrastructure orchestrator first authenticates the customer, calls the infrastructure controller to create a container or a VM for the customer, and then updates the information in the database.
+The infrastructure orchestrator controls the entire lifecycle of our vCPE service.
 
@@
 
-The cloud database is used for restoring the of our vCPE services, which include each customer’s credential, customer’s container settings and virtual CPE service states.
-The cloud database is using PostgreSQL, which is a open source, easily customized and object-relational database system.
-Only Infrastructure Orchestrator has permissions to access cloud database.
+The cloud database is used for restoring the metadata of our vCPE services, which include each customer’s credentials, customer’s container/VM settings, and virtual CPE service states.
+The cloud database employs PostgreSQL, which is an open source, easily customizable and object-relational database system.
+Only the infrastructure orchestrator has permissions to access the cloud database.
 
@@
 
-VNF Controllers contains a SDN controller developed with ryu framework\cite{web:ryu} and a remote launcher module.
-The SDN controller does not have a remote launcher module to remotely execute a SDN controller.
-We built a light-weight server as a launcher module to resolve the remotely execution issue.
-The remote launcher module monitor the SDN controller process ID (PID) and properly kill the SDN controller process ID when on demand.
-When the infrastructure controller once create the container, the remote module will run up initially, waiting request from VNF Orchestrator.
-The details of SDN controller design will be presented at section \ref{sec:mft}.
+VNF controllers comprises an SDN controller developed using ryu framework\cite{web:ryu} and a remote launcher module.
+The SDN controller does not have a remote launcher module for remotely executing an SDN controller.
+We built a light-weight server as a launcher module to resolve this problem.
+The remote launcher module monitors the SDN controller process ID (PID) and kills the SDN controller PID on demand.
+Once the infrastructure controller once creates the container, the remote module will initially runs, waiting for requests from VNF Orchestrator.
+The details of an SDN controller design are presented at Section \ref{sec:mft}.
 
@@
 
-The VNF Orchestrator is a Web application server hosting on Amazon Web server, being online for customer and provide a dashboard for virtual CPE and containers management and configuration.
-Through the web UI provided by the VNF Orchestrator, the customers can subscribe to the desired service and without typing any command via the command line interface (CLI).
-After receiving the subscribing message, the VNF orchestrator will request the infrastructure orchestrator to create a new VNF controller, and then send the virtual CPE configuration to the new VNF controller.
-Based on configuration demands under different conditions, the network administrator is able to select any of the listed network functions on the dashboard such as Firewall, NAT, DHCP and QoS management.
+The VNF orchestrator is a web application server hosted on Amazon web server, and provides to customers an online dashboard for vCPE and containers management and configuration.
+Through the web-based UI provided by the VNF orchestrator, customers can subscribe to the desired service and without typing any command through the command line interface.
+After receiving the subscription message, the VNF orchestrator requests the infrastructure orchestrator to create a new VNF controller, and then sends the virtual CPE configuration to the new VNF controller.
+Based on configuration demands under different conditions, the network administrator can select any of the listed network functions on the dashboard, such as Firewall, NAT, DHCP, and quality of service (QoS) management.
 
 \subsection{Network Functions}
-The proposed vCPE service provides following network functions.
+The proposed vCPE service provides the following network functions.
 
 \subsubsection{Firewall}
-The firewall service could filter the packets based on packet header fields, including MAC address, IP, and layer4 protocols.
-The network manager can add new rules or remove rules to the access control list through our vCPE GUI.
+The firewall service can filter the packets based on packet header fields, including MAC address, IP, and layer4 protocols.
+The network manager can add new rules or remove rules from the access control list through our vCPE GUI.
 
 \subsubsection{NAT}
-The NAT service is a network function that can remap  IP address to another one.
-The Source NAT (SNAT) is typically used by internal users (inside private network) to access the Internet (outside network).
-The network function uses the action “Set-Field”, which deined by OpenFlow protocol for rewriting packet header fields.
-Via vCPE GUI interface, the network manager can set up the WAN port of SDN switch, public IP, default gateway, and local network address when using this function.
+The NAT service is a network function that can remap the IP address to another one.
+The source NAT (SNAT) is typically used by internal users (inside a private network) to access the Internet (outside the network).
+The network function uses the action set-field action, which is deined by OpenFlow protocol for rewriting packet header fields.
+Through the vCPE GUI interface, the network manager can set up the WAN port of the SDN switch, public IP, default gateway, and local network address when using this function.
 
 \subsubsection{DHCP}
-DHCP service allocates IP addresses to hosts dynamically.
-To implement the function, the SDN controller cope with UDP packets which use port 67 and 68.
-It generates DHCP offer and DHCP acknowledge to reply DHCP discovery and DHCP request received from the hosts.
+DHCP dynamically allocates IP addresses to hosts.
+To implement this function, the SDN controller copes with UDP packets that use port 67 and 68.
+The SDN controller generates DHCP offers and DHCP acknowledgements in reply to DHCP discoveries and DHCP requests received from the hosts.
 
 \subsubsection{Forwarding}
-Forwarding Service is a basic service that forward traffic to its destination and we use the Mac address learning concept to implement our forwarding function.
+The forwarding Service is a basic service that forwards traffic to its destination. We used the Mac address learning concept to implement the forwarding function.
 
 \subsubsection{QoS}
-Quality of Service (QoS) are always used to control the traffic flows of a network and prevent the traffic to exceed the network capacity and cause traffic congestion.
-Therefore we implement the bandwidth management using meter which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.
-Beside achieving network functions virtualization with SDN technology, we also make the network administrator manage and monitor a network more easily.
-As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
-In this paper, our QoS integrates with a flow classification engine and offers the two ways of bandwidth management.
+Quality of Service (QoS) is considered in controlling the traffic flows of a network and prevent the traffic from exceeding the network capacity and leading to congestion.
+Therefore, we implemented bandwidth management using meters which are defined within OpenFlow protocol 1.3, to set the limitation on the bandwidth.
+In addition to achieving network functions virtualization with SDN technology, we enabled network administrator to manage and monitor a network more easily.
+Consequently, we can offer the user the highest network quality under limitations on network resources without traffic congestion.
+In this study, we integrated QoS with a flow classification engine and offered two methods of bandwidth management.
 
 \begin{itemize}[\IEEEsetlabelwidth{Z}]
-\item For a specific host.
-\item For a specific application.
+\item Set the limitation on the bandwidth of a specific host.
+\item Set the limitation on the bandwidth of a specific application.
 \end{itemize}
@@
 \subsection{Application Identification}
-Application identification is to identify each flow as an application name to enable QoS management system
-to do bandwidth control or distribution at application level\cite{dynamic-qos-umeida}\cite{network-slicing-asia-pacific}.
-The application name means the name of application which establishes the flow.
-A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
-Applications include desktop applications, native mobile applications,
-and web applications, such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
-We use supervised machine learning and a method based on inspecting domain name service (DNS)
-responses to do flow classification.
-After application identification system classifies a flow as an application name,
-it sends the classification result to a server with database.
-The server stores the classification result into the database, and waits for requests from QoS management system.
-The detail will be described in section \ref{sec:app_identification}.
+Application identification entails identifying the application of each flow to enable QoS management system
+to execute bandwidth control or distribution at application level \cite{dynamic-qos-umeida}, \cite{network-slicing-asia-pacific}.
+The application name indicates the name of the application which establishes the flow.
+A flow is defined by a 5-tuple (source IP address, source port, destination IP address, destination port, and transport layer protocol).
+Applications include desktop applications, native mobile applications, and web-based applications, such as Facebook, Skype, YouTube, Instagram, Line, and WeChat.
+We used supervised machine learning (ML) and a method based on the inspect of domain name service (DNS) responses for flow classification.
+After the application identification system classifies a flow under an application name, it sends the classification result to a server connected to a database.
+The server stores the classification result in the database, and waits for requests from the QoS management system.
+This process is described in detail in Section \ref{sec:app_identification}.
 

### 2017-03-02 netsoft_paper.tex
fix some typo

@@
 This component is used to control the workflow, maintain the state associated with the VNF, and provide an interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
-We used an SDN controller to implement the NFV controller; and notably, we use southbound APIs of the SDN controller framework to manage the interface between the stateful and stateless component with OpenFlow protocol, which was originally designed for this purpose.
+We used an SDN controller to implement the VNF controller; and notably, we use southbound APIs of the SDN controller framework to manage the interface between the stateful and stateless components with the OpenFlow protocol, which was originally designed for this purpose.
 
@@
 By using the advantages of this architecture, we can assign stateless or light-weight state work to the SDN switch (e.g., packet filtering and packet counting) to reduce the load on the computing resources.
-If we want to update our service, we are required to update only the stateful component, because the stateless component merely follows the commands from stateful component.
+If we want to update our service, we are required to update only the stateful component, because the stateless component merely follows the commands from the stateful component.
 
@@
 Because computing infrastructures involves algorithms and policies and the generic network devices perform only stateless processing, the customers need to simply purchase a general SDN switch for their home gateway.
-They can obtain a different network function service by subscribing to a different the NFV controller through our vCPE platform.
+They can obtain a different network function service by subscribing to a different VNF controller through our vCPE platform.
 
@@
 Each green area is a local network domain of the customer.
-An SDN-enabled switch is presented at the gateway of this domain.
+An SDN switch is presented at the gateway of this domain.
 The customer can subscribe to our vCPE service through our dashboard.
-After subscription, the vCPE system creates a new Docker container in which an SDN controller is running.
-The customer only needs to set up the gateway SDN switch to connect the SDN controller through the OpenFlow protocol; thereafter, the switch will executes the service.
+After subscription, the vCPE system creates a new Docker container or new VM in which an SDN controller is run.
+The customer only needs to set up the gateway SDN switch to connect the SDN controller through the OpenFlow protocol; thereafter, the switch executes the service.
 
@@
 \ref{fig:desc_vcpe_framework}) is adapted from the NFV-MANO architectural framework in \cite{nfv2014-v111}, including an infrastructure controller, an infrastructure orchestrator, a cloud database, VNF controllers and a VNF Orchestrator.
-The infrastructure orchestrator, VNF orchestrator and cloud database are web servers.
 Each component is introduced in the following subsection.
@@
 
-The infrastructure controller comprises a Docker management server that can manage the Docker resources like containers.
-The infrastructure does not manage  customer authentication or maintaining the state of the running service; however, it follows the request from the infrastructure orchestrator to create, delete, start, stop, and inspect containers and VMs.
+The infrastructure controller comprises a Docker management server that can manage the Docker resources like containers and images and a OpenStack server that can manage the VM resources.
+The infrastructure controller does not manage customer authentication or maintaining the state of the running service; however, it follows the request from the infrastructure orchestrator to create, delete, start, stop, and inspect containers and VMs.
 
@@
 When a customer subscribes to our service, the infrastructure orchestrator first authenticates the customer, calls the infrastructure controller to create a container or a VM for the customer, and then updates the information in the database.
-The infrastructure orchestrator controls the entire lifecycle of our vCPE service.
+The infrastructure orchestrator controls the entire lifecycle of our vCPE services.
 
@@
 
-VNF controllers comprises an SDN controller developed using ryu framework\cite{web:ryu} and a remote launcher module.
+VNF controllers comprises an SDN controller developed using ryu framework \cite{web:ryu} and a remote launcher module.
 The SDN controller does not have a remote launcher module for remotely executing an SDN controller.
@@
 The remote launcher module monitors the SDN controller process ID (PID) and kills the SDN controller PID on demand.
-Once the infrastructure controller once creates the container, the remote module will initially runs, waiting for requests from VNF Orchestrator.
+Once the infrastructure controller  creates the container or the VM, the remote module will initially runs, waiting for requests from VNF Orchestrator.
 The details of an SDN controller design are presented at Section \ref{sec:mft}.
@@
 
-The VNF orchestrator is a web application server hosted on Amazon web server, and provides to customers an online dashboard for vCPE and containers management and configuration.
-Through the web-based UI provided by the VNF orchestrator, customers can subscribe to the desired service and without typing any command through the command line interface.
+The VNF orchestrator is a web application server hosted on Amazon web server, and provides to customers an online dashboard for vCPE services management and configuration.
+Through the web-based UI provided by the VNF orchestrator, customers can subscribe to the desired service without typing any command through the command line interface.
 After receiving the subscription message, the VNF orchestrator requests the infrastructure orchestrator to create a new VNF controller, and then sends the virtual CPE configuration to the new VNF controller.

### 2017-03-02 netsoft_paper.tex
fix mtt strategy

@@
 To implement this function, the SDN controller copes with UDP packets that use port 67 and 68.
-The SDN controller generates DHCP offers and DHCP acknowledgements in reply to DHCP discoveries and DHCP requests received from the hosts.
+The SDN controller generates DHCP Offer packets and DHCP Ack packets in reply to DHCP Discover packets and DHCP Request packets received from the hosts.
 
@@
 \subsubsection{QoS}
-Quality of Service (QoS) is considered in controlling the traffic flows of a network and prevent the traffic from exceeding the network capacity and leading to congestion.
+QoS is used to control the traffic flows of a network and prevent the traffic from exceeding the network capacity and leading to congestion.
 Therefore, we implemented bandwidth management using meters which are defined within OpenFlow protocol 1.3, to set the limitation on the bandwidth.
@@
 \subsection{Multiple Flow Tables Strategy}
-In subsection \ref{ssec:desc_nfv_overview}, the vCPE service design architecture have been introduced.
-The network functions are handled by the cooperation between SDN controller on cloud and SDN switch at the local network gateway.
-The controller transform the network functions to series of OpenFlow rules requests and send to SDN switch.
-Following the orders from controller, the SDN switch inserts rules to its flow tables, checks incoming packets against the flow entry match fields, and execute the actions in matching rules.
-The flow table\cite{sdn-ft} defines all matching and corresponding processing, thus playing an important role to executive network function.
+In subsection \ref{ssec:desc_nfv_overview}, we introduce the vCPE service design architecture.
+The network functions are managed through cooperation between the SDN controller on the cloud and SDN switch at the local network gateway.
+The controller transforms the network functions into a series of OpenFlow rule requests and sends it to the SDN switch.
+Following the orders from the controller, the SDN switch inserts the rules into its flow tables, examines the incoming packets against the flow entry match fields, and executes the actions in matching rules.
+The flow table \cite{sdn-ft} defines all matching and corresponding processing, thus playing an important role in the executive network function.
 
-Since the flow table is a crucial component, and we find that single flow table binds us to implement our network functions.
-The\cite{onf-multi-tables} also mentioned two condition for single flow table is too restrictive.
-The first is a single packet need to perform independent actions based on matching different fields.
-The second is that the packet needs two-stage processing.
-Involves into both situation, our network functions implemented by multiple flow tables strategy.
+We found that a single flow table restricts the implementation of our network functions.
+In \cite{onf-multi-tables} , two conditions under which a single flow table is too restrictive were reported.
+The first is a condition where a single packet must perform independent actions based on matching with different fields.
+The second is a condition where the packet requires two-stage processing.
+To satisfy both conditions, we implemented the network functions by using a multiple flow table strategy.
 
-In multiple flow tables strategy, the most important question is: which flow table should we insert rules into?
-We use the network function as a demarcation, that is, SDN applications which are responsible for specific network functions will only insert rules to one specific flow table, so we can focus on the design of the network function itself.
-In this way, however, the order of flow table become crucial.
-Should we put this network function at first, or the other?
-The answer is about the type of match and action in the rules generated by the network function
+In a multiple flow table strategy, it is most important to determine which flow table the rules should be inserted into.
+We used the network function as a demarcation, that is, SDN applications responsible for specific network functions inserted rules into one specific flow table to enable us to focus on the design of the network function itself.
+However, the order of the flow table and the sequence of the network functions become crucial.
+This can be addressed by considering the type of match and action in the rules generated by the network function.
 
-The network functions of vCPE services including Firewall, NAT, DHCP, Forwarding and QoS.
-We have determined the order of each function, shown in \ref{fig:mft_table_overview}.
-(Notice that the flow tables are counting from zero) In the following subsections, we will introduce how to implement these network functions, which type of rules will be inserted to SDN switch, and how these rules affect our decision of the order of flow tables.
+The network functions of vCPE services are the firewall service, NAT, DHCP, forwarding, and QoS.
+The order of each function was determined as shown in Fig.
+\ref{fig:mft_table_overview} (note that the flow tables are counted from zero).
+In the following sections, we introduce the method of implementing these network functions, the type of rules to be inserted into the SDN switch, and the effect of these rules on deciding the order of the flow tables
 

### 2017-03-03 netsoft_paper.tex
wallace edit

@@
-%% netsoft_paper.tex
+%% paper.tex
 %% V1.4b
-%% 2017/02/24
+%% 2017/03/05
 %% by HSNL, NTHU
-%% see http://www.michaelshell.org/
-%% for current contact information.
 
@@
 \usepackage{amsmath}
-\usepackage{fixltx2e}
-\usepackage{caption}
 \usepackage{enumerate}
@@
 
-% title
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Performance Optimization of Service Chain \\ for vCPE in Small Networks \\ with OpenFlow Switch}
+\title{Performance Optimization of Service Chain for vCPE in Small Networks with OpenFlow Switch}
 
@@
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
 \begin{abstract}
@@
 In this paper, a vCPE framework with multiple flow table management based on cloud is implemented.
-The proposed of vCPE framework is to create a SDN-enabled VNF using both resoures in SDN switch and on cloud and these VNFs can be deployed as edge.
+The proposed of vCPE framework is to create a SDN-enabled VNF using both resources in SDN switch and on cloud and these VNFs can be deployed as edge.
 The system is also integrated with an application identification engine based on machine learning algorithms thus providing flow control in vCPE framework with confidence.
@@
 \begin{IEEEkeywords}
-Software defined network, virtual customer premise equipment, network function virtualization, OpenFlow
+Software defined network, network function virtualization, NFV orchestration, virtual customer premise equipment, OpenFlow, multiple flow tables
 \end{IEEEkeywords}
@@
 \section{Introduction}
-\IEEEPARstart{S} oftware Define Network \cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}.
-Openflow\cite{sp:openflow13} gives a brand new viewpoint on network research, and makes innovation on industries.
-This technic proposed not just a novel architecture but also bring out more methods of flexible traffic engineering.
+\IEEEPARstart{S}{oftware} Define Network (SDN) \cite{sdn-new-norm}, \cite{sdn-comprehensive} has been developing almost a decade since the first OpenFlow article had be presented in 2008\cite{openflow-campus-network}.
+OpenFlow\cite{sp:openflow13} gives a brand new viewpoint on network research, and makes innovation on industries.
+This technology proposed not just a novel architecture but also bring out more methods of flexible traffic engineering.
 After tons of implementations and researches had been proposed, this architecture exposed some weakness in performance.
@@
 It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
-At the same time as SDN was developed, Network Function Virtualization (NFV) \cite{nfvwp}\cite{nfv-survey}\cite{laptop-sdn} has been introduced by Telco operators.
+At the same time as SDN was developed, Network Function Virtualization (NFV) \cite{nfvwp,nfv-survey,laptop-sdn} has been introduced by telco operators.
 Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years.
 To replace the old platform with high maintenance cost, they use virtual machine (VM) based on new computers as solutions.
-This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC\cite{nec-vcpe}.
+This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is Virtual Customer Premise Equipment (vCPE) which was innovated by NEC\cite{nec-vcpe}.
 vCPE manage network functions on operation side to reduce cost which was deployed on cloud \cite{cloud4nfv}.
@@
 The first one is the lack of hardware support because these ideas need large size of flow tables to achieve multi VNF support.
-And the other is VM based on cloud may slow down the high speed network exchanging network\cite{nfv-placemet},\cite{nfv-placement-model}.
+And the other is VM based on cloud may slow down the high speed network exchanging network\cite{nfv-placemet, nfv-placement-model}.
 From Pica8\cite{pica8-switch} finished their first OpenFlow switches, there are so many implementation method on a SDN switch.
@@
 The other is it may can’t figure out encryption connections because not all of IDS or IPS have key matching feature.
-Most of modern cloud applications use https protocol as basic communication method which makes matter even worse.
+Most of modern cloud applications use HTTPS protocol as basic communication method which makes matter even worse.
 This study gives an algorithm to identify applications with statistical method with machine learning.
@@
 Our network functions (Fig.
-\ref{fig:desc_nfv_overview}) are designed with SDN-enabled NFV architecture concept \cite{sdn-enabled}, using the synergies between computer infrastructures (NFVs) and network infrastructures (NFVIs) \cite{nfv2014-v121},\cite{nfv2015}.
+\ref{fig:desc_nfv_overview}) are designed with SDN-enabled NFV architecture concept \cite{sdn-enabled}, using the synergies between computer infrastructures (NFVs) and network infrastructures (NFVIs) \cite{nfv2014-v121, nfv2015}.
 An NFV is a VNF controller, mainly used for addressing stateful processing and NFVI is an SDN switch used for stateless processing.
@@
 \subsection{Service Deployment Model}
-Unlike a related study that explored the virtualization of network function in PE devices \cite{vcpe-enhance}, we introduced a network function service deployment model based on the NetFATE (Network Function at the Edge) approach \cite{netfate}; the archtecture of the model is presented in Fig.
+Unlike a related study that explored the virtualization of network function in PE devices \cite{vcpe-enhance}, we introduced a network function service deployment model based on the NetFATE (Network Function at the Edge) approach \cite{netfate}; the architecture of the model is presented in Fig.
 \ref{fig:desc_nfv_overview}.
@@
 \subsubsection{Infrastructure Orchestrator}
-
 The infrastructure orchestrator plays a key role in our system.
@@
 When a customer subscribes to our service, the infrastructure orchestrator first authenticates the customer, calls the infrastructure controller to create a container or a VM for the customer, and then updates the information in the database.
-The infrastructure orchestrator controls the entire lifecycle of our vCPE services.
+The infrastructure orchestrator controls the entire life-cycle of our vCPE services.
 
 \subsubsection{Cloud Database}
-
-The cloud database is used for restoring the metadata of our vCPE services, which include each customer’s credentials, customer’s container/VM settings, and virtual CPE service states.
+The cloud database is used for restoring the meta data of our vCPE services, which include each customer’s credentials, customer’s container/VM settings, and virtual CPE service states.
 The cloud database employs PostgreSQL, which is an open source, easily customizable and object-relational database system.
@@
 \subsubsection{VNF Controllers}
-
-VNF controllers comprises an SDN controller developed using ryu framework \cite{web:ryu} and a remote launcher module.
+VNF controllers comprises an SDN controller developed using Ryu framework \cite{web:ryu} and a remote launcher module.
 The SDN controller does not have a remote launcher module for remotely executing an SDN controller.
@@
 \subsubsection{VNF Orchestrator}
-
 The VNF orchestrator is a web application server hosted on Amazon web server, and provides to customers an online dashboard for vCPE services management and configuration.
@@
 The source NAT (SNAT) is typically used by internal users (inside a private network) to access the Internet (outside the network).
-The network function uses the action set-field action, which is deined by OpenFlow protocol for rewriting packet header fields.
+The network function uses the action set-field action, which is defined by OpenFlow protocol for rewriting packet header fields.
 Through the vCPE GUI interface, the network manager can set up the WAN port of the SDN switch, public IP, default gateway, and local network address when using this function.
@@
 Consequently, we can offer the user the highest network quality under limitations on network resources without traffic congestion.
-In this study, we integrated QoS with a flow classification engine and offered two methods of bandwidth management.
+In this study, we integrated QoS with a flow classification engine and offered two methods of bandwidth management:
 
 \begin{itemize}[\IEEEsetlabelwidth{Z}]
-\item Set the limitation on the bandwidth of a specific host.
-\item Set the limitation on the bandwidth of a specific application.
+\item set the limitation on the bandwidth of a specific host;
+\item set the limitation on the bandwidth of a specific application.
 \end{itemize}
@@
 \includegraphics[width=6in]{./figures/mft_table_overview}
-\caption{The flow table order of vCPE service.}
+\caption{Flow table order of vCPE service.}
 \label{fig:mft_table_overview}
@@
 We found that a single flow table restricts the implementation of our network functions.
-In \cite{onf-multi-tables} , two conditions under which a single flow table is too restrictive were reported.
+In \cite{onf-multi-tables}, two conditions under which a single flow table is too restrictive were reported.
 The first is a condition where a single packet must perform independent actions based on matching with different fields.
@@
 To satisfy both conditions, we implemented the network functions by using a multiple flow table strategy.
+
+Before we discuss about the multiple flow table strategy, we introduce the pipeline of OpenFlow flow table first \cite{sp:openflow13}.
+The processing of each packet always starts at the first flow table.
+When processed by a flow table, the packet is matched the flow entries of the flow table and adds corresponding action to the instruction set.
+The packet can executes the instrcution set immediately, or execute after finishing the journey in switch.
+A flow entry can direct a packet to next table by go-to action.
+In our multiple flow table management model, we will set the go-to-next-table action as the table-miss action.
+Therefore, the packet is processed table-by-table in a certain sequence.
 
@@
 \ref{fig:mft_table_overview} (note that the flow tables are counted from zero).
-In the following sections, we introduce the method of implementing these network functions, the type of rules to be inserted into the SDN switch, and the effect of these rules on deciding the order of the flow tables
+Each packet In the following sections, we introduce the method of implementing these network functions, the type of rules to be inserted into the SDN switch, and the effect of these rules on deciding the order of the flow tables
 
 \subsection{Service Control}
-Service control is about which service we want to enable or disable.
-To enable a service, we need to modify the table-miss rule.
-We always put a packet-in rule in the flow table of the last active service as a table-miss in case that there isn't any corresponding rule.
-To make our service chain possible, the rules of each service except the last service contains an additional action, go to next flow table, so the packets can continue to pass through all active services.
+Service control is used to enable or disable services.
+To enable a service, the table-miss rule should be modified.
+A packet-in rule is always placed in the flow table of the last active service as a table miss in case there is no corresponding rule.
+To enable the service chain, the rules of each service except the last service contain an additional action, “go to next flow table,” which enables the packets to continue to pass through all active services.
 
-To disable a service, we not only need to modify the table-miss rule but also have to add an enforce rule.
-Each enforce rules has maximum priority and the action is goto next flow table.
-It means that packets will still pass through the disabled service's table, and the only thing they do in this flow table is ignoring other rules and go to next flow table.
+To disable a service, we must not only modify the table-miss rule but also add an enforce rule.
+Each enforce rule has maximum priority with the action “go to next flow table.” It indicates that packets still pass through the disabled service’s table, but ignore other rules and proceed to the next flow table.
 
 \subsection{Firewall}
-Firewall service is able to block traffic dynamically, and in this service, the packets will not cause any packet-in event.
+The firewall service can dynamically block traffic and prevent the packets from causing a packet-in event.
 
@@
 \begin{itemize}[\IEEEsetlabelwidth{Z}]
-\item Block any traffic from a source IP or destination IP.
-\item Block traffic based on known layer 4 protocols, such as SSH, HTTP, etc.
-\item Block traffic to customize layer 4 ports of a host.
+\item block any traffic from a source IP or destination IP address;
+\item block traffic based on known layer 4 protocols, such as SSH and HTTP;
+\item block traffic to customize layer 4 ports of a host.
 \end{itemize}
@@
 For different policies, the controller applies corresponding rules to the SDN switch.
-After the policies are set, the blocking rules will be installed immediately.
-Then any traffic that hit the blocking rules will be dropped.
-For normal traffic, they will not be affected.
+After the policies are set, the blocking rules are immediately installed.
+Subsequently, any traffic that satisfies the blocking criteria is dropped.
+Normal traffic is unaffected.
 
-As shown in Table \ref{table:fw}, all the actions of flow entries are drop.
-The first rule illustrates that SSH connection with source IP address 192.168.2.1 would be blocked.
-The second rule shows the flow entry would block the Telnet protocol.
+As shown in Table \ref{table:fw}, all the actions of flow entries are dropped.
+The first rule illustrates that SSH connection with the source IP address 192.168.2.1 is blocked.
+The second rule indicates that the flow entry blocks the Telnet protocol.
 
-In our multiple flow tables model, the firewall service is located in the flow table 1, since once packets are caught by the blocking rules, they doesn't need to apply any other services.
-The packets which match the rules will be dropped immediately, and their journey in the flow table ends here.
-To other no-blocked packets, they pass all blocking rules and finally match the table-miss rule, which will let the packets go on the next flow table.
-The action of firewall is different from other services, since in other services, no matter what actions are taken to the packets, the packets have to go to the next flow table.
+In our multiple flow table model, the firewall service is located in flow table 1 because once packets are detected by the blocking rules, they do not need to be applied to any other services.
+The packets that satisfy the blocking rules are immediately dropped, and their journey in the flow table ends.
+The other unblocked packets pass all blocking rules and finally satisfy the table-miss rule, which allows the packets to proceed to the next flow table.
+The action of the firewall is different from those of other services, because in other services, irrespective of the actions taken with the packets, the packets must proceed to the next flow table.
 
@@
 \hline
-IP proto & IP Src      & IP Dst       & L4 sport & L4 dport & Action \\ \hline
-TCP      & 192.168.2.1 & *            & *        & 22       & Drop   \\ \hline
-TCP      & *           & *            & *        & 23       & Drop   \\ \hline
+IP proto & IP src      & IP dst       & L4 sport & L4 dport & action \\ \hline
+TCP      & 192.168.2.1 & *            & *        & 22       & drop   \\ \hline
+TCP      & *           & *            & *        & 23       & drop   \\ \hline
 \end{tabular}
   \begin{tablenotes}
-    \item[] Symbol * represents wildcard (match any value).
+    \item[] Symbol * represents wildcard (matches any value).
   \end{tablenotes}
@@
 \subsection{NAT}
-The NAT service could allow a lot of hosts to use one public IP address to connect the network.
-In order to achieve this thing, SDN controller have to set the packet header filed.
-Because the SDN switch would set the field, the first packet have to go to controller.
-And controller would add the flow to SDN switch, after that the packet would not go to controller.
-It can decrease the burdens of the controller.
+The NAT service allows numerous hosts to use one public IP address for connecting to the network.
+To achieve this, the SDN controller must set the packet header field.
+Because the SDN switch sets the field, the first packet must proceed to the controller.
+When the controller adds the flow to the SDN switch, the packet does not proceed to the controller.
+This can reduce the burden on the controller.
 
-Below is a examples to show how the NAT service modify the IP address and port number.
-For outgoing packet, the SDN switch doesn’t have any flow entry in flow table, so the Packet-in event will be triggered at the beginning.
-The packet that is sent by private network host will be sent to SDN controller, and the packet header fields are modified by Set-Field action.
-The source IP address and source port number of outgoing packet will be modified to public IP address and remaped a new port number for NAT.
-For ingoing packet, the destination IP and destination port number are modified to fit private IP and port number.
-And then SDN controller add these flow entries to SDN switch, it can’t avoid that all the packet sent to controller.
+Following is an example that illustrates the modification of the IP address and port number by using the NAT service.
+For an outgoing packet, the SDN switch does not have any flow entry in the flow table, and hence, a packet-in event is triggered initially.
+The packet that is sent by a private network host is sent to the SDN controller, and the packet header fields are modified using the set-field action.
+The source IP address and source port number of the outgoing packet are modified to a public IP address and a new port number is remapped for NAT.
+For the incoming packet, the destination IP address and destination port number are modified to fit the private IP address and port number.
+Subsequently, the SDN controller adds these flow entries to the SDN switch; all packets must be sent to the controller
 
-Fig.
-\ref{fig:mft_nat} show the public IP address of NAT is 140.114.71.178 and a host private IP is 192.168.8.254 and port number 7878.
-The client sent the packet to a server with IP address 140.114.71.177 and port number 9898.
+In Fig.
+\ref{fig:mft_nat}, the public IP address of NAT is 140.114.71.178, and the host private IP address is 192.168.8.254 with the port number 7878.
+The client sent the packet to a server with the IP address 140.114.71.177 and port number 9898.
 
-As shown in Table \ref{table:nat}, when host sent the packet to server (outgoing), the Packet-in will be trigger, and then packet to controller.
-The Set-Field action would modify the Source IP to public IP address of NAT is 140.114.71.178 and source port to 2000.
-when the server sends back to the client (ingoing), the packet header field would be modified.
-The destination IP address and destination port number would be modified to 192.168.8.254 and 7788.
+As shown in Table \ref{table:nat}, when the host sends the packet to the server (outgoing), a packet-in event is triggered, and the packet is sent to the controller.
+The set-field action modifies the source IP address to a public IP address of NAT, 140.114.71.178, and the source port to 2000.
+When the server sends the packet back to the client (incoming), the packet header field is modified.
+The destination IP address and destination port number are modified to 192.168.8.254 and 7788, respectively.
 
-In the single flow table framework, we have to add the two rules to SDN switch to match the outgoing and ingoing situation.
-At the first, we predict the NAT service to be put one the last table in the multiple flow tables framework.
-Because the NAT service need to set the packet header fields and play a role of connection to the outside network.
-And the most important thing is that the SDN switch is according to order of table to match.
-We have to consider the outgoing and ingoing situations.
-As a result of all the above factors combined, the NAT service is located at the first and the last table in our multiple flow table framework.
+In the single flow table framework, two rules must be added to the SDN switch to match the outgoing and incoming situations.
+First, we predicted that the NAT service must be placed in the last table of the multiple flow table framework because the NAT service must set the packet header fields and enable connection to the outside network.
+Most importantly, the SDN switch is placed according to the order of tables to match the field.
+The outgoing and incoming situations must be considered.
+In consideration of all the aforementioned factors, we place the NAT service in the first and last tables in our multiple flow table framework.
 
@@
 \includegraphics[width=3in]{./figures/mft_nat}
-\caption{The flow table order of vCPE service.}
+\caption{Example of modification of IP address and port number by NAT service.}
 \label{fig:mft_nat}
@@
 \begin{table*}[!t]
-\caption{Flow entry for modifying the packet header fields of packets}
+\caption{Flow entry for modifying the packet header fields}
 \label{table:nat}
@@
 \hline
-            &IP Src          & IP Dst          & L4 src port  & L4 dst port & Action                                                                            \\ \hline
-1. outgoing &192.168.8.254   &140.114.71.177   & 7878         & 9898        & \begin{tabular}[c]{@{}l@{}}IP Src $\,\to\,$ 140.114.71.178; \\ L4 src port $\,\to\,$ 2000\end{tabular} \\ \hline
-2. ingoing  &140.114.71.177  &140.114.71.178   & 9898         & 2000        & \begin{tabular}[c]{@{}l@{}}IP Dst $\,\to\,$ 192.168.8.254; \\ L4 dst port $\,\to\,$ 7878\end{tabular} \\ \hline
+            &IP src          & IP dst          & L4 src port  & L4 dst port & action                                                                            \\ \hline
+1. outgoing &192.168.8.254   &140.114.71.177   & 7878         & 9898        & \begin{tabular}[c]{@{}l@{}}IP src $\,\to\,$ 140.114.71.178; \\ L4 src port $\,\to\,$ 2000\end{tabular} \\ \hline
+2. ingoing  &140.114.71.177  &140.114.71.178   & 9898         & 2000        & \begin{tabular}[c]{@{}l@{}}IP dst $\,\to\,$ 192.168.8.254; \\ L4 dst port $\,\to\,$ 7878\end{tabular} \\ \hline
 \end{tabular}
@@
 \subsection{DHCP}
-DHCP service implements DHCP protocol to dynamically assign IP addresses to hosts.
-DHCP operation uses UDP protocol. The clients use port 68 as the source port and 67 as the destination port.
-On the contrary, the server use port 67 as the source port and 68 as the destination port.
-Our system is able to handle these packets  to realize DHCP service.
+The DHCP service implements the DHCP protocol to dynamically assign IP addresses to hosts.
+A DHCP operation uses the UDP protocol.
+Clients use port 68 as the source port and port 67 as the destination port.
+By contrast, the server uses port 67 as the source port and port 68 as the destination port.
+Our system can handle packets to realize the DHCP service.
 
-The service follows these steps:
+This service is executed through the following steps:
 \begin{enumerate}
 \item The controller adds a DHCP rule for DHCP packets when the service is enabled.
-\item All packets match this DHCP rule cause packet-in.
-\item The controller checks if a packet is a DHCP discovery packet.
-If so, the controller assigns an IP address, and generate a DHCP offer then do packet-out.
-If not, the controller then checks whether it's a DHCP request.
-If the result is positive, the controller generate a DHCP acknowledge then do packet-out.
+\item All packets match this DHCP rule, causing a packet-in event.
+\item The controller determines whether a packet is a DHCP discovery packet.
+If so, the controller assigns an IP address, generates a DHCP offer, and then performs a packet-out event.
+If not, the controller determines whether it is a DHCP request.
+If the result is positive, the controller generates a DHCP acknowledgement and then performs a packet-out event.
 \end{enumerate}
 
-Our system support multiple flow table, but a specific flow table for DHCP service is not required.
-The reason is that only one rule will be installed for all hosts who request for DHCP service.
-When the service is disabled, the DHCP rule will be deleted,
-and the packets will continue to pass through our service chain.
-Following DHCP packets can reach other DHCP servers without entering our service chain
-since our controller will automatically flood out broadcast packets.
+Our system supports multiple flow tables; however, a specific flow table for the DHCP service is not required because only one rule is installed for all hosts who request the DHCP service.
+When the service is disabled, the DHCP rule is deleted, and the packets continue to pass through our service chain.
+The subsequent DHCP packets can reach other DHCP servers by forwarding service.
 
 \subsection{Forwarding} \label{ssec:forwarding}
-In this service, when the first packet in a new connection incoming, it will cause a packet-in event because there is no corresponding rule.
-When controller receives the packet, it will record IP-layer information, including source IP, destination IP, input port number, source mac address and destination mac address.
-With the recorded information, the controller is able to install a 5-tuple forwarding rule for this connection and following packets don’t need to packet-in again.
-The 5-tuple is source IP, destination IP, network layer protocol, source layer 4 port, and destination layer 4 port.
+In the forwarding service, when the first packet in a new connection is incoming, a packet-in event occurs because no corresponding rule is present.
+When the controller receives the packet, it records the IP-layer information, including the source IP address, destination IP address, input port number, source MAC address, and destination MAC address.
+By using the recorded information, the controller can install a 5-tuple forwarding rule with out-port action for this connection, and the subsequent packets do not need to undergo the packet-in event.
+The 5-tuple comprises the source IP address, destination IP address, network layer protocol, source layer 4 port, and destination layer 4 port.
 
-In order to gather per-session statistics information, 5-tuple rules are needed.
-This is why we don’t add rules  based on mac address.
-The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second.
-In this way, we can get the real-time bandwidth statistics of each connection by just subtracting the byte count from byte count of last second.
+To gather per-session statistical information, 5-tuple rules are required.
+Therefore, rules based on the MAC address are not added.
+The controller installs a pair of dummy rules for every connection, and then requests the switch to obtain current flow statistics every second.
+Thus, the real-time bandwidth statistics of each connection can be obtained by merely subtracting the byte count from the byte count of the last second.
 
 \subsection{QoS}
-QoS service is mainly for traffic control and we provide two management funtion for QoS service.
-We will introduce these two strategy first and then discuss the flow table order of QoS service in multiple table model.
+QoS is mainly used for traffic control. Two management functions are provided for QoS. We first introduce three strategies and then discuss the flow table order of QoS in the multiple table model.
 
 \subsubsection{Rate Limitation of Hosts}
-When some hosts take up a lot of bandwidth of network, it will make other hosts in slow speed or make traffic congestion.
-To prevent this, rate limiting is used to control the rate of traffic from a host.
-For implementing the host rate limitation, we create a meter for desired bandwidth first and then add a flow, of which match is host’s mac address and action is the meter we just created.
+When some hosts utilize a high network bandwidth, the speed for other hosts slows or traffic congestion occurs.
+To prevent these effects, rate limiting is used to control the rate of traffic from a host.
+For implementing the host rate limitation, we first create a meter for the desired bandwidth and then add a flow, of which the match is the host’s MAC address and the action is the meter.
 
-The concept of this option is shown in Fig.
-\ref{fig:mft_qos_rate_host}.
+This method is illustrated in \ref{fig:mft_qos_rate_host}.
 In T0, host 1 and host 2 are not limited yet.
-Since host 2 takes up a lot of bandwidth from network in T0 to T1, the network administrator sets host 2 rate-limited under 400 Kbps.
-When controller receive this request, marked as (a), it will create a new meter with meter id = 1 and bandwidth = 400 Kbps, and set the rule in the flow table with destination MAC address = MAC address of host 1 and meter = 1.
-According to our flow table, it will limit the rate of the target host.
-Then the traffic from host 2 will reduce and be limited with 400Kbps immediately.
-The similar situation also occurs to host 1 in T2.
-The administrator chooses to set host 1 under 600 Kbps, marked as (b), and then traffic from host 1 will be limited with 600Kbps.
+Because host 2 utilizes a substantial amount of bandwidth from the network in T0–T1  the network administrator sets the host 2 rate limit to 400 Kbps.
+When the controller receives this request, marked as (a), it creates a meter with meter id = 1 and bandwidth = 400 Kbps and sets the rule in the flow table with the destination MAC address = MAC address of Host 1 and meter = 1.
+According to our new flow table, it limits the rate of the target host.
+Then, the traffic from Host 2 is reduced and immediately limited to 400 Kbps.
+A similar situation occurs for Host 1 in T2.
+The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then the traffic from Host 1 is limited to 600 Kbps.
 
@@
 \includegraphics[width=3in]{./figures/mft_qos_rate_host}
-\caption{Illustration of rate-limiting for a certain host}
+\caption{Illustration of rate limiting for a certain host}
 \label{fig:mft_qos_rate_host}
@@
 \subsubsection{Rate Limitation of Applications}
-There are more and more network’s applications used such as online games, video streaming, conference call, etc.
-Therefore, there are massive traffic working in the network.
-Consequently, we integrate with a flow classification engine to identify the flow belongs which application is.
-The integration scenario will be shown as Fig.
+
+An increasing number of network applications such as online games, video streaming, and conference calls are used.
+Therefore, substantial traffic exists in the network.
+Consequently, we integrated a flow classification engine to identify which application the flow belongs to.
+The integration scenario is presented in Fig.
 \ref{fig:class_classifying}.
 
-In order to rate limit for a certain application, we need to gathering per-flow statistics information first. When
-a connection is created, the first packet of this connection will be handled by the forwarding service and add 5-tuple rules into SDN switch, so we can get the bandwidth information of per-flow connection.
-(See subsection \ref{ssec:forwarding} for details).
-With the classified result of application identification, we can know the application type of each connection.
+To rate the limit for a certain application, we must first gather per-flow statistical information.
+When a connection is created, the first packet of the connection is handled by the forwarding service and the 5-tuple rules are added into the SDN switch to obtain the bandwidth information of the per-flow connection (see Section \ref{ssec:forwarding} for details).
+With the classified result of application identification, the application type of each connection can be determined.
 
-When network administrator request to rate limit a certain application to a certain bandwidth, we will equally distribute the bandwidth to each connection of the application.
-The controller set all flows belong to the same application into the same meter, and modifying the bandwidth of meter to achive our goal.
-For instance, if there is an application and we can find out which flows belong to this application through the flow classification engine and we want to limit this application to 1000Kbps.
-As Figure.
-\ref{fig:mft_qos_rate_app}, in T0, we know there are 3 connections belong this application and we will set the bandwidth of meter to each link with 1000/3 = 333Kbps.
-In T2, there are more two connections added to this application and we will reset the bandwidth of meter to each links with 1000/5 = 200Kbps.
-In T2, there is a connection ended by this application, we will reset the bandwidth of meter to each links with 1000/4 = 250Kbps, therefore.
-Whereas, the sum of bandwidth from this application is always being 1000 Kbps.
-That is, the bandwidth will be dynamically adjusted according the numbers of connections.
+When the network administrator requests to rate limit a certain application to a certain bandwidth, the bandwidth is equally distributed to each connection of the application.
+The controller sets all flows that belong to the same application into the same meter, and the bandwidth of the meter is modified to achieve the desired value.
+For example, suppose that we can determine which flows belong to an application through the flow classification engine.
+This application is to be limited to 1000 Kbps.
+In T0 (Fig.
+\ref{fig:mft_qos_rate_app}), three connections belong to this application, and the bandwidth of the meter to each link is set as 333 (1000/3) Kbps.
+In T2, two connections are added to this application, and the bandwidth of the meter to each link is reset as 200 (1000/5) Kbps.
+In T2, one connection is obtained in this application, and hence, the bandwidth of the meter to each link is reset as 250 (1000/4) Kbps.
+However, the sum of bandwidth from this application should always be 1000 Kbps.
+In other words, the bandwidth is dynamically adjusted.
 
-It is worth mentioning that we would not change any rules in flow table and we only change the bandwidth of the correspond meter in the meter table.
-Therefore, there only have a little overhead to switch and controller.
+It is worth noting that we did not change any rules in flow table; we merely change the bandwidth of the correspond meter in the meter table to reduce the overhead of switch and controller.
+
 \begin{figure}[!t]
@@
 \includegraphics[width=3in]{./figures/mft_qos_rate_app}
-\caption{Illustration of rate-limiting for a certain application.}
+\caption{Illustration of rate limiting for a certain application.}
 \label{fig:mft_qos_rate_app}
@@
 \subsubsection{The Flow Table Order of Forwarding and QoS Service}
-Since the location of NAT, DHCP and firewall are determined. Here we only need to decide the arrangement of QoS and forwarding.
-Let's consider the scenario that we put the QoS flow table after the forwarding flow table.
-Plus, we have only two services enabled, forwarding and QoS, then suppose a host is not limited by QoS policies.
-The very first packet will not be affected in both arrangement.
-For the following packets, the difference can be observed.
-The packets which has matched the rules of the forwarding flow table will still cause packet-ins when they go to QoS flow table.
-This is not supposed to happen, since the host is not restrained by QoS policies and any packet-in increase the controller's load.
-To reduce the burden of the controller, we put QoS flow table ahead of forwarding flow table.
-In this scenario, all packets that pass through QoS flow table will continue to go to forwarding flow table without matching any QoS rules.
-Then the packets except the very first packet will just be forwarded by forwarding service instead of causing packet-ins.
-Hence the controller's load will decrease.
-To use our system, the forwarding service is necessary, so there is no such scenario that users enable QoS and disable forwarding.
+Because the location of NAT, DHCP, and the firewall have been determined, we only need to decide the arrangement of QoS and forwarding.
+Assume that we place the QoS flow table after the forwarding flow table.
+In addition, we have only two services enabled, forwarding and QoS; therefore, the packet-in rule is in the last flow table of active service, Qos service.
+Then, suppose that a host is not limited by QoS policies.
+The first packet is not affected in both arrangements.
+For the subsequent packets, a difference can be observed.
+The packets that satisfy the rules in the forwarding flow table can not match rate limit rules in QoS flow table, because the host is not limited by QoS service; instead.
+As a result, the packets cause packet-in events by matching the packet-in rule in QoS service.
+This is unexpected because the packets already get the out-port action from the forwarding service.
+That is, it is not necessary to send these packet go to controller, and any packet-in event increases the controller’s load.
+
+To reduce this load on the controller, we place the QoS flow table ahead of the forwarding flow table.
+In this scenario, all packets that pass through the QoS flow table continue to proceed to the forwarding flow table without satisfying any QoS rules.
+Then, all packets except the first packet are merely forwarded by the forwarding service instead of causing packet-in events.
+Thus, the controller’s load decreases.
 
 \section{Application Identification Method}\label{sec:app_identification}
-In order to let QoS management system be able to control or distribute bandwidth at application level,
-we designed and implemented an application identification system (also called flow classification system)
-to judge each flow is established by what application.
-In other words, the application identification system can classify each flow as an application name in real time,
-rather than a rough category or a transport layer protocol.
-The corresponding application name of a flow means the name of the application which establishes the flow.
-We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification.
-The system analyzes the packets whose transport protocol are TCP or UDP.
-Except for DNS responses, the system only reads headers to get transport layer information of
-packets without inspecting their payload.
+To enable the QoS management system to control or distribute bandwidth at the application level, we designed and implemented an application identification system (also called flow classification system) to identify the application that establishes each flow.
+In other words, the application identification system can classify each flow under an application name in real time, rather than a rough category or a transport layer protocol.
+The corresponding application name of a flow indicates the name of the application that establishes the flow.
+We use supervised ML and a method based on the inspection of DNS responses for flow classification.
+The system analyzes the packets with the transport protocols TCP or UDP.
+Except for DNS responses, the system reads only headers to obtain the transport layer information of packets without inspecting their payload
 
 \subsection{Architecture of Application Identification System}
-There are training phase (also called preparation phase) and classifying phase,
-their architectures are shown in Fig. \ref{fig:class_training} and Fig. \ref{fig:class_classifying} respectively.
-These architectures can be integrated, and do training and classifying in the same time.
+The application identification system comprises a training phase (also called the preparation phase) and a classification phase; their architectures are presented in Figs.
+\ref{fig:class_training} and \ref{fig:class_classifying}, respectively.
+These architectures can be integrated to perform training and classification simultaneously.
 
@@
 \includegraphics[width=3in]{./figures/classification_classifying}
-\caption{Architecture of our application identification system in classifying phase.}
+\caption{Architecture of our application identification system in classification phase.}
 \label{fig:class_classifying}
@@
 \subsection{Overall Procedure of Application Identification}
-In training phase, we generate some data needed by our proposed method.
-In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify;
-otherwise, we use supervised ML to classify.
+In the training phase, we generate data required for the proposed method.
+In the classification phase, if a flow meets some requirement, we use the method based on the inspection of DNS responses for classification; otherwise, we use supervised ML.
 
 \subsection{Procedure of Supervised ML}
-In training phase, the architecture is show in Fig. \ref{fig:class_training}.
-Flow classification engine is to build classification model by training data from Trainer,
-and update the model when new training data comes.
-Trainer is to analyze traffic from mirror port to get flow attributes.
-After Trainer finishes calculating flow attributes of a flow,
-it gets ground truth of the flow from Scanner or App Meta Server to generate training data,
-and sends training data to flow classification engine.
-App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
-Scanner is to get mappings of 5-tuple and ground truth from OS.
-In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}.
-Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result,
-and sends classification result to Classifier.
-Classifier is to analyze traffic from mirror port to get flow attributes.
-After Classifier finishes calculating flow attributes of a flow,
-it use flow attributes to ask flow classification engine for classification result if needed.
+The architecture in the training phase is presented in Fig.
+\ref{fig:class_training}.
+The flow classification engine is used for building a classification model by using training data from the trainer.
+The model is updated when new training data are received.
+The trainer is used for analyzing traffic from the mirror port to obtain flow attributes.
+After the trainer calculates the attributes of a flow, it obtains the ground truth of the flow from the scanner or app meta server to generate training data and sends the training data to the flow classification engine.
+The app meta server is used to store mappings of the 5-tuple and ground truth from the scanner and accept queries from the trainer.
+The scanner is used to obtain mappings of the 5-tuple and ground truth from the OS.
+The architecture in the classification phase is presented in Fig.
+\ref{fig:class_classifying}.
+In this architecture, the flow classification engine uses flow attributes from the classifier and classification model to obtain a classification result and sends the classification result to the classifier.
+The classifier analyzes the traffic from the mirror port to obtain flow attributes.
+After the classifier calculates the attributes of a flow, it uses them to order the classification result from the flow classification engine if required.
 
-\subsection{Flow ttributes of Supervised ML}
-In ML, when system calculates flow attributes, we only use transport layer information of packets which have payload.
-We use Application Round (APPR) proposed by\cite{classfication-cloud} to analyze flow behavior.
-We use number of packets, packet sizes, transmission time,
-transmission direction, throughput, and APPR to define flow attributes.
-There are 69 attributes in total, as defined in our previous work\cite{Chia-Chin-master}.
+\subsection{Flow Attributes Adopted in Supervised ML}
+In ML, when the system calculates flow attributes, we use only the transport layer information of packets with a payload.
+Moreover, we use the application round (APPR) proposed in \cite{classfication-cloud} to analyze the flow behavior.
+We use the number of packets, packet size, transmission time, transmission direction, throughput, and APPR to define flow attributes.
+A total of 69 attributes are defined, as reported in our previous study \cite{Chia-Chin-master}.
 
-\subsection{Algorithms of Supervised ML}
-We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato.
-We call Weka Java API to build classification model.
-We use three algorithms, namely RandomSupSpace with RandomTree\cite{TinKamHo1998},
-FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
+\subsection{Algorithms Adopted in Supervised ML}
+We used algorithms implemented by Weka, an open-source ML tool developed at the University of Waikato.
+We called the Weka Java API to build the classification model.
+In addition, we used three algorithms, RandomSupSpace with RandomTree \cite{TinKamHo1998}, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
 
-\subsection{Procedure of a Method Based on Inspecting DNS Response}
-In training phase, we collect the mappings of server IP and application name.
-A mapping of server IP and application name means the application has ever established connection
-with the server whose IP is the server IP, and the server IP has ever occurred in any DNS response we have captured.
-In classifying phase, we do not use those server IPs which have more than two corresponding applications among the mappings to classify.
-We only use server IPs which have one corresponding application in the mappings to classify.
-When system detect a flow, we check whether source IP or destination IP of the flow match any of these server IPs.
-If it matches, we regard corresponding application name as classification result;
-otherwise, we use flow attributes of the flow and classification model of supervised ML to classify.
+\subsection{Procedure of the Method Based on Inspecting of DNS Responses}
+In the training phase, we collect the mappings of the server IP address and application name.
+A mapping of the server IP address and application name indicates whether the application has ever established a connection with the server, the IP address of which is identified as the server IP address, and the server IP address has ever occurred in any DNS response captured.
+In the classification phase, we do not use server IP addresses with more than two corresponding applications among the mappings for classification.
+We use only those server IP addresses with one corresponding application in the mappings for classification.
+When the system detects a flow, we examine whether the source IP or destination IP address of the flow matches any of the server IP addresses.
+If it matches, we consider the corresponding application name as the classification result; otherwise, we use flow attributes of the flow and the classification model of supervised ML for classification.
 
@@
 \includegraphics[width=3in]{./figures/evaluation_nat_result}
-\caption{Result of Multiple Table Performance Evaluation}
+\caption{Results of Multiple Table Performance Evaluation}
 \label{fig:evaluation_nat_result}
@@
 
-The single flow table framework implementation is easier than multiple flow table framework,
-but the multiple flow table framework is more flexible.
-To verify the efficacy of multiple flow table vCPE framework,
-this experiment use the NAT service to compare the throughput between single flow table vCPE and multiple flow table vCPE.
+Implementing a single flow table framework is easier than implementing a multiple flow table framework; however, multiple flow table frameworks are more flexible.
+To verify the efficiency of the multiple flow table vCPE framework, we conducted an experiment by using the NAT service to compare the throughput between single flow table vCPE and multiple flow table vCPE.
 
-To begin with, an overview of the experiment environment is shown in Fig. \ref{fig:evaluation_nat_scenario}.
-The NFV controller run on the Dell PowerEdge R630 Rack Server,
-and the SDN switch use the Pica8 P-3290 switch\cite{pica8-switch}.
-We use the iPerf2\cite{iperf} to generate the network traffic.
-The iperf server would connect the public IP address with 140.114.71.178, and then the iperf client connect to the SDN switch, and is controlled by NFV controller.
-NFV controller run the NAT service, but use the different framework that are single flow table and multiple flow table.
+An overview of the experimental environment is presented in Fig.
+\ref{fig:evaluation_nat_scenario}.
+The NFV controller was run on the Dell PowerEdge R630 rack server, and the Pica8 P-3290 switch \cite{pica8-switch} was used as the SDN switch.
+We used iPerf2 \cite{iperf} to generate network traffic.
+The iPerf server connected the public IP address with 140.114.71.178, and then the iPerf client connected to the SDN switch and was controlled by the NFV controller.
+The NFV controller ran the NAT service, but used different frameworks, a single flow table and multiple flow table.
 
-We use the iPerf to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps.
-These experiments would use diffrent payload sizes to inspect their performances.
+We used iPerf to generate UDP packets and send them to the server from the client, and we fixed the bandwidth at 100 Mbps.
+In this experiment, different payload sizes were used to evaluate the performance of the flow tables.
 As shown in Fig.
-\ref{fig:evaluation_nat_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets.
-Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well.
-We can see that the throughput value of multiple table framework is close to single table framework.
-So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other, which shown as Fig.
-\ref{fig:evaluation_nat_result}.
+\ref{fig:evaluation_nat_result}, the throughput values indicate that the performance for large packets such as 1024 bytes and 1470 bytes was higher than that for small packets.
+
+Because the NAT service is required to set the packet header field and a small payload tends to result in more packets being sent to the server simultaneously, the performance for larger packets is high.
+The throughput value of the multiple table framework is close to that of the single table framework.
+Thus, the multiple table framework is more flexible than the single table framework; however, the performance of the frameworks is similar (Fig.
+\ref{fig:evaluation_nat_result}).
 
@@
 \subsubsection{Testing Data Set}
-Testing data set are mappings of flow attributes and ground truth.
+1)	Testing Data Set: The testing data set comprised mappings of flow attributes and the ground truth.
 These mappings are also called rules.
-This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan.
+The testing data set was generated using our system in our lab in National Tsing Hua University in Taiwan.
 We manually operated applications to generate traffic.
-Each platform of an application took around 50 minutes.
-When the application identification system generated rules, it exported them into a file,
-because we wanted to do 10-fold cross validation on a testing data set.
-There are 14659 rules in total,
-and there are 137 applications if we count each platform version of an application as one application.
-The testing data set does not contain all of platform version of each application which is in this testing data set.
+An application was used for approximately 50 min for each platform.
+The application identification system generated the rules and these rules were exported into a file for performing a ten-fold cross validation of the testing data set.
+A total of 14 659 rules were generated, and 137 applications were used if each platform version of an application is counted as one application.
+The testing data set did not contain all platform versions of each application that is in
 
 \subsubsection{Validation Method}
-Although the system can do online training and classifying,
-we do offline training and classifying, shown as Fig. \ref{fig:evaluation_classification}.
-More specifically, when we did online training to analyze traffic,
-get ground truth, and export the rules into a file. We do 10-fold cross validation on the rules.
-There are 10 rounds in 10-fold cross validation. We split the data set into 10 subsets.
-At each round, we used 1 of 10 subsets as a classifying data set and the union of the other subsets as a training data set.
-Then we did 10 rounds, and each subset acted as the classifying data set exactly once.
-We implemented Classifier Light and Trainer Light, acting as Classifier and Trainer respectively without the function of analyzing traffic.
-Because there are labels in classifying data set, we can calculate accuracy.
+Although the system can perform online training and classification, we performed offline training and classification, as shown in Fig.
+\ref{fig:evaluation_classification}.
+More specifically, we performed online training to analyze traffic, obtain the ground truth, and export the rules into a file.
+We then performed a tenfold cross validation of the rules.
+The ten-fold cross validation comprised ten rounds.
+We split the data set into ten subsets.
+At each round, we used one of ten subsets as the classification data set and the combination of the other subsets as the training data set.
+Then, we performed ten rounds, and each subset acted as the classification data set once.
+We implemented Classifier Light and Trainer Light, which acted as the classifier and trainer, respectively, without the function of analyzing traffic.
+Because the classification data set contained labels, we could calculate accuracy.
 
@@
 \subsubsection{Mapping of Category Names}
-Mapping of category names: At each round of 10-fold cross validation We do name mapping on training dataset
-before we use training data set to build classification model,
-and do name mapping on classifying data set before we use classifying data set to calculate accuracy.
-The main reason is that some application have different ground truth in different operating system.
-After name mapping, there are 99 categories in testing data set.
+Mapping of Category Names: At each round of the tenfold cross validation, we applied name mapping to the training data set before we used it to build the classification model and we applied name mapping to the classification data set before we used it to calculate accuracy.
+The main reason for performing name mapping is that some applications have different ground truths in different operating systems.
+After name mapping, the testing data set contained 99 categories.
 
 \subsubsection{Accuracy Matrices and Results}
-To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
-as shown in Eq. (1), Eq. (2), and Eq. (3)\cite{muc4}. In each round in 10-fold cross validation,
-we calculate precision and recall of each category to calculate F1 score of each category.
-After ten rounds, we calculate average F1 score of each category in 10 rounds.
-Table I shows F1 score of each category in top 40 most popular applications in testing data set.
-Next, we calculate average F1 score of all categories in 10 rounds, and we get 0.9062.
-The result (Table.
-\ref{table:classification_result}) shows it achieved high accuracy, which makes QoS possible to do bandwidth control or distribution at application level.
+Accuracy Matrices and Results: To evaluate the accuracy, we used precision, recall, and the F-measure (also called the F1 score), as shown in \ref{eqn_1}, \ref{eqn_2}, and \ref{eqn_3} \cite{muc4}.
+In each round of the tenfold cross validation, we calculated the precision and recall of each category to calculate the F1 score of each category.
+After ten rounds, we calculated the average F1 scores of each category in ten rounds.
+Table I presents the F1 scores in each category of the top 40 most popular applications in the testing data set.
+Next, we calculated the average F1 score of all categories in the ten rounds as 0.9062.
+The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy, enabling QoS for bandwidth control or distribution at the application level.
 
@@
 \label{eqn_3}
-F1\ score = \dfrac{2\times Precision\times Recall}{Precsion + Recall}
+F1\ score = \dfrac{2\times Precision\times Recall}{Precision + Recall}
 \end{equation}
@@
 \begin{table}[!t]
-\caption{40 POPULAR APPLICATIONS’ AVERAGE \\ F1 SCORE IN 10 ROUNDS}
+\caption{AVERAGE F1 SCORE IN TEN ROUNDS of 40 POPULAR APPLICATIONS}
 \label{table:classification_result}
@@
 
-\subsection{Integration Evaluation: QoS Limit Host bandwidth Evaluation}
+\subsection{Evaluation of QoS When Host Bandwidth Is Limited}
 
-We choose a way to verify our function is downloading the file in that it is a situation always takes up the network recourse in real world.
-We decide to download the image of Ubuntu 14.04 which is about 1GB size.
+We verify our function by downloading a file, because downloading is a situation that always consumes network resources in practice.
+We downloaded an image of Ubuntu 14.04 that was approximately 1 GB in size.
 
-As shown in Fig.
-\ref{fig:class_classifying}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service.
-And the OpenFlow-enable switch use the the Edge-Core AS5712-54X\cite{edge-core-switch} switch that operating system is PicOS TM r2.6.
+The NFV controller ran on the Dell PowerEdge R630 rack server and executed QoS (Fig.
+\ref{fig:class_classifying}).
+The Edge-Core AS5712-54X \cite{edge-core-switch} switch was used as the OpenFlow-enabled switch with the PicOS TM r2.6 operating system.
 
-We used a desktop computer to be the experimental host and record the bandwidth in every 2 seconds.
-As shown in Fig \ref{fig:qos_limit_host}, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps in the beginning.
-At \nth{10} seconds, we wanted to limit this host’s bandwidth to 1024Kbps and we added the rule the destination MAC address is matching this desktop computer with a meter of 1024Kbps.
-Then we can find out the bandwidth from this host is decrease and be limited to about 1024Kbps immediately.
+We used a desktop computer as the experimental host to record the bandwidth every 2 s.
+As shown in Fig 13, we started downloading the file without rate limiting; the rate was between 190 000 and 410 000 Kbps initially.
+At the \nth{10} second, we limited the host bandwidth to 1024 Kbps and added the rule matching the destination MAC address with a meter of 1024 Kbps.
+Then, we determined that the bandwidth from this host decreased and was limited to approximately 1024 Kbps immediately.
 
-At \nth{36} seconds, we cancel the limit to this host.
-That is, removing the meter field from the rule in the flow table.
-Obviously, we also observed the bandwidth of download from this host is rising rapidly and without limiting.
+At the \nth{36} second, we canceled the limit to this host.
+In other words, we removed the meter field from the rule in the flow table.
+We observed that the bandwidth of the download from this host rapidly increased without rate limiting.
 
@@
 \includegraphics[width=3in]{./figures/qos_limit_host}
-\caption{Limit the download rate to a host.}
+\caption{Limiting the download rate of a host.}
 \label{fig:qos_limit_host}
@@
 \includegraphics[width=3in]{./figures/mft_qos_rate_domain_app}
-\caption{Limit the Youtube rate to a network domain.}
+\caption{Limit the rate of Youtube in a network domain.}
 \label{fig:mft_qos_rate_domain_app}
@@
 
-\subsection{Integration Evaluation: QoS Limit Application Bandwidth Evaluation}
+\subsection{Evaluation of QoS When Application Bandwidth Is Limited}
+Currently, numerous people use streaming applications, which consume a high amount of network resources. We employed application identification to determine the application to which each flow belongs.
 
-There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source.
-We integrated with application identification to classify each flow belongs what the application is, consequently.
+In our experimental environment (Fig.
+\ref{fig:class_classifying}), we used a mirror switch to replicate all traffic from the SDN switch and to enable the application identification system to classify the flows according to the applications they belong to.
+The application identification system uploaded the identification results to the database.
 
-In our experiment environment, as shown in Fig.
-\ref{fig:class_classifying}.
-We use a mirror switch to replicate the whole traffic form SDN switch and provide the application identification system to classify the flows belong which applications.
-Application identification system will upload the result of identification to database.
-Then the controller will get the result from the database and update the flow information of application.
-Therefore, we can use the flow information (5-tuple and the result of identification) to complete our limitation to application.
+Subsequently, the controller received the results from the database and updated the flow information of the applications.
+Therefore, we could use the flow information (5-tuple and identification results) to limit the application bandwidth.
 
-We choose YouTube to verify our limitation function of applications and there are 3 hosts (host 1, host 2 and host 3) in the same network domain.
-Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of host 1, host 2 and host 3.
+We selected YouTube to verify our function for limiting applications and used three hosts (Host 1, Host 2, and Host 3) in the same network domain.
+Then, we limited the bandwidth of YouTube in this network domain (i.e., the sum of bandwidths of Host 1, Host 2, and Host 3).
 
-As shown in Figure.
-\ref{fig:mft_qos_rate_domain_app}, in the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps.
-At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain.
-Therefore, we can find out the total traffic of Youtube from this network domain is reducing immediately.
-Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
+Initially, without limitation, the total bandwidth of this network was approximately 3000–4000 Kbps (Fig.
+\ref{fig:mft_qos_rate_domain_app}).
+At the \nth{8} second, we limited the total bandwidth from YouTube to 2048 Kbps.
+We observed that the total traffic from YouTube in this network domain immediately decreased.
+Clearly, the total traffic from YouTube did not exceed the set bandwidth (2048 Kbps) because we limited YouTube in this network domain.
 
-When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.
+Using this function for limiting applications, we can guarantee that the traffic in a network domain does not exceed the network capacity, thus preventing traffic congestion.
 
 \section{Conclusion}
-The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implpemented with multiple flow table management model.
-In this way, the customers only need a SDN switch at local network, and some network functions that could not have been done by single table machanism are also resolved.
+The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implemented with multiple flow table management model.
+In this way, the customers only need a SDN switch at local network, and some network functions that could not have been done by single table mechanism are also resolved.
 The experimental results show that the framework provide performance in VNF compete over single table SDN application.
-The integration evaluation also show its flexibility to integrate with any bonus applicaion identification system, IDS or IPS.
+The integration evaluation also show its flexibility to integrate with any bonus application identification system, IDS or IPS.
 

### 2017-03-08 netsoft_paper.tex
describe more in flow classification

@@
 
+\subsection{Definition of Ground Truth of Flow in Supervised ML}
+Ground truth of a flow can be defined based on server (owner of server, category of service, or name of application providing service in server), client (category or name of application in client, or name of executable file in client), or communication (transport layer protocol).
+Similar with\cite{Qazi2013} \cite{Iwai2016}, we defined ground truth of a flow based on the application establishing the flow in client for desktop applications and native mobile applications.
+As for web-based applications, we defined ground truth of a flow based on domain name of web service.
+
+\subsection{Method to Obtain Ground Truth of Flow in Supervised ML}
+We install our software on various devices establishing the flows.
+We call the software Scanner.
+Scanner has different versions for different operating systems (OSs).
+For desktop applications on Windows, trainer acts as scanner.
+It uses Windows API and local port of the flow to obtain the ground truth of the flow.
+As for Mac OS X, scanner calls the UNIX command “lsof” and parses the result to obtain lists of 5-tuples, process IDs (PIDs), and application names.
+Then scanner uses the PID and “ps” to obtain corresponding complete application names.
+As for native mobile applications on iOS, scanner uses a method similar to that used on OS X.
+However, we have to install package of UNIX command and jailbreak the iPhones before scanner runs.
+As for native mobile applications on Android, scanner calls “cat /proc/net/tcp,” “cat /proc/net/tcp6,” and “cat /proc/net/udp,” and parses the results to obtain mappings of 5-tuples and UIDs.
+Next, the Android API and UIDs are used to obtain corresponding application names as ground truth.
+Finally, mappings of 5-tuples and application names are obtained.
+For iOS and Android, scanner has to run in background.
+
+As for web-based applications, we implemented a browser in Java.
+We let it run in Windows.
+It has two main modules.
+One browses websites to generate traffic.
+It browses only one website at a time.
+The other module obtains the PID of the browser module, shortens the domain name of the currently browsed website to act as the application name, and receives requests from Scanner.
+When scanner in Windows detects an active flow, it uses the Windows API to check what process established the flow.
+It obtains the process name and the PID of the process.
+When it encounters a process name that is “java.exe” or “javaw.exe,” it sends the PID to the browser.
+If the PID is the browser’s PID, the browser sends the application name to Scanner to act as the ground truth of that flow.
+
 \subsection{Flow Attributes Adopted in Supervised ML}
@@
 Moreover, we use the application round (APPR) proposed in \cite{classfication-cloud} to analyze the flow behavior.
-We use the number of packets, packet size, transmission time, transmission direction, throughput, and APPR to define flow attributes.
-A total of 69 attributes are defined, as reported in our previous study \cite{Chia-Chin-master}.
+We use the number of packets, packet size, transmission time, transmission direction, throughput, and APPR to define flow attributes, such as total number of packets transmitted by the client, size of data transmitted by the server in Round N, and the average transmission time of each packet in Round N.A total of 69 attributes are defined, as reported in our previous study \cite{Chia-Chin-master}.
+
+\subsection{Procedure of Calculating Flow Attributes}
+When each packet comes in, the system creates or updates the information of the flow of the packet.
+The system stores the information of each flow simultaneously.
+When a flow meet the requirement to be summarized to produce statistical flow attributes, it takes less than 0.1 seconds to summarize that flow.
+The attributes of most flows, in our experience, require less than 10 seconds to calculate.
+After system calculates flow attributes, it takes less than 0.1 second to classify the answer.
 
 \subsection{Algorithms Adopted in Supervised ML}
-We used algorithms implemented by Weka, an open-source ML tool developed at the University of Waikato.
-We called the Weka Java API to build the classification model.
-In addition, we used three algorithms, RandomSupSpace with RandomTree \cite{TinKamHo1998}, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
+We use algorithms implemented by Weka, an open-source ML tool developed at the University of Waikato.
+We call the Weka Java API to build the classification model.
+We did model selection on all algorithms provided by Weka 3.8.0.
+To reduce effort, we generated two small data sets containing approximately 100 applications to act as a training data set and a classifying data set; this was done to avoid 10-fold cross validation on a testing data set.
+These data sets can be used for model selection, but they were not the data sets that were used to verify accuracy in the experiment of this study.
+Finally, considering accuracy, time to build classification model, memory usage to build and apply classification model, we use three algorithms, RandomSupSpace with RandomTree [35], FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.
+For a flow, we derive the classification result of each algorithm, and do majority voting to obtain final classification result.
+
+We studied the detail of these algorithms, and posited two reasons why these algorithms achieve high accuracy.
+One is that all of them are based on the random tree pattern, a type of decision tree that reduces overfitting by randomly selecting a subset of attributes, then selecting one attribute to split the node.
+The second reason is that two of them perform ensemble learning, a type of learning that is favorable for reducing overfitting to enhance accuracy.
 
 \subsection{Procedure of the Method Based on Inspecting of DNS Responses}
-In the training phase, we collect the mappings of the server IP address and application name.
+Similar with \cite{Plonka_flexibletraffic}, we do flow classification based on DNS responses.
+However, different from\cite{Plonka_flexibletraffic}, we link IP addresses in DNS responses to application names derived from OS of client, and use the IP addresses which have been linked to only one application to classify.
+
+More specifically, in the training phase, we collect the mappings of the server IP address and application name.
 A mapping of the server IP address and application name indicates whether the application has ever established a connection with the server, the IP address of which is identified as the server IP address, and the server IP address has ever occurred in any DNS response captured.
@@
 Next, we calculated the average F1 score of all categories in the ten rounds as 0.9062.
-The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy, enabling QoS for bandwidth control or distribution at the application level.
+The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy even there were up to 137 applications in testing data set.
+Some applications achieved higher F1 score; we believe this happened because these applications had sufficient training data, simple flow combinations, or rarely query servers that accepted requests from numerous applications.
+We will gather more data to prove our belief in the future.
+At least, it achieved high accuracy in overall, enabling QoS to effectively do bandwidth control or distribution at the application level in a local network of enterprise, where number of applications on which network manager wants to do bandwidth control may not be very large.
+In the future, we will add more applications to our testing data set.
 
@@
 \end{table}
+
+\subsubsection{Performance Analysis}
+In each round of 10-fold cross validation, after the flow classification engine received a training data set that had approximately 14659 rules, it spent around 6 minutes building a classification model on a workstation with ordinary hardware, including an Intel® Core™ i5-5200U CPU @ 2.20 GHz with 16 GB of RAM.
+When we only used supervised ML without our proposed method based on DNS responses, ClassifierLight read the classifying data set and asked the flow classification engine for a classification result.
+The system had approximately 1418 rules, and required around 5 minutes to verify accuracy.
+No out of memory errors occurred for the flow classification engine both in building classification models and classifying flows.
+We think this absence of errors happened because we chose a favorable classification algorithm so that memory usage was frugal and time required to build a model was short, even though the hardware was ordinary; 14659 rules and 99 categories existed in the training data set after name mapping.
 

### 2017-03-08 netsoft_paper.tex

@@
 This study gives an algorithm to identify applications with statistical method with machine learning.
-The algorithm only use connection “attributes” to train an identification models such as packet direction, packet length.
+The algorithm only use connection ``attributes'' to train an identification models such as packet direction, packet length.
 Afterward, the algorithm can identify network applications by this model.
@@
 A packet-in rule is always placed in the flow table of the last active service as a table miss in case there is no corresponding rule.
-To enable the service chain, the rules of each service except the last service contain an additional action, “go to next flow table,” which enables the packets to continue to pass through all active services.
+To enable the service chain, the rules of each service except the last service contain an additional action, ``go to next flow table'', which enables the packets to continue to pass through all active services.
 
 To disable a service, we must not only modify the table-miss rule but also add an enforce rule.
-Each enforce rule has maximum priority with the action “go to next flow table.” It indicates that packets still pass through the disabled service’s table, but ignore other rules and proceed to the next flow table.
+Each enforce rule has maximum priority with the action, ``go to next flow table''.
+It indicates that packets still pass through the disabled service’s table, but ignore other rules and proceed to the next flow table.
 
@@
 It uses Windows API and local port of the flow to obtain the ground truth of the flow.
-As for Mac OS X, scanner calls the UNIX command “lsof” and parses the result to obtain lists of 5-tuples, process IDs (PIDs), and application names.
-Then scanner uses the PID and “ps” to obtain corresponding complete application names.
+As for Mac OS X, scanner calls the UNIX command ``lsof'' and parses the result to obtain lists of 5-tuples, process IDs (PIDs), and application names.
+Then scanner uses the PID and ``ps'' to obtain corresponding complete application names.
 As for native mobile applications on iOS, scanner uses a method similar to that used on OS X.
 However, we have to install package of UNIX command and jailbreak the iPhones before scanner runs.
-As for native mobile applications on Android, scanner calls “cat /proc/net/tcp,” “cat /proc/net/tcp6,” and “cat /proc/net/udp,” and parses the results to obtain mappings of 5-tuples and UIDs.
+As for native mobile applications on Android, scanner calls ``cat /proc/net/tcp'', ``cat /proc/net/tcp6'', and ``cat /proc/net/udp'', and parses the results to obtain mappings of 5-tuples and UIDs.
 Next, the Android API and UIDs are used to obtain corresponding application names as ground truth.
@@
 It obtains the process name and the PID of the process.
-When it encounters a process name that is “java.exe” or “javaw.exe,” it sends the PID to the browser.
+When it encounters a process name that is ``java.exe'' or ``javaw.exe'', it sends the PID to the browser.
 If the PID is the browser’s PID, the browser sends the application name to Scanner to act as the ground truth of that flow.

### 2017-03-08 netsoft_paper.tex
fix some small error in flow classication

--- 2017-03-08 netsoft_paper.tex
@@
 \subsection{Definition of Ground Truth of Flow in Supervised ML}
-Ground truth of a flow can be defined based on server (owner of server, category of service, or name of application providing service in server), client (category or name of application in client, or name of executable file in client), or communication (transport layer protocol).
-Similar with\cite{Qazi2013} \cite{Iwai2016}, we defined ground truth of a flow based on the application establishing the flow in client for desktop applications and native mobile applications.
-As for web-based applications, we defined ground truth of a flow based on domain name of web service.
+Ground truth of a flow can be defined based on server (owner of server, category of service, or name of application providing service in server), client (category or name of application in client, or name of executable file in client), or communication (transport layer protocol, or application layer protocol).
+Similar with\cite{Qazi2013} \cite{Iwai2016}, we define ground truth of a flow based on the application establishing the flow in client for desktop applications and native mobile applications.
+As for web-based applications, we define ground truth of a flow based on domain name of web service.
 
@@
 We install our software on various devices establishing the flows.
-We call the software Scanner.
-Scanner has different versions for different operating systems (OSs).
+We call the software scanner.
+Scanner has different implementation versions for different operating systems (OSs).
 For desktop applications on Windows, trainer acts as scanner.
@@
 Next, we calculated the average F1 score of all categories in the ten rounds as 0.9062.
-The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy even there were up to 137 applications in testing data set.
+The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy even there were up to 137 applications in testing data set, enabling QoS to effectively do bandwidth control or distribution at the application level in an enterprise network.
 Some applications achieved higher F1 score; we believe this happened because these applications had sufficient training data, simple flow combinations, or rarely query servers that accepted requests from numerous applications.
-We will gather more data to prove our belief in the future.
-At least, it achieved high accuracy in overall, enabling QoS to effectively do bandwidth control or distribution at the application level in a local network of enterprise, where number of applications on which network manager wants to do bandwidth control may not be very large.
-In the future, we will add more applications to our testing data set.
+We will gather more data to prove our belief, and add more applications to testing data set in the future.
 
@@
 \subsubsection{Performance Analysis}
-In each round of 10-fold cross validation, after the flow classification engine received a training data set that had approximately 14659 rules, it spent around 6 minutes building a classification model on a workstation with ordinary hardware, including an Intel® Core™ i5-5200U CPU @ 2.20 GHz with 16 GB of RAM.
+In each round of 10-fold cross validation, after the flow classification engine received a training data set that had approximately 13241 rules, it spent around 6 minutes building a classification model on a workstation with ordinary hardware, including an Intel® Core™ i5-5200U CPU @ 2.20 GHz with 16 GB of RAM.
 When we only used supervised ML without our proposed method based on DNS responses, ClassifierLight read the classifying data set and asked the flow classification engine for a classification result.
@@
 No out of memory errors occurred for the flow classification engine both in building classification models and classifying flows.
-We think this absence of errors happened because we chose a favorable classification algorithm so that memory usage was frugal and time required to build a model was short, even though the hardware was ordinary; 14659 rules and 99 categories existed in the training data set after name mapping.
+We think this absence of errors happened because we chose a favorable classification algorithm so that memory usage was frugal and time required to build a model was short, even though the hardware was ordinary; 13241 rules and 99 categories existed in the training data set after name mapping.
 

### 2017-03-08 netsoft_paper.tex
fix name to chia an lee

--- 2017-03-08 netsoft_paper.tex
@@
 Nen-Fu Huang\IEEEauthorrefmark{1},
-Chia-An Li\IEEEauthorrefmark{1},
+Chia-An Lee\IEEEauthorrefmark{1},
 Chi-Hsuan Li\IEEEauthorrefmark{1},

### 2017-03-08 netsoft_paper.tex

--- 2017-03-08 netsoft_paper.tex
@@
 We install our software on various devices establishing the flows.
-We call the software scanner.
+We call the software Scanner.
 Scanner has different implementation versions for different operating systems (OSs).

### 2017-03-16 netsoft_paper.tex
add chia-an fix and manuscript fix

--- 2017-03-08 netsoft_paper.tex
@@
 
-\documentclass[journal]{IEEEtran}
+\documentclass[10pt,journal]{IEEEtran}
 
@@
 
+% \author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
+%         John~Doe,~\IEEEmembership{Fellow,~OSA,}
+%         and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
+% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
+% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+% GA, 30332.\protect\\
+% % note need leading \protect in front of \\ to get a newline within \thanks as
+% % \\ is fragile and will error, could use \hfil\break instead.
+% E-mail: see http://www.michaelshell.org/contact.html
+% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
+% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
 % author names and IEEE memberships
-\author{\IEEEauthorblockN{
-Nen-Fu Huang\IEEEauthorrefmark{1},
-Chia-An Li\IEEEauthorrefmark{1},
-Chi-Hsuan Li\IEEEauthorrefmark{1},
-Chia-Chi Chen\IEEEauthorrefmark{1},
-I-Hsien Hsu\IEEEauthorrefmark{1}, \\
-Che-Chuan Li\IEEEauthorrefmark{1},
-Ching-Hsuan Chen\IEEEauthorrefmark{2} and
-I-Ju Liao\IEEEauthorrefmark{1}}
-
-\IEEEauthorblockA{
-\IEEEauthorrefmark{1}
-Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan} \\
-\IEEEauthorblockA{
-\IEEEauthorrefmark{2}
-Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan}
-}
-
-% The paper headers
-% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+\author{Nen-Fu~Huang, Chia-An~Lee, Chi-Hsuan~Li, Chia-Chi~Chen, I-Hsien~Hsu,\\
+        Che-Chuan~Li, Ching-Hsuan~Chen, and~I-Ju~Liao
+\IEEEcompsocitemizethanks{
+  \IEEEcompsocthanksitem Chia-An Lee, Chi-Hsuan Li, Chia-Chi Chen, I-Hsien Hsu, Che-Chuan Li and I-Ju Liao are with the Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan E-mail: ck\_star2001@hotmail.com
+  \IEEEcompsocthanksitem Ching-Hsuan Chen is with Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan}}
 
@@
 \begin{abstract}
-In the last decade, along with the continuously developing of software defined network (SDN), numerous SDN applications have played important roles in modern network.
-Virtual Customer Premise Equipment (vCPE) is one of potential applications can make game change because it can reduce OPEX and CAPEX in the same time.
-This service compose of many technologies with complex architecture like Virtualized Network Functions (VNFs) and Service Chaining.
-Many researches discuss algorithm or mechanism to link multiple VNFs as a single Network Function Virtualization (NFV) then connect NFVs as a service chain in cloud.
-Nevertheless, the hardware resource and characteristic of SDN switch that never mention before may waste in this architecture.
-In this paper, a vCPE framework with multiple flow table management based on cloud is implemented.
-The proposed of vCPE framework is to create a SDN-enabled VNF using both resources in SDN switch and on cloud and these VNFs can be deployed as edge.
-The system is also integrated with an application identification engine based on machine learning algorithms thus providing flow control in vCPE framework with confidence.
-Experimental results show that the framework provide performance in VNF compete over single table SDN application.
+Virtual Customer Premise Equipment (vCPE) is one of the game-changing applications that could reduce OPEX and CAPEX simultaneously.
+This service is based on a complex software architecture with several technologies behind like Virtualized Network Functions (VNFs) and Service Chaining.
+Many researches have discussed algorithm or mechanism about linking multiple VNFs as a single Network Function Virtualization (NFV) in order to form a service chain in a virtual environment.
+Nevertheless, the waste of hardware resource and characteristic of SDN switch has never been mentioned before in this architecture.
+In this paper, a vCPE framework with multiple flow table management is implemented.
+This proposed vCPE framework is able to create a SDN-enabled VNF which could be deployed as the edge by employing both resources in SDN switch and on the cloud.
+Last but not least, the system is also integrated with an application identification engine based on machine learning algorithms thus providing flow control in the vCPE framework with confidence.
 \end{abstract}
@@
 We install our software on various devices establishing the flows.
-We call the software Scanner.
+We call the software scanner.
 Scanner has different implementation versions for different operating systems (OSs).
@@
 
-Initially, without limitation, the total bandwidth of this network was approximately 3000–4000 Kbps (Fig.
+Initially, without limitation, the total bandwidth of this network was approximately 3000 to 4000 Kbps (Fig.
 \ref{fig:mft_qos_rate_domain_app}).
@@
 
-\section{Conclusion}
+\section{Conlusion and Future Works}
 The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implemented with multiple flow table management model.
-In this way, the customers only need a SDN switch at local network, and some network functions that could not have been done by single table mechanism are also resolved.
-The experimental results show that the framework provide performance in VNF compete over single table SDN application.
-The integration evaluation also show its flexibility to integrate with any bonus application identification system, IDS or IPS.
+In this way, the customers only need a SDN switch at local network, and some network functions that could not be realized by single table mechanism are also resolved.
+The experimental results show that the framework provides better performance in VNF compete over single table SDN application.
+The integration evaluation also demonstrates its flexibility to integrate with any other bonus application identification system, IDS or IPS
+
+This paper implemented multiple VNF cascade system over the single-table sdn switch.
+However, the multi-table environment in experiment basing on the single-table switch environment can't achieve the better performance compare with single-table switch.
+Although the multi-table based sdn switches are available on the market, those switches have different supporting table for different flow entry which might not be compatible to the customer requirement .If the algorithm is not appropriate designed for the specific network application entry, it will cause system crashed.
+We plan to design the algorithms specifically for multi-table switch in order to minimize the possibility of the crash of the system and maximize the performance.
 
@@
 
-\begin{IEEEbiography}
-{Nen-Fu Huang}
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-{Chia-An Lee} was born in 1988. He received the B.S. degree in Undergraduate Program of Computer Science in 2010 from National Tsing Hua University, Hsinchu, Taiwan.
-Currently he is a Ph.D student of the Department of Computer Science in National Tsing Hua University.
-His research include Software Define Network ,Network Function Virtualization, Moocs, and data analytics.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-{Chi-Hsuan Li} received the B.S.
-degree in Undergraduate Program of Electrical Engineering and Computer Science in 2015 from National Tsing Hua University, Hsinchu, Taiwan.
-Currently she is a graduate student of the Department of Computer Science in National Tsing Hua University.
-Her research interest is Software Define Network and Network Function Virtualization.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/chia-chi.jpg}}]
-{Chia-Chi Chen} was born in 1994 and  received the B.S. degree in Computer Science in 2016 from National Tsing Hua University, Taiwan.
-He is a graduate student and major in Computer Science from National Tsing Hua University now.
-Mr. Chen research chiefly focuses on Software Defined Network in High Speed Network Lab at National Tsing Hua University.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/i-hsien.jpg}}]
-{I-Hsien Hsu} was born in 1994 and  received the B.S. degree in Computer Science in 2016 from National Tsing Hua University, Taiwan.
-He is a graduate student and major in Computer Science from National Tsing Hua University now.
-His research mainly focuses on Software Defined Network in High Speed Network Lab at National Tsing Hua University.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/che-chuan.jpg}}]
-{Che-Chuan Li} was born in Tainan City, Taiwan, in 1993.
-He received the B.S.
-degree in computer science from National Tsing Hua University, Hsinchu, Taiwan, in 2015.
-He is currently pursuing the M.S.
-degree in computer science at National Tsing Hua University, Hsinchu, Taiwan.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./avatars/chin-hsuan.jpg}}]
-{Ching-Hsuan Chen} received the bachelor degree in Computer Science department in 2016 from National Tsing Hua University, Hsinchu, Taiwan.
-Now he is a graduate student of the Institute of Communications Engineering in the same university, National Tsing Hua University.
-His research mainly focuses on Software Define Network and Network Function Virtualization.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}
-{I-Ju Liao}
-\end{IEEEbiography}
-
 \end{document}

### 2017-03-16 netsoft_paper.tex
fix typo

@@
 
-\subsubsection{Stateful Processing Component (VNF Controller in VM/Container)}
+\subsubsection{Stateful Processing Component (VNF Controller in VM or Container)}
 This component is used to control the workflow, maintain the state associated with the VNF, and provide an interface for service providers or customers to configure and update the behavior of the stateless datapath processing component.
@@
 
-\section{Conlusion and Future Works}
+\section{Conclusion and Future Works}
 The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implemented with multiple flow table management model.

### 2017-03-16 netsoft_paper.tex
Host -> host

@@
 Because host 2 utilizes a substantial amount of bandwidth from the network in T0–T1  the network administrator sets the host 2 rate limit to 400 Kbps.
-When the controller receives this request, marked as (a), it creates a meter with meter id = 1 and bandwidth = 400 Kbps and sets the rule in the flow table with the destination MAC address = MAC address of Host 1 and meter = 1.
+When the controller receives this request, marked as (a), it creates a meter with meter id = 1 and bandwidth = 400 Kbps and sets the rule in the flow table with the destination MAC address = MAC address of host 1 and meter = 1.
 According to our new flow table, it limits the rate of the target host.
-Then, the traffic from Host 2 is reduced and immediately limited to 400 Kbps.
-A similar situation occurs for Host 1 in T2.
-The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then the traffic from Host 1 is limited to 600 Kbps.
+Then, the traffic from host 2 is reduced and immediately limited to 400 Kbps.
+A similar situation occurs for host 1 in T2.
+The administrator chooses to set host 1 under 600 Kbps, marked as (b), and then the traffic from host 1 is limited to 600 Kbps.
 
@@
 
-We selected YouTube to verify our function for limiting applications and used three hosts (Host 1, Host 2, and Host 3) in the same network domain.
-Then, we limited the bandwidth of YouTube in this network domain (i.e., the sum of bandwidths of Host 1, Host 2, and Host 3).
+We selected YouTube to verify our function for limiting applications and used three hosts (host 1, host 2, and host 3) in the same network domain.
+Then, we limited the bandwidth of YouTube in this network domain (i.e., the sum of bandwidths of host 1, host 2, and host 3).
 
